### 2019-01-14 ms.tex
first commit

\documentclass[twocolumn]{aastex62}

\newcommand{\vdag}{(v)^\dagger}
\newcommand\aastex{AAS\TeX}
\newcommand\latex{La\TeX}

\newcommand{\project}[1]{\textsl{#1}}
\newcommand{\JWST}{\project{JWST}}
\newcommand{\HST}{\project{HST}}
\newcommand{\Spitzer}{\project{Spitzer}}
\newcommand{\Kepler}{\project{Kepler}}

\submitjournal{AJ}

\shorttitle{That's No Moon}
\shortauthors{Kreidberg et al.}

\begin{document}

\title{That's No Moon: New Analysis Shows No Evidence for Lunar Companion Orbiting Kepler-1625b}

\author{Laura Kreidberg}
\affiliation{Harvard Society of Fellows, 78 Mount Auburn Street, Cambridge, MA 02138}
\affiliation{Harvard-Smithsonian Center for Astrophysics, 60 Garden Street, Cambridge, MA 02138}
\author{Rodrigo Luger}
\author{Megan Bedell}

\begin{abstract}
The planet Kepler-1625b was recently suggested to have an EXOMOON. We present here a reanalysis of the \HST/WFC3 observations of the Kepler-1625 system. We find that the data are well fit with a single transit model. We also do a moon model, and it is not favored. Upper limit on moon. Instrument systematics? Focus searches for exomoons on alternative targets.
\end{abstract}

\keywords{planets and satellites: individual (Kepler-1625b)}

\section{Introduction} \label{sec:intro}
Moons are abundant in the Solar System, and provide clues to the formation history, evolution, and even habitability of the planets they orbit. The great scientific potential of moons has prompted extensive search for lunar companions in exoplanetary systems (exomoons), and creative development of new search techniques \citep[e.g.][]{kipping09a, kipping09b, kipping13, simon10, peters13, heller14, noyola14, hippke15, agol15, sengupta16, vanderburg18}.

Recently, a potential exomoon candidate was identified in the Kepler-1625 system \citep{teachey18a}. The host planet, Kepler-1625b, is fairly long-period large world, with a radius consistent with that of Jupiter and an orbital period of 287 days. 
long period makes it ideal for stability of moon!

It was discovered in the Analysis of the four-year \Kepler\ mission  \citep{teachey18}.

Of the FIXME transits observed by \Kepler\, FIXME what did they show.

Recently, analysis by FIXME of \Kepler\ observations of FIXME suggested a moon. Follow-up happened.

\citep{rodenbeck18} found moon was model dependent

Given the extraordinary nature of this claim, we wished to present a reanalysis.

\section{Observations} \label{sec:observations}
The Kepler-1625 system was observed with 26 continuous \HST\ orbits on 28 - 29 October, 2017 (Program GO 15149: PI: A. Teachey). The observations used Wide Field Camera 3 and the G141 grism.

\section{Data Reduction} \label{sec:reduction}
We reduced the \HST\ data using custom software developed in \cite{kreidberg14a}. We began the data reduction by fitting the centroid of the direct image with a two-dimensional Gaussian. This centroid determines the location of the spectral trace. We reduced the grism exposures with the optimal extraction routine of \citep{horne86}. The extraction box was centered on the spectral trace and spanned the pixel range (

flt
Remaining exposures: optimal extraction. For the optimal extraction, we estimateda

\subsection{Sky Subtraction}
The star Kepler-1625 is faint (H mag = FIXME) relative to most other exoplanet host stars observed with WFC3, which makes accurate background subtraction especially important for this target. Moreover, the host star is in a crowded field, so the pixels used to estimate the background must be chosen carefully to avoid contamination from other stars.  We identified several uncontaminated regions by eye: $130 < X < 215$ and $6 < Y  < 24$;  $220 < X < 250$ and $110 < X < 155$; $6 < X < 47$ and $127 < Y < 141$, where $X$ and $Y$ are pixel numbers in the spectral and spatial direction, respectively (numbering from zero).  To estimate the background and its uncertainty for each exposure, we took the median and median absolute deviation of the pixel counts in these three regions.

\subsection{Measurement of Spectral Drift}
The position of the spectrum on the detector shifts slightly over time ($\sim0.1$ pixel) due to pointing drift. This drift can significantly change the flux measured for the target star: if the spectrum moves onto less sensitive pixels, fewer photoelectrons will be recorded. To enable a correction for these variations, we measured the position of the spectrum in each exposure.

We measured position shifts using a similar approach as \cite{deming12}. We used the first exposure in the visit as a template, and interpolated all subsequent spectra to the same wavelength scale as the first. To determine shifts in the spatial direction, we summed the raw image in the spectral direction. We used the first exposure in the visit as a template, and  . For interpolation in the s

\section{Analysis}
\begin{figure*}
\includegraphics[width = 1.0 \textwidth]{figures/fig3_bestfits.pdf}
    \caption{Best fit models compared to transit light curves from this work (left) and from TK18 (right). The top panel shows the best fit no-moon model (blue), and the bottom shows the best fit moon model (red). The lower left of each panel indicates the fit rms (in ppm) and the $\Delta_{\chi_2}$ relative to the overall best fit (data reduction from this work, moon model). The dotted gray line marks the possible moon ingress identified by TK18.}
\label{fig:bestfit}
\end{figure*}

\begin{figure}
\includegraphics[width = 0.5 \textwidth]{figures/fig2_rms.pdf}
    \caption{Light curve rms versus bin size for the best fit no-moon model. The fit to data from this work (orange line) agrees well with the expected photon-limited, $\sqrt{N}$ decrease in rms with bin size (black line). The TK18 rms ranges from $1.3 - 2\times$ the photon limit for bin sizes of 1 to 20 data points. The increase in relative rms for larger bin sizes indicates that time-correlated noise is present in the TK18 data.}
\label{fig:rms}
\end{figure}

\begin{figure}
\includegraphics[width = 0.5 \textwidth]{figures/fig4_shifts.pdf}
    \caption{ Drifts}
\label{fig:shifts}
\end{figure}

\section{Discussion}
We did not find evidence for the exomoon. Why are we different from Teachey and Kipping?

\acknowledgments
Alex Teachey, Dan Foreman-Mackey

\bibliographystyle{aasjournal}
\bibliography{ms.bib}

\end{document}

% End of file `sample62.tex'.

### 2019-01-14 figures/fig1_diagnostics.py

@@ -1,0 +1,23 @@
+import numpy as np
+import matplotlib.pyplot as plt
+
+d = np.genfromtxt("12_26_23_33/diagnostics.txt")
+
+plt.subplot(311)
+plt.plot(d[:,1] - np.min(d[:,1]), d[:,3], '.k')
+plt.ylabel("Background (e-)")
+
+plt.subplot(312)
+plt.plot(d[:,1]- np.min(d[:,1]), (d[:,4] - np.median(d[:,4]))/45., '.k')
+plt.ylim(-0.2,0.2)
+plt.ylabel("Spectral shift (pix)")
+
+plt.subplot(313)
+plt.plot(d[:,1]- np.min(d[:,1]), 1.*(d[:,5] - np.mean(d[:,5])), '.k')
+plt.ylim(-0.2,0.2)
+plt.ylabel("Spatial shift (pix)")
+
+plt.xlabel("Time (days since first exposure)")
+
+plt.tight_layout()
+plt.show()

### 2019-01-14 figures/fig2_rms.py

@@ -1,0 +1,104 @@
+import numpy as np
+import matplotlib.pyplot as plt
+import pickle
+import glob, os
+from matplotlib import rc
+
+
+# COMPUTE ROOT-MEAN-SQUARE AND STANDARD ERROR OF DATA FOR VARIOUS BIN SIZES
+def computeRMS(data, maxnbins=None, binstep=1, isrmserr=False):
+    #data    = fit.normresiduals
+    #maxnbin = maximum # of bins
+    #binstep = Bin step size
+
+    # bin data into multiple bin sizes
+    npts    = data.size
+    if maxnbins is None:
+        maxnbins = npts/12.
+    binsz   = np.arange(1, maxnbins+binstep, step=binstep)
+    nbins   = np.zeros(binsz.size)
+    rms     = np.zeros(binsz.size)
+    rmserr  = np.zeros(binsz.size)
+    for i in range(binsz.size):
+        nbins[i] = int(np.floor(data.size/binsz[i]))
+        bindata   = np.zeros(int(nbins[i]), dtype=float)
+        # bin data
+        # ADDED INTEGER CONVERSION, mh 01/21/12
+        for j in range(int(nbins[i])):
+            bindata[j] = data[int(j*binsz[i]):int((j+1)*binsz[i])].mean()
+        # get rms
+        rms[i]    = np.sqrt(np.mean(bindata**2))
+        rmserr[i] = rms[i]/np.sqrt(2.*int(nbins[i]))
+    # expected for white noise (WINN 2008, PONT 2006)
+    stderr = (data.std()/np.sqrt(binsz))*np.sqrt(nbins/(nbins - 1.))
+    if isrmserr == True:
+        return rms, stderr, binsz, rmserr
+    else:
+        return rms, stderr, binsz
+
+
+# Compute standard error
+def computeStdErr(datastd, datasize, binsz):
+    #datastd  = fit.normresiduals.std()
+    #datasize = fit.normresiduals.size
+    #binsz    = array of bins
+
+    nbins   = np.zeros(binsz.size)
+    for i in range(binsz.size):
+        nbins[i] = int(np.floor(datasize/binsz[i]))
+    stderr = (datastd/np.sqrt(binsz))*np.sqrt(nbins/(nbins - 1.))
+    return stderr
+
+
+
+plt.figure(figsize = (4,3))
+
[…]

### 2019-01-14 figures/fig3_bestfits.py

@@ -1,0 +1,89 @@
+import numpy as np
+import matplotlib.pyplot as plt
+import pickle
+
+err = 379.e-6
+chi2min = 201.38
+
+plt.figure(figsize = (8.5,4))
+
+plt.subplot(221)
+plt.title("Data from this work")
+phase, data_nosys, norm_resid, t_hr, fit_hr, rms, rms_predicted, chi2, chi2red, chi2red_rms395 = pickle.load(open("lk_fits/lk_lsq_nomoon.p", "rb"))
+plt.plot(phase, data_nosys, '.k')
+plt.plot(t_hr, fit_hr, color = 'b', label = 'no moon')
+chi2 = np.sum((norm_resid/err)**2) 
+ax = plt.gca()
+ax.text( 0.03, 0.27,
+        '$\Delta_{\chi^2_\\nu} = $' + '{0:0.1f}'.format(chi2red_rms395 - chi2min)   + '\n'
+        + 'rms = ' + '{0:0d}'.format(int(rms)), 
+        verticalalignment='top',horizontalalignment='left',
+        transform=ax.transAxes, fontsize = 10
+)
+plt.xlim(-0.0035, 0.0035)
+plt.axvline(0.0016925, linestyle = 'dotted', color = '0.5')
+plt.gca().set_xticklabels([])
+plt.legend(loc = 'lower right')
+plt.ylabel("Relative flux")
+
+plt.subplot(223)
+phase, data_nosys, norm_resid, t_hr, fit_hr, rms, rms_predicted, chi2, chi2red, chi2red_rms395 = pickle.load(open("lk_fits/lk_lsq_moon.p", "rb"))
+plt.plot(phase, data_nosys, '.k')
+plt.plot(t_hr, fit_hr, color = 'r', label = 'moon')
+chi2 = np.sum((norm_resid/err)**2) 
+ax = plt.gca()
+ax.text( 0.03, 0.27,
+        '$\Delta_{\chi^2_\\nu} = $' + '{0:0.1f}'.format(chi2red_rms395 - chi2min)   + '\n'
+        + 'rms = ' + '{0:0d}'.format(int(rms)), 
+        verticalalignment='top',horizontalalignment='left',
+        transform=ax.transAxes, fontsize = 10
+)
+plt.xlim(-0.0035, 0.0035)
+plt.axvline(0.0016925, linestyle = 'dotted', color = '0.5')
+plt.ylabel("Relative flux")
[…]

### 2019-01-14 figures/fig4_shifts.py

@@ -1,0 +1,71 @@
+import numpy as np                                                              
+import matplotlib.pyplot as plt 
+
+
+a1= 9.9706e-01 	 
+a2= 9.9901e-01 	
+a3= 9.9923e-01 
+a4= 9.9951e-01
+a5= 9.9952e-01 
+a6= 9.9976e-01 
+a7= 9.9978e-01 
+a8= 9.9984e-01
+a9= 1.0000e+0
+
+a_s = [0., a1, a2, a3, a4, a5, a6, a7, a8, a9]
+
+c = 10.**6.9693
+
+a = 1.4788e-03 	 
+b = -1.0032e-02  
+
+d = np.genfromtxt("raw_orbnum.txt")
+
+t = d[:,0]
+f = d[:,1]/c
+expnum = d[:,2]
+xshifts = d[:,3]/45.
+yshifts = d[:,4]
+orbnum = d[:,5]
+
+for i in np.arange(9): 
+    ind = expnum == i
+    f[ind] /= a_s[int(i)]
+
+sys = 1. + a*xshifts + b*yshifts
+
+f /= sys
+
+plt.figure(figsize = (4,5))
+
+plt.subplot(211)
+plt.plot(t - np.min(t), xshifts, '.k', alpha = 0.5, label = "spectral")
+binf = []
+bint = []
+for i in range(24):
+    ind = orbnum == i
+    binf.append(np.mean(xshifts[ind]))
+    bint.append(np.mean(t[ind] - np.min(t)))
+#plt.plot(np.array(bint), np.array(binf), 'or')
+
+plt.ylabel("Spectral shift (pixels)")
+
+plt.subplot(212)
+plt.plot(t - np.min(t), yshifts, '.k', alpha = 0.5, label = "spatial")
+
+binf = []
+bint = []
+for i in range(24):
+    ind = orbnum == i
+    binf.append(np.mean(yshifts[ind]))
+    bint.append(np.mean(t[ind] - np.min(t)))
+#plt.plot(np.array(bint), np.array(binf), 'or')
+
+plt.ylabel("Spatial shift (pixels)")
+
+plt.xlabel("Time from first exposure (days)")
+
+
+plt.tight_layout()
+plt.savefig('fig4_shifts.pdf')
+#plt.show()

### 2019-01-14 figures/fig5_corner.py

@@ -1,0 +1,22 @@
+import numpy as np
+import mycorner as corner
+import matplotlib.pyplot as plt
+
+chain = np.load("mcmc_output/mcmc_LK.npy")
+ndim = chain.shape[-1]
+samples_lk = chain[:, 2000:10000, :].reshape((-1, ndim))
+
+chain = np.load("mcmc_output/mcmc_TK18.npy")
+ndim = chain.shape[-1]
+samples_tk = chain[:, 2000:10000, :].reshape((-1, ndim))
+
+samples_lk = samples_lk[:,5:7]
+
+samples_tk = samples_tk[:,5:7].T
+corner.corner(samples_lk, samples_tk, plot_datapoints = False, 
+            levels = [0.68, 0.95, 0.997], fill_contours = True, alpha = 0.5, 
+            color = 'blue', 
+            labels = ["Moon mid-transit time\n(BJD$_\mathrm{TDB}$ - 2458055)", 
+            "Moon radius (R$_\oplus$)"]) 
+
+plt.savefig('fig5_pairs.pdf')

### 2019-01-14 figures/mycorner.py

@@ -1,0 +1,574 @@
+from __future__ import print_function, absolute_import
+
+import logging
+import numpy as np
+import matplotlib.pyplot as pl
+from matplotlib.ticker import MaxNLocator, NullLocator
+from matplotlib.colors import LinearSegmentedColormap, colorConverter
+from matplotlib.ticker import ScalarFormatter
+
+try:
+    from scipy.ndimage import gaussian_filter
+except ImportError:
+    gaussian_filter = None
+
+__all__ = ["corner", "hist2d", "quantile"]
+
+
+def corner(xs, ys, bins=20, range=None, weights=None, color="k",
+           smooth=None, smooth1d=None,
+           labels=None, label_kwargs=None,
+           show_titles=False, title_fmt=".2f", title_kwargs=None,
+           truths=None, truth_color="#4682b4",
+           scale_hist=False, quantiles=None, verbose=False, fig=None,
+           max_n_ticks=5, top_ticks=False, use_math_text=False,
+           hist_kwargs=None, **hist2d_kwargs):
+    """
+    Make a *sick* corner plot showing the projections of a data set in a
+    multi-dimensional space. kwargs are passed to hist2d() or used for
+    `matplotlib` styling.
+    Parameters
+    ----------
+    xs : array_like[nsamples, ndim]
+        The samples. This should be a 1- or 2-dimensional array. For a 1-D
+        array this results in a simple histogram. For a 2-D array, the zeroth
+        axis is the list of samples and the next axis are the dimensions of
+        the space.
+    bins : int or array_like[ndim,]
+        The number of bins to use in histograms, either as a fixed value for
+        all dimensions, or as a list of integers for each dimension.
+    weights : array_like[nsamples,]
+        The weight of each sample. If `None` (default), samples are given
+        equal weight.
+    color : str
+        A ``matplotlib`` style color for all histograms.
+    smooth, smooth1d : float
+       The standard deviation for Gaussian kernel passed to
+       `scipy.ndimage.gaussian_filter` to smooth the 2-D and 1-D histograms
+       respectively. If `None` (default), no smoothing is applied.
+    labels : iterable (ndim,)
+        A list of names for the dimensions. If a ``xs`` is a
+        ``pandas.DataFrame``, labels will default to column names.
+    label_kwargs : dict
+        Any extra keyword arguments to send to the `set_xlabel` and
+        `set_ylabel` methods.
+    show_titles : bool
[…]

### 2019-01-15 ms.tex
extraction

@@
 \submitjournal{AJ}
+
+\sloppy
 
@@
 
-It was discovered in the Analysis of the four-year \Kepler\ mission  \citep{teachey18}.
+It was discovered in the Analysis of the four-year \Kepler\ mission  \citep{teachey18b}.
 
@@
 
-Given the extraordinary nature of this claim, we wished to present a reanalysis.
+%Given the extraordinary nature of this claim, we wished to present a reanalysis.
 
-\section{Observations} \label{sec:observations}
-The Kepler-1625 system was observed with 26 continuous \HST\ orbits on 28 - 29 October, 2017 (Program GO 15149: PI: A. Teachey). The observations used Wide Field Camera 3 and the G141 grism.
+\section{Observations and Data Reduction} \label{sec:data}
+The Kepler-1625 system was observed with 26 continuous \HST\ orbits on 28 - 29 October, 2017 (Program GO 15149: PI: A.
+Teachey).
+The observations used the Wide Field Camera 3 (WFC3) G141 grism in staring mode, which fixed the spectrum in a constant position on the detector.
+At the beginning of the visit, there was a single exposure taken with the F130N filter, which is used to determine the position of the spectral trace.
+The following exposures used the G141 grism with the \texttt{SPARS25}, \texttt{NSAMP}=15 readout pattern (exposure time of 290.8 seconds; 9 exposures per orbit).
+For additional description of the observation design, see \cite{teachey18b}.
 
-\section{Data Reduction} \label{sec:reduction}
 We reduced the \HST\ data using custom software developed in \cite{kreidberg14a}.
-We began the data reduction by fitting the centroid of the direct image with a two-dimensional Gaussian.
-This centroid determines the location of the spectral trace.
-We reduced the grism exposures with the optimal extraction routine of \citep{horne86}.
-The extraction box was centered on the spectral trace and spanned the pixel range (
+We used the \texttt{flt} data product provided by STScI, which is corrected for dark current, bias, and nonlinearity.
+The \texttt{flt} files are also flatfielded, and cosmic rays are rejected based on a fit to the up-the-ramp samples.
+To begin the data reduction, we fit the centroid of the direct image with a two-dimensional Gaussian.
+The centroid position determines the position of the spectral trace, which we calculated using the coeffients provided in the configuration file from STScI: \texttt{G141.F130N.V4.32.conf}\footnote{available at \url{http://www.stsci.edu/hst/wfc3/analysis/grism_obs/calibrations/wfc3_g141.html}}.
+We then created an extraction box centered on the spectral trace.
+We varied the height and width of the box in 1-pixel increments to find the window that minimized the root-mean-square (rms) deviation from the best fit to the transit light curve.
+The best was FIXME .
 
-flt
-Remaining exposures: optimal extraction. For the optimal extraction, we estimateda
+Using this window, we reduced the grism exposures with the optimal extraction routine of \citep{horne86}, which minimizes background noise in the extracted spectrum by weighting pixels that are dominated by the target spectrum more heavily than pixels dominated by the background.
+The inputs for the optimal extraction are the background-subtracted data array, the error array (including photon noise read noise, and uncertainty due to background subtraction), an initial guess for the spectrum and its uncertainty, and a mask array for bad pixels.
+For the error array, we used a quadrature sum of the photon noise (the square root of the pixel counts), the read noise (12 electrons for \texttt{flt} files, according to the WFC3 data handbook), and the error due to background subtraction (described in \ref{sec:background}).
+We initially masked  pixels with the data quality flag 4 or 512 (dead pixels or blobs).
+For the initial guess of the spectrum and its uncertainty, we did a simple box extraction (sum over all rows in the extraction window), and assumed the variance was equal to the box-extracted spectrum (expected for photon noise limit).
+See \ref{sec:background} for further detail on background subtraction.
 
-\subsection{Sky Subtraction}
-The star Kepler-1625 is faint (H mag = FIXME) relative to most other exoplanet host stars observed with WFC3, which makes accurate background subtraction especially important for this target.
+In brief, optimal extraction is an iterative procedure with the following steps.
+First, we create a smoothed image by median-filtering each row of the data with a 9-pixel-wide window.
+We then normalize the smoothed image by dividing each column by its sum, and multiply it by the best guess spectrum.
+We compare the smoothed image to the real data and mask outliers in the data that are greater than a threshold $\sigma_\mathrm{cut}$.
+We then recompute the best guess spectrum with the new mask and the optimal weights from \cite{horne86}.
+The process is iterated until no outliers greater than the threshold remain.
+This procedure masks any cosmic rays or bad pixels that were missed by the initial \texttt{flt} calibration.
+We tested a range of thresholds ($4 < \sigma_\mathrm{cut} < 15$) and found that different $\sigma_\mathrm{cut}$ choices did not significantly change the final transit light curve.
+The data reported in this work use $\sigma_\mathrm{cut} = 15$.
+
+%sky subtraction error - error in mean, plus uncertainty due to extraction box?; uncertainty in mean is very small (0.5 e/pix)
+%interpolation to common wavelength scale (row by row) - take out; NO DIFFERNCE
+%interpolation based on spectral drift - try both; NO DIFFERENCE
+%correct MAD to 1.4826
+%change convolution to 4 pix
+%convolution for spectral drift -
+
+\subsection{Background Subtraction} 
+\label{sec:background}
+The star Kepler-1625 is faint (H mag = 14.0) relative to most other exoplanet host stars observed with WFC3, which makes accurate background subtraction especially important for this target.
 Moreover, the host star is in a crowded field, so the pixels used to estimate the background must be chosen carefully to avoid contamination from other stars.
 We identified several uncontaminated regions by eye: $130 < X < 215$ and $6 < Y  < 24$;  $220 < X < 250$ and $110 < X < 155$; $6 < X < 47$ and $127 < Y < 141$, where $X$ and $Y$ are pixel numbers in the spectral and spatial direction, respectively (numbering from zero).
-To estimate the background and its uncertainty for each exposure, we took the median and median absolute deviation of the pixel counts in these three regions.
+To estimate the background and its uncertainty for each exposure, we took the median and median absolute deviation (MAD) of the pixel counts in these three regions.
+The per pixel uncertainty due to background subtraction is 1.4826 times the MAD.
 
-\subsection{Measurement of Spectral Drift}
-The position of the spectrum on the detector shifts slightly over time ($\sim0.1$ pixel) due to pointing drift.
-This drift can significantly change the flux measured for the target star: if the spectrum moves onto less sensitive pixels, fewer photoelectrons will be recorded.
-To enable a correction for these variations, we measured the position of the spectrum in each exposure.
+\subsection{Pointing Drift Measurement}
+The position of the spectrum on the detector shifts slightly over time ($\sim0.1$ pixel/day) due to the spacecraft's pointing drift.
+This drift can change the flux measured for the target star: if the spectrum moves onto less sensitive pixels, fewer photoelectrons are recorded.
+To enable a correction for this effect, we measured the position of the spectrum over time.
+To measure shifts in the spatial direction, we first summed each \texttt{flt} image over all columns (which we dub the ``column sum").
+We used the first exposure in the visit as a template, and for each subsequent exposure, we used least-squares minimization to calculate the shift in pixels that minimized the difference between its column sum and the template.
+The shifts are a fraction of a pixel, so we used the NumPy \texttt{interp} routine to do linear interpolation on a sub-pixel scale.
+The WFC3 point spread function is undersampled, so we convolved each column sum with a 4-pixel-wide Gaussian  before the interpolation \citep[following][]{deming13}.
 
-We measured position shifts using a similar approach as \cite{deming12}.
-We used the first exposure in the visit as a template, and interpolated all subsequent spectra to the same wavelength scale as the first.
-To determine shifts in the spatial direction, we summed the raw image in the spectral direction.
-We used the first exposure in the visit as a template, and  .
-For interpolation in the s
+To measure the spectral shifts, we repeated this procedure with two differences: (1) we used the optimally extracted spectrum rather than the column sum; and (2) in addition to calculating the best fit shift, we also calculated a best fit normalization factor (a scalar multiple for the whole spectrum), to ensure that our results are not biased by the varying brightness of the host star during the planet's transit.
+
+Figure\,\ref{fig:shifts} shows the best fit shifts.
+Over the entire 26-orbit visit, the maximum shift is less than 0.2 pixel in the spatial direction and 0.3 pixel in the spectral direction.
+The largest shift occurs after orbit 14, when the telescope reacquired the guide stars.
+
+\begin{figure}
+\includegraphics[width = 0.5 \textwidth]{figures/fig4_shifts.pdf}
+    \caption{Shift (in pixels) relative to the mean position of the spectrum in the spectral direction (top) and spatial direction (bottom).
+The largest shift occurs after orbit 14 due to a guide star reacquisition.}
+\label{fig:shifts}
+\end{figure}
 
 \section{Analysis}
+We fit the light curves with the \texttt{planetplanet} package
+
+Host star parameters were estimated using the Gaia DR2 parallax \citep{Gaia, GaiaDR2} along with UBV photometry from \citet{Everett2012} and JHK photometry from 2MASS \citep{2MASS}.
+We employed the isochrone python package \citep{isochrone} with the Dartmouth isochrone grid \citep{Dotter2008} to obtain posterior constraints on the stellar parameters.
+The resulting parameters indicate that Kepler-1625 has stellar mass $1.37^{+0.13}_{-0.16}$ M$_{\odot}$, radius $1.81^{+0.18}_{-0.16}$ R$_{\odot}$, and age $2.8^{+1.6}_{-1.2}$ Gyr.
+
+\section{Comparison with Teachey \& Kipping (2018)}
+
 \begin{figure*}
@@
     \caption{Light curve rms versus bin size for the best fit no-moon model.
-The fit to data from this work (orange line) agrees well with the expected photon-limited, $\sqrt{N}$ decrease in rms with bin size (black line).
-The TK18 rms ranges from $1.3 - 2\times$ the photon limit for bin sizes of 1 to 20 data points.
+The fit to data from this work (blue line) agrees well with the expected photon-limited, $\sqrt{N}$ decrease in rms with bin size (black line).
+The TK18 rms (red line) ranges from $1.3 - 2\times$ the photon limit for bin sizes of 1 to 20 data points.
 The increase in relative rms for larger bin sizes indicates that time-correlated noise is present in the TK18 data.}
@@
 \begin{figure}
-\includegraphics[width = 0.5 \textwidth]{figures/fig4_shifts.pdf}
-    \caption{ Drifts}
-\label{fig:shifts}
+\includegraphics[width = 0.5 \textwidth]{figures/fig5_pairs.pdf}
+    \caption{Posterior distributions}
+\label{fig:corner}
 \end{figure}
@@
 
+The HST data presented in this paper were obtained from the Mikulski Archive for Space Telescopes (MAST).
+STScI is operated by the Association of Universities for Research in Astronomy, Inc., under NASA contract NAS5-26555.
+Support for MAST for non-HST data is provided by the NASA Office of Space Science via grant NNX13AC07G and by other grants and contracts.
+We also use data from the European Space Agency (ESA) mission {\it Gaia} (\url{https://www.cosmos.esa.int/gaia}), processed by the {\it Gaia} Data Processing and Analysis Consortium (DPAC, \url{https://www.cosmos.esa.int/web/gaia/dpac/consortium}).
+Funding for the DPAC has been provided by national institutions, in particular the institutions participating in the {\it Gaia} Multilateral Agreement.
+We also use data products from the Two Micron All Sky Survey, which is a joint project of the University of Massachusetts and the Infrared Processing and Analysis Center/California Institute of Technology, funded by the National Aeronautics and Space Administration and the National Science Foundation.
+This research has made use of the SIMBAD database, operated at CDS, Strasbourg, France; the REBOUND integrator package \citep{reinliu2012rebound}; the NumPy package \citep{van2011numpy}; and NASA's Astrophysics Data System.
+
 \bibliographystyle{aasjournal}

### 2019-01-15 figures/fig2_rms.py

@@ -64,7 +64,7 @@ normfactor = stderr[0]
 #normfactor = m.rms_predicted
 plt.loglog(binsz, stderr/normfactor, color='black', ls='-', label='Expected  rms', zorder = -1) # expected noise
 #print(stderr/normfactor)
-plt.loglog(binsz, rms/normfactor*np.sqrt(chi2red), color='orange', label='This work')    # our noise
+plt.loglog(binsz, rms/normfactor*np.sqrt(chi2red), color='blue', label='This work')    # our noise
 
 print("excess over photon, LK:", binsz) 
 print("excess over photon, LK:", rms*np.sqrt(chi2red)/stderr)
@@ -75,7 +75,7 @@ d = d[ind]
 resid = d[:,1]
 rms, stderr, binsz, rmserr = computeRMS(resid, maxnbins = None, binstep = 1, isrmserr = True)
 #normfactor = m.rms_predicted
-plt.loglog(binsz, rms/normfactor*np.sqrt(chi2red), color='blue',  label='TK18')    # our noise
+plt.loglog(binsz, rms/normfactor*np.sqrt(chi2red), color='red',  label='TK18')    # our noise
 
 
 print(rms/normfactor*np.sqrt(chi2red))

### 2019-01-15 figures/fig3_bestfits.py

@@ -10,8 +10,8 @@ plt.figure(figsize = (8.5,4))
 plt.subplot(221)
 plt.title("Data from this work")
 phase, data_nosys, norm_resid, t_hr, fit_hr, rms, rms_predicted, chi2, chi2red, chi2red_rms395 = pickle.load(open("lk_fits/lk_lsq_nomoon.p", "rb"))
-plt.plot(phase, data_nosys, '.k')
-plt.plot(t_hr, fit_hr, color = 'b', label = 'no moon')
+plt.plot(phase, data_nosys, '.w', markeredgecolor = 'k')
+plt.plot(t_hr, fit_hr, color = 'b', label = 'no moon', linewidth = 2.)
 chi2 = np.sum((norm_resid/err)**2) 
 ax = plt.gca()
 ax.text( 0.03, 0.27,
@@ -28,8 +28,8 @@ plt.ylabel("Relative flux")
 
 plt.subplot(223)
 phase, data_nosys, norm_resid, t_hr, fit_hr, rms, rms_predicted, chi2, chi2red, chi2red_rms395 = pickle.load(open("lk_fits/lk_lsq_moon.p", "rb"))
-plt.plot(phase, data_nosys, '.k')
-plt.plot(t_hr, fit_hr, color = 'r', label = 'moon')
+plt.plot(phase, data_nosys, '.w', markeredgecolor = 'k')
+plt.plot(t_hr, fit_hr, color = 'b', label = 'moon', linewidth = 2.)
 chi2 = np.sum((norm_resid/err)**2) 
 ax = plt.gca()
 ax.text( 0.03, 0.27,
@@ -48,8 +48,8 @@ plt.legend(loc = 'lower right')
 plt.subplot(222)
 plt.title("Data from T&K (2018)")
 phase, data_nosys, norm_resid, t_hr, fit_hr, rms, rms_predicted, chi2, chi2red, chi2red_rms395 = pickle.load(open("teachey_fits/lsq_teachey_nomoon.p", "rb"))
-plt.plot(phase, data_nosys, '.k')
-plt.plot(t_hr, fit_hr, color = 'b', label = 'no moon')
+plt.plot(phase, data_nosys, '.w', markeredgecolor = 'k')
+plt.plot(t_hr, fit_hr, color = 'r', label = 'no moon', linewidth = 2.)
 chi2 = np.sum((norm_resid/err)**2) 
 ax = plt.gca()
 ax.text( 0.03, 0.27,
[…]

### 2019-01-15 figures/fig4_shifts.py

@@ -47,6 +47,7 @@ for i in range(24):
     binf.append(np.mean(xshifts[ind]))
     bint.append(np.mean(t[ind] - np.min(t)))
 #plt.plot(np.array(bint), np.array(binf), 'or')
+plt.ylim(-0.15, 0.15)
 
 plt.ylabel("Spectral shift (pixels)")
 
@@ -60,6 +61,7 @@ for i in range(24):
     binf.append(np.mean(yshifts[ind]))
     bint.append(np.mean(t[ind] - np.min(t)))
 #plt.plot(np.array(bint), np.array(binf), 'or')
+plt.ylim(-0.15, 0.15)
 
 plt.ylabel("Spatial shift (pixels)")
 

### 2019-01-16 ms.tex
data reduction

@@
 \newcommand{\Kepler}{\project{Kepler}}
+
+\usepackage{amsmath}
+\newcommand{\Mod}[1]{\ \mathrm{mod}\ #1}
 
@@
 We reduced the \HST\ data using custom software developed in \cite{kreidberg14a}.
-We used the \texttt{flt} data product provided by STScI, which is corrected for dark current, bias, and nonlinearity.
-The \texttt{flt} files are also flatfielded, and cosmic rays are rejected based on a fit to the up-the-ramp samples.
+This software has yielded consistent results with multiple independent pipelines \citep[e.g.][]{knutson14b, spake18}.
+We ran our pipeline on the \texttt{flt} data product provided by the Space Telescope Science Institute (STScI).
+The \texttt{flt} files are corrected for dark current, bias, and nonlinearity, and they are cleaned of cosmic ray hits based on a fit to the up-the-ramp samples.
+In keeping with previous WFC3 analysis, we discarded the first orbit of data, where the instrument systematics have larger amplitude.
+
 To begin the data reduction, we fit the centroid of the direct image with a two-dimensional Gaussian.
 The centroid position determines the position of the spectral trace, which we calculated using the coeffients provided in the configuration file from STScI: \texttt{G141.F130N.V4.32.conf}\footnote{available at \url{http://www.stsci.edu/hst/wfc3/analysis/grism_obs/calibrations/wfc3_g141.html}}.
+To process the spectra, we flatfielded the raw data using the spectroscopic flatfield coefficients provided by STScI in \texttt{WFC3.IR.G141.flat.2.fits}, following the instructions in Section 6 of the aXe User Manual\footnote{\url{http://axe-info.stsci.edu/}}.
 We then created an extraction box centered on the spectral trace.
@@
 
-Using this window, we reduced the grism exposures with the optimal extraction routine of \citep{horne86}, which minimizes background noise in the extracted spectrum by weighting pixels that are dominated by the target spectrum more heavily than pixels dominated by the background.
-The inputs for the optimal extraction are the background-subtracted data array, the error array (including photon noise read noise, and uncertainty due to background subtraction), an initial guess for the spectrum and its uncertainty, and a mask array for bad pixels.
-For the error array, we used a quadrature sum of the photon noise (the square root of the pixel counts), the read noise (12 electrons for \texttt{flt} files, according to the WFC3 data handbook), and the error due to background subtraction (described in \ref{sec:background}).
-We initially masked  pixels with the data quality flag 4 or 512 (dead pixels or blobs).
+We reduced the grism exposures with the optimal extraction routine of \citep{horne86}, which minimizes background noise in the extracted spectrum by weighting pixels that are dominated by the target spectrum more heavily than pixels dominated by the background.
+The inputs for optimal extraction are the background-subtracted data array, the error array (including photon noise read noise, and uncertainty due to background subtraction), an initial guess for the spectrum and its uncertainty, and a mask array for bad pixels.
 For the initial guess of the spectrum and its uncertainty, we did a simple box extraction (sum over all rows in the extraction window), and assumed the variance was equal to the box-extracted spectrum (expected for photon noise limit).
-See \ref{sec:background} for further detail on background subtraction.
+We measured and subtracted the background from the data array as described in \ref{sec:background}.
+For the error array, we used a quadrature sum of the photon noise (the square root of the pixel counts), the read noise (12 photoelectrons for \texttt{flt} files; WFC3 Data Handbook\footnote{\url{http://www.stsci.edu/hst/wfc3/documents/handbooks/currentDHB/}}), and the error due to background subtraction (described in \ref{sec:background}).
+The initial bad pixel mask included pixels marked with the data quality flag 4 or 512 (dead pixels or blobs).
 
 In brief, optimal extraction is an iterative procedure with the following steps.
-First, we create a smoothed image by median-filtering each row of the data with a 9-pixel-wide window.
-We then normalize the smoothed image by dividing each column by its sum, and multiply it by the best guess spectrum.
-We compare the smoothed image to the real data and mask outliers in the data that are greater than a threshold $\sigma_\mathrm{cut}$.
-We then recompute the best guess spectrum with the new mask and the optimal weights from \cite{horne86}.
+First, we created a smoothed image by median-filtering each row of the data with a 9-pixel-wide window.
+We then normalized the smoothed image by dividing each column by its sum, and multiplied it by the best guess spectrum.
+We compared the smoothed image to the real data and masked outliers in the data that are greater than a threshold $\sigma_\mathrm{cut}$.
+We then recomputed the best guess spectrum with the new mask and the optimal weights from \cite{horne86}.
 The process is iterated until no outliers greater than the threshold remain.
@@
 To enable a correction for this effect, we measured the position of the spectrum over time.
+
 To measure shifts in the spatial direction, we first summed each \texttt{flt} image over all columns (which we dub the ``column sum").
@@
 \section{Analysis}
-We fit the light curves with the \texttt{planetplanet} package
+The raw light transit light curve (shown in Figure~\ref{fig:raw}) contains both astrophysical signal and instrument systematic noise that is common to WFC3 data \citep{zhou17}.
+We model the astrophysics and the instrument systematics simultaneously.
+
+\subsection{Astrophysics Model}
+For the astrophysics, we used the \texttt{planetplanet} package \citep{luger17}, a photodynamical code that calculates light curves for multiple occulting bodies orbiting a star.
+Within \texttt{planetplanet}, the orbits are computed with the N-body integrator \texttt{REBOUND} \citep{rein??}.
+In our analysis, we considered two astrophysical scenarios: a no-moon model and a moon model.
+The free parameters for the no-moon model were: the stellar radius, the planet radius, the time of central transit, the planet inclination, and.
+We used a quadratic limb darkening law and fixed the coefficients to the prediction for FIXME from FIXME.
+We also fixed the orbital period to FIXME \citep{teachey18b}.
+Eccentricity zero, Jupiter mass.
+Varying this parameters would allow
 
@@
 The resulting parameters indicate that Kepler-1625 has stellar mass $1.37^{+0.13}_{-0.16}$ M$_{\odot}$, radius $1.81^{+0.18}_{-0.16}$ R$_{\odot}$, and age $2.8^{+1.6}_{-1.2}$ Gyr.
+
+\subsection{Instrument Systematics Model}
+There are two systematic trends in the data. One is the orbit-long ramp, attributed to charge traps in the detector filling up over the orbit \citep{zhou17}. The other is a visit-long
+
+. To model the ramp, we use the nonparametric model for the orbit-long hook from \cite{teachey18b}, which is
+
+and a decorrelation
+
+For exposure number $i$, we 
+\begin{equation}
+S_i = c_{i\Mod9}\times(1 + aX_i + bY_i) 
+\end{equation}
 

### 2019-01-17 ms.tex
analysis

@@
 In keeping with previous WFC3 analysis, we discarded the first orbit of data, where the instrument systematics have larger amplitude.
+We also discard exposures taken during the South Atlantic Anomaly passage (exposures 107, 116, 125, and 126).
 
@@
 
-We reduced the grism exposures with the optimal extraction routine of \citep{horne86}, which minimizes background noise in the extracted spectrum by weighting pixels that are dominated by the target spectrum more heavily than pixels dominated by the background.
+We reduced the grism exposures with the optimal extraction routine of \cite{horne86}, which minimizes background noise in the extracted spectrum by weighting pixels that are dominated by the target spectrum more heavily than pixels dominated by the background.
 The inputs for optimal extraction are the background-subtracted data array, the error array (including photon noise read noise, and uncertainty due to background subtraction), an initial guess for the spectrum and its uncertainty, and a mask array for bad pixels.
@@
 The data reported in this work use $\sigma_\mathrm{cut} = 15$.
+To create the braodband transit light curve, we sum each spectrum over all wavelengths.
 
@@
 The per pixel uncertainty due to background subtraction is 1.4826 times the MAD.
+
+\begin{figure}
+\includegraphics[width = 0.5 \textwidth]{figures/fig4_shifts.pdf}
+    \caption{Shift (in pixels) relative to the mean position of the spectrum in the spectral direction (top) and spatial direction (bottom).
+The largest shift occurs after orbit 14 due to a guide star reacquisition.}
+\label{fig:shifts}
+\end{figure}
 
@@
 
-\begin{figure}
-\includegraphics[width = 0.5 \textwidth]{figures/fig4_shifts.pdf}
-    \caption{Shift (in pixels) relative to the mean position of the spectrum in the spectral direction (top) and spatial direction (bottom).
-The largest shift occurs after orbit 14 due to a guide star reacquisition.}
-\label{fig:shifts}
-\end{figure}
-
 \section{Analysis}
-The raw light transit light curve (shown in Figure~\ref{fig:raw}) contains both astrophysical signal and instrument systematic noise that is common to WFC3 data \citep{zhou17}.
-We model the astrophysics and the instrument systematics simultaneously.
+The raw light transit light curve (shown in Figure~\ref{fig:raw}) contains both astrophysical signal and instrument systematic noise, which we model simultaneously.
 
@@
 Within \texttt{planetplanet}, the orbits are computed with the N-body integrator \texttt{REBOUND} \citep{rein??}.
-In our analysis, we considered two astrophysical scenarios: a no-moon model and a moon model.
-The free parameters for the no-moon model were: the stellar radius, the planet radius, the time of central transit, the planet inclination, and.
-We used a quadratic limb darkening law and fixed the coefficients to the prediction for FIXME from FIXME.
-We also fixed the orbital period to FIXME \citep{teachey18b}.
-Eccentricity zero, Jupiter mass.
-Varying this parameters would allow
+In our analysis, we considered two scenarios: a no-moon model and a moon model.
+The free parameters for the no-moon model were: the stellar radius $R_*$, the planet radius $R_\mathrm{planet}$, the time of central transit $t_\mathrm{planet}$, and the planet inclination $i$.
+For the moon model, we added a third body with radius $R_\mathrm{moon}$, transit time $t_\mathrm{moon}$, and orbital period $P_\mathrm{moon}$.
+We fixed the inclination of the moon to $90^\circ$ to exclude grazing transit scenarios, where the moon radius could be arbitrarily large.
+We also fixed the moon mass and eccentricity to zero.
+We fixed the planet's orbital period to 287.378949 days \citep{teachey18b}.
+For both the moon and no-mooon models, we fixed the planet eccentricity to zero and the mass to $1\,M_\mathrm{Jup}$.
+The \texttt{planetplanet} model uses these input parameters and returns the relative system flux for each exposure.
 
-Host star parameters were estimated using the Gaia DR2 parallax \citep{Gaia, GaiaDR2} along with UBV photometry from \citet{Everett2012} and JHK photometry from 2MASS \citep{2MASS}.
+\subsubsection{Stellar Parameters}
+For both the moon and no-moon scenarios, we used a quadratic stellar limb darkening law and fixed the coefficients to the prediction for a 5700~K, solar metallicity \texttt{PHOENIX} model from \cite{espinoza15}; $u_1, u_2 = [0.216, 0.183]$.
+
+We estimated the host star parameters using the Gaia DR2 parallax \citep{Gaia, GaiaDR2} along with UBV photometry from \citet{Everett2012} and JHK photometry from 2MASS \citep{2MASS}.
 We employed the isochrone python package \citep{isochrone} with the Dartmouth isochrone grid \citep{Dotter2008} to obtain posterior constraints on the stellar parameters.
 The resulting parameters indicate that Kepler-1625 has stellar mass $1.37^{+0.13}_{-0.16}$ M$_{\odot}$, radius $1.81^{+0.18}_{-0.16}$ R$_{\odot}$, and age $2.8^{+1.6}_{-1.2}$ Gyr.
+In our analysis, we fixed the stellar mass to the best fit value ($1.37\,M_\odot$), and used a Gaussian prior on the radius, $R_* \sim N(1.81, 0.17)$.
 
 \subsection{Instrument Systematics Model}
-There are two systematic trends in the data. One is the orbit-long ramp, attributed to charge traps in the detector filling up over the orbit \citep{zhou17}. The other is a visit-long
+There are two systematic trends in the data.
+One is the orbit-long ramp, attributed to charge traps in the detector filling up over the orbit \citep{zhou17}.
+The other is a visit-long trend over multiple orbits, which could be due to shifts in the target star position onto more/less sensitive pixels.
 
-. To model the ramp, we use the nonparametric model for the orbit-long hook from \cite{teachey18b}, which is
+To fit the orbit-long ramp, we used the non-parametric model from \cite{teachey18b}, which assigns each of the nine exposures per orbit a normalization constant, $c_1, ..., c_9$.
+To fit the visit-long trend, we used a linear combination of $X$ and $Y$ position (the shift relative to the mean in the spatial and spectral directions, respectively; shown in Figure~\ref{fig:shifts}).
+In sum, for exposure number $i$, the systematics model is:
+\begin{equation}
+S_i = c_{j}\times(1 + aX_i + bY_i) 
+\end{equation}
+where $a$ and $b$, and $c_j$ are free parameters, and $j = i\Mod9 + 1$ is the exposure number relative to the first exposure in the orbit.
 
-and a decorrelation
+We also considered a second, more complex systematics model, $S_2$, which added a visit-long quadratic trend.
+A long-term trend was favored by the \cite{teachey18b} analysis, and has been observed in other long-duration WFC3 time series \citep[e.g.][]{stevenson14, kreidberg18b}.
+The model is:
+\begin{equation}
+S_{2,i} = c_{j}\times(1 + aX_i + bY_i) \times (1 + vt_i + v_2t_i^2)
+\end{equation}
+where $v$ and $v_2$ are free parameters and $t_i$ is the time elapsed since the first exposure in the visit.
 
-For exposure number $i$, we 
-\begin{equation}
-S_i = c_{i\Mod9}\times(1 + aX_i + bY_i) 
-\end{equation}
+\subsection{Light Curve Fits}
+We fit the raw, broadband transit light curve using the models described above.
+For comparison, we also fit the raw light curve from \cite{teachey18b}.
+In total, we fit each data set with four different models:
 
-\section{Comparison with Teachey \& Kipping (2018)}
+\begin{enumerate}
+\item{No moon, non-parametric ramp, X-Y decorrelation} 
+\item{Moon, non-parametric ramp, X-Y decorrelation} 
+\item{No moon, non-parametric ramp, X-Y decorrelation, visit-long polynomial} 
+\item{Moon, non-parametric ramp, X-Y decorrelation, visit-long polynomial} 
+\end{enumerate}
+
+For each model, we determined the best fit parameters with least-squares minimization.
+We also ran a Markov chain Monte Carlo (MCMC) fit to determine the posterior probability of each parameters.
+The MCMC used the \texttt{emcee} package \citep{foremanmackey13} with 50 walkers and ran for $10^4$ steps.
+
+\section{Results}
+Figure FIXME shows the best fits.
 

### 2019-01-17 figures/fig6_rawdata.py

@@ -1,0 +1,32 @@
+import numpy as np
+import matplotlib.pyplot as plt
+
+
+d = np.genfromtxt("lc_kep1625_kreidberg.txt")
+ind = np.arange(len(d))                                                
+d = d[(ind!=106)&(ind!=115)&(ind != 0)&(ind!=124)&(ind!=125)] 
+
+
+plt.subplot(211)
+med = np.median(d[0:50, 1])
+
+plt.plot(d[:,0] - np.min(d[:,0]), d[:,1]/1.e6, '.b', alpha = 0.5, label = "This work")
+
+
+e = np.genfromtxt("prehook_correction_discrete.dat")
+med = np.median(e[0:50, 1])
+plt.plot(e[:,0] - np.min(e[:,0]), e[:,1]*290.776306/1.e6, '.r', alpha = 0.5, label = "TK18")
+plt.ylabel("Photoelectrons ($\\times10^6$)")
+
+plt.legend(loc = 'lower right')
+plt.ylim(9, 9.4)
+
+
+plt.subplot(212)
+
+plt.ylabel("Difference (e-$\\times10^6$)")
+plt.xlabel("Time since first exposure (days)")
+plt.plot(d[:,0] - np.min(d[:,0]), (d[:,1] - e[:,1]*290.776306)/1.e6, '.k', label = "difference")
+
+plt.tight_layout()
+plt.savefig("fig6_rawdata.pdf")

### 2019-01-20 ms.tex
sig test

@@
 \begin{abstract}
-The planet Kepler-1625b was recently suggested to have an EXOMOON.
-We present here a reanalysis of the \HST/WFC3 observations of the Kepler-1625 system.
-We find that the data are well fit with a single transit model.
-We also do a moon model, and it is not favored.
-Upper limit on moon.
-Instrument systematics?
-Focus searches for exomoons on alternative targets.
+    Observations of the Kepler-1625 system with the Kepler and Hubble Space Telescopes suggested the presence of a candidate exomoon, a Neptune-radius satellite orbiting a long-period Jovian planet.
+Here we present a reanalysis of the Hubble observations.
+We find that the transit light curve is well fit with a single orbiting body, and that the addition of a moon does not significantly improve the fit quality.
+The $3\,\sigma$ upper limit on the moon radius is FIXME.
+FIXME: why are we different from TK18?
+We conclude that FIXME, and future follow-up efforts for exomoons should focus on alternative targets.
 \end{abstract}
@@
 Recently, a potential exomoon candidate was identified in the Kepler-1625 system \citep{teachey18a}.
-The host planet, Kepler-1625b, is fairly long-period large world, with a radius consistent with that of Jupiter and an orbital period of 287 days.
-long period makes it ideal for stability of moon!
+The host planet, Kepler-1625b has radius consistent with that of Jupiter and an orbital period of 287 days.
+The first evidence for the exomoon candidate, Kepler-1625b I, came from three transit observations from the \Kepler\ primary mission that showed FIXME \citep{teachey18a}...
 
-It was discovered in the Analysis of the four-year \Kepler\ mission  \citep{teachey18b}.
+%Of the FIXME transits observed by \Kepler\, FIXME what did they show.
 
-Of the FIXME transits observed by \Kepler\, FIXME what did they show.
+%Recently, analysis by FIXME of \Kepler\ observations of FIXME suggested a moon. Follow-up happened.
 
-Recently, analysis by FIXME of \Kepler\ observations of FIXME suggested a moon. Follow-up happened.
-
-\citep{rodenbeck18} found moon was model dependent
-
-%Given the extraordinary nature of this claim, we wished to present a reanalysis.
+%\citep{rodenbeck18} found moon was model dependent
 
@@
 The data reported in this work use $\sigma_\mathrm{cut} = 15$.
-To create the braodband transit light curve, we sum each spectrum over all wavelengths.
+To create the broadband transit light curve, we sum each spectrum over all wavelengths.
 
@@
 For the astrophysics, we used the \texttt{planetplanet} package \citep{luger17}, a photodynamical code that calculates light curves for multiple occulting bodies orbiting a star.
-Within \texttt{planetplanet}, the orbits are computed with the N-body integrator \texttt{REBOUND} \citep{rein??}.
+Within \texttt{planetplanet}, the orbits are computed with the N-body integrator \texttt{REBOUND} \citep{rein12}.
+The \texttt{planetplanet} model returns the system flux at a specified orbital architecture and time.
+
 In our analysis, we considered two scenarios: a no-moon model and a moon model.
@@
 For the moon model, we added a third body with radius $R_\mathrm{moon}$, transit time $t_\mathrm{moon}$, and orbital period $P_\mathrm{moon}$.
-We fixed the inclination of the moon to $90^\circ$ to exclude grazing transit scenarios, where the moon radius could be arbitrarily large.
+We allowed the moon period to vary from 1.6 to 260 days.
+These limits span the duration of the \HST\ observations (so there is one possible moon occultation event), to the orbit at 0.5 the Hill radius, based on the stability limit for prograde moon orbits \citep{domingos06}.
+The Hill radius calculation assumed the planet and stellar masses are $1\,M_\mathrm{Jup}$ and $1.37\,M_\odot$.
+
+The models also had several fixed parameters.
+For the moon model, we fixed inclination of the moon to $90^\circ$ to exclude grazing transit scenarios, where the moon radius could be arbitrarily large.
 We also fixed the moon mass and eccentricity to zero.
-We fixed the planet's orbital period to 287.378949 days \citep{teachey18b}.
-For both the moon and no-mooon models, we fixed the planet eccentricity to zero and the mass to $1\,M_\mathrm{Jup}$.
-The \texttt{planetplanet} model uses these input parameters and returns the relative system flux for each exposure.
+For both the no-moon and moon models, we fixed the planet's orbital period to 287.378949 days \citep{teachey18b}.
+We also fixed the planet eccentricity to zero and the mass to $1\,M_\mathrm{Jup}$.
+These choices restrict the orbital FIXME
 
@@
 
-We also considered a second, more complex systematics model, $S_2$, which added a visit-long quadratic trend.
+%We also considered a second, more complex systematics model, $S_2$, which added a visit-long quadratic trend.
 A long-term trend was favored by the \cite{teachey18b} analysis, and has been observed in other long-duration WFC3 time series \citep[e.g.][]{stevenson14, kreidberg18b}.
 The model is:
-\begin{equation}
-S_{2,i} = c_{j}\times(1 + aX_i + bY_i) \times (1 + vt_i + v_2t_i^2)
-\end{equation}
-where $v$ and $v_2$ are free parameters and $t_i$ is the time elapsed since the first exposure in the visit.
+%\begin{equation}
+%S_{2,i} = c_{j}\times(1 + aX_i + bY_i) \times (1 + vt_i + v_2t_i^2)
+%\end{equation}
+%where $v$ and $v_2$ are free parameters and $t_i$ is the time elapsed since the first exposure in the visit.
 
@@
 For comparison, we also fit the raw light curve from \cite{teachey18b}.
-In total, we fit each data set with four different models:
-
-\begin{enumerate}
-\item{No moon, non-parametric ramp, X-Y decorrelation} 
-\item{Moon, non-parametric ramp, X-Y decorrelation} 
-\item{No moon, non-parametric ramp, X-Y decorrelation, visit-long polynomial} 
-\item{Moon, non-parametric ramp, X-Y decorrelation, visit-long polynomial} 
-\end{enumerate}
-
-For each model, we determined the best fit parameters with least-squares minimization.
+We determined the best fit model parameters with least-squares minimization.
 We also ran a Markov chain Monte Carlo (MCMC) fit to determine the posterior probability of each parameters.
 The MCMC used the \texttt{emcee} package \citep{foremanmackey13} with 50 walkers and ran for $10^4$ steps.
+We discarded the first 20\% of the MCMC chain as burn-in.
+As a quick test for convergence, we divided the remainder of the chain in half and checked that the results from the first half were consistent with the second half.
+
+%\begin{enumerate}
+%\item{No moon, non-parametric ramp, X-Y decorrelation} 
+%\item{Moon, non-parametric ramp, X-Y decorrelation} 
+%\item{No moon, non-parametric ramp, X-Y decorrelation, visit-long polynomial} 
+%\item{Moon, non-parametric ramp, X-Y decorrelation, visit-long polynomial} 
+%\end{enumerate}
 
@@
 \includegraphics[width = 0.5 \textwidth]{figures/fig5_pairs.pdf}
-    \caption{Posterior distributions}
+    \caption{Posterior distributions for the moon radius and time of central transit. Blue = this work; red = our analysis of TK18 data.}
 \label{fig:corner}
@@
 \acknowledgments
-Alex Teachey, Dan Foreman-Mackey
+Dan Foreman-Mackey
 
@@
 We also use data products from the Two Micron All Sky Survey, which is a joint project of the University of Massachusetts and the Infrared Processing and Analysis Center/California Institute of Technology, funded by the National Aeronautics and Space Administration and the National Science Foundation.
-This research has made use of the SIMBAD database, operated at CDS, Strasbourg, France; the REBOUND integrator package \citep{reinliu2012rebound}; the NumPy package \citep{van2011numpy}; and NASA's Astrophysics Data System.
+This research has made use of the SIMBAD database, operated at CDS, Strasbourg, France; the REBOUND integrator package \citep{rein12}; the NumPy package \citep{van2011numpy}; and NASA's Astrophysics Data System.
 

### 2019-01-20 figures/fig3_bestfits.py

@@ -1,21 +1,32 @@
 import numpy as np
 import matplotlib.pyplot as plt
 import pickle
+from scipy.stats import f, norm
+
+def get_significance(chi2ratio, df1, df2):
+	alpha = (1. - f.cdf(chi2ratio, df1, df2))/2.
+	z = norm.ppf(1.-alpha)
+	return z
 
 err = 379.e-6
 chi2min = 201.38
+
+#teachey_dir = "teachey_fits/"
+teachey_dir = "teachey_fits_xydecorr/"
+lk_dir = "lk_fits_new/"
 
 plt.figure(figsize = (8.5,4))
 
 plt.subplot(221)
 plt.title("Data from this work")
-phase, data_nosys, norm_resid, t_hr, fit_hr, rms, rms_predicted, chi2, chi2red, chi2red_rms395 = pickle.load(open("lk_fits/lk_lsq_nomoon.p", "rb"))
+phase, data_nosys, norm_resid, t_hr, fit_hr, rms, rms_predicted, chi2, chi2red, chi2red_rms395, dof_nomoon = pickle.load(open(lk_dir + "no_moon.p", "rb"))
 plt.plot(phase, data_nosys, '.w', markeredgecolor = 'k')
 plt.plot(t_hr, fit_hr, color = 'b', label = 'no moon', linewidth = 2.)
 chi2 = np.sum((norm_resid/err)**2) 
 ax = plt.gca()
 ax.text( 0.03, 0.27,
-        '$\Delta_{\chi^2_\\nu} = $' + '{0:0.1f}'.format(chi2red_rms395 - chi2min)   + '\n'
+        #'$\Delta{\chi^2} = $' + '{0:0.1f}'.format(chi2red_rms395 - chi2min)   + '\n'
+        '${\chi^2} = $' + '{0:0.1f}'.format(chi2)   + '\n'
         + 'rms = ' + '{0:0d}'.format(int(rms)), 
         verticalalignment='top',horizontalalignment='left',
         transform=ax.transAxes, fontsize = 10
@@ -25,15 +36,17 @@ plt.axvline(0.0016925, linestyle = 'dotted', color = '0.5')
 plt.gca().set_xticklabels([])
 plt.legend(loc = 'lower right')
 plt.ylabel("Relative flux")
+chi2nu_lk_nomoon = chi2/dof_nomoon
 
 plt.subplot(223)
[…]

### 2019-01-20 figures/fig5_corner.py

@@ -2,6 +2,8 @@ import numpy as np
 import mycorner as corner
 import matplotlib.pyplot as plt
 
+def quantile(x, q): return np.percentile(x, [100. * qi for qi in q])
+
 chain = np.load("mcmc_output/mcmc_LK.npy")
 ndim = chain.shape[-1]
 samples_lk = chain[:, 2000:10000, :].reshape((-1, ndim))
@@ -13,10 +15,11 @@ samples_tk = chain[:, 2000:10000, :].reshape((-1, ndim))
 samples_lk = samples_lk[:,5:7]
 
 samples_tk = samples_tk[:,5:7].T
-corner.corner(samples_lk, samples_tk, plot_datapoints = False, 
-            levels = [0.68, 0.95, 0.997], fill_contours = True, alpha = 0.5, 
-            color = 'blue', 
-            labels = ["Moon mid-transit time\n(BJD$_\mathrm{TDB}$ - 2458055)", 
-            "Moon radius (R$_\oplus$)"]) 
+#corner.corner(samples_lk, samples_tk, plot_datapoints = False, 
+            #levels = [0.68, 0.95, 0.997], fill_contours = True, alpha = 0.5, 
+            #color = 'blue', 
+            #labels = ["Moon mid-transit time\n(BJD$_\mathrm{TDB}$ - 2458055)", 
+            #"Moon radius (R$_\oplus$)"]) 
 
-plt.savefig('fig5_pairs.pdf')
+print(quantile(samples_lk[:, 1], [0.95, 0.997]))
+#plt.savefig('fig5_pairs.pdf')

### 2019-01-20 figures/fig6_rawdata.py

@@ -3,6 +3,7 @@ import matplotlib.pyplot as plt
 
 
 d = np.genfromtxt("lc_kep1625_kreidberg.txt")
+#d = np.genfromtxt("lc_kep1625_kreidberg_rot_1_16_19.txt")
 ind = np.arange(len(d))                                                
 d = d[(ind!=106)&(ind!=115)&(ind != 0)&(ind!=124)&(ind!=125)] 
 

### 2019-01-21 ms.tex
update aperture

@@
 \begin{abstract}
-    Observations of the Kepler-1625 system with the Kepler and Hubble Space Telescopes suggested the presence of a candidate exomoon, a Neptune-radius satellite orbiting a long-period Jovian planet.
-Here we present a reanalysis of the Hubble observations.
-We find that the transit light curve is well fit with a single orbiting body, and that the addition of a moon does not significantly improve the fit quality.
+    Observations of the Kepler-1625 system with the Kepler and Hubble Space Telescopes have suggested the presence of a candidate exomoon, a Neptune-radius satellite orbiting a long-period Jovian planet.
+Here we present a new analysis of the Hubble observations from an independent data reduction pipeline.
+We find that the transit light curve is well fit with a planet-only model, and that the addition of a moon does not significantly improve the fit quality.
 The $3\,\sigma$ upper limit on the moon radius is FIXME.
@@
 We varied the height and width of the box in 1-pixel increments to find the window that minimized the root-mean-square (rms) deviation from the best fit to the transit light curve.
-The best was FIXME .
+The best was $443  < X < 578$, and $517 < Y < 531$, where $X$ and $Y$ are physical pixels in the spectral and spatial direction, respectively.
 
@@
 
-The models also had several fixed parameters.
+The models also fixes several parameters that are poorly constrained by the light curve shape.
 For the moon model, we fixed inclination of the moon to $90^\circ$ to exclude grazing transit scenarios, where the moon radius could be arbitrarily large.
@@
 We also fixed the planet eccentricity to zero and the mass to $1\,M_\mathrm{Jup}$.
-These choices restrict the orbital FIXME
 
@@
 
+%For more direct comparison with \citep{teachey18b}, we also considered a second systematics model that included three terms: (1) a visit-long second order polynomial trend in time, and (2) a constant offset after orbit 14.
 %We also considered a second, more complex systematics model, $S_2$, which added a visit-long quadratic trend.
@@
 %\begin{equation}
-%S_{2,i} = c_{j}\times(1 + aX_i + bY_i) \times (1 + vt_i + v_2t_i^2)
+%S_{2,i} = c_{j} \times (1 + vt_i + v_2t_i^2)
 %\end{equation}
@@
 We fit the raw, broadband transit light curve using the models described above.
-For comparison, we also fit the raw light curve from \cite{teachey18b}.
 We determined the best fit model parameters with least-squares minimization.
@@
 
-\section{Discussion}
-We did not find evidence for the exomoon. Why are we different from Teachey and Kipping?
+\section{Comparison with Teachey \& Kipping 2018}
+For comparison, we also fit the raw light curve from \cite{teachey18b}.
 

### 2019-01-21 figures/fig3_bestfits.py

@@ -8,11 +8,12 @@ def get_significance(chi2ratio, df1, df2):
 	z = norm.ppf(1.-alpha)
 	return z
 
-err = 379.e-6
+err = 370.e-6
 chi2min = 201.38
 
 #teachey_dir = "teachey_fits/"
-teachey_dir = "teachey_fits_xydecorr/"
+#teachey_dir = "teachey_fits_xydecorr/"
+teachey_dir = "teachey_fits_poly2d_tophat/"
 lk_dir = "lk_fits_new/"
 
 plt.figure(figsize = (8.5,4))
@@ -27,7 +28,7 @@ ax = plt.gca()
 ax.text( 0.03, 0.27,
         #'$\Delta{\chi^2} = $' + '{0:0.1f}'.format(chi2red_rms395 - chi2min)   + '\n'
         '${\chi^2} = $' + '{0:0.1f}'.format(chi2)   + '\n'
-        + 'rms = ' + '{0:0d}'.format(int(rms)), 
+        + 'rms = ' + '{0:0.1f}'.format(rms), 
         verticalalignment='top',horizontalalignment='left',
         transform=ax.transAxes, fontsize = 10
 )
@@ -47,7 +48,7 @@ ax = plt.gca()
 ax.text( 0.03, 0.27,
 #        '$\Delta{\chi^2} = $' + '{0:0.1f}'.format(chi2red_rms395 - chi2min)   + '\n'
         '${\chi^2} = $' + '{0:0.1f}'.format(chi2)   + '\n'
-        + 'rms = ' + '{0:0d}'.format(int(rms)), 
+        + 'rms = ' + '{0:0.1f}'.format(rms), 
         verticalalignment='top',horizontalalignment='left',
         transform=ax.transAxes, fontsize = 10
 )
@@ -74,7 +75,7 @@ ax = plt.gca()
 ax.text( 0.03, 0.27,
         #'$\Delta{\chi^2} = $' + '{0:0.1f}'.format(chi2red_rms395 - chi2min)   + '\n'
         '${\chi^2} = $' + '{0:0.1f}'.format(chi2)   + '\n'
-        + 'rms = ' + '{0:0d}'.format(int(rms)), 
+        + 'rms = ' + '{0:0.1f}'.format(rms), 
         verticalalignment='top',horizontalalignment='left',
         transform=ax.transAxes, fontsize = 10
 )
@@ -94,7 +95,7 @@ ax = plt.gca()
 ax.text( 0.03, 0.27,
[…]

### 2019-01-22 ms.tex
new mcmc

@@
 We find that the transit light curve is well fit with a planet-only model, and that the addition of a moon does not significantly improve the fit quality.
-The $3\,\sigma$ upper limit on the moon radius is FIXME.
+The $3\,\sigma$ upper limit on the moon radius is $3.5R_\oplus$.
 FIXME: why are we different from TK18?
@@
 We varied the height and width of the box in 1-pixel increments to find the window that minimized the root-mean-square (rms) deviation from the best fit to the transit light curve.
-The best was $443  < X < 578$, and $517 < Y < 531$, where $X$ and $Y$ are physical pixels in the spectral and spatial direction, respectively.
+The best was $445  < X < 569$, and $517 < Y < 531$, where $X$ and $Y$ are physical pixels in the spectral and spatial direction, respectively.
 

### 2019-01-22 figures/fig3_bestfits.py

@@ -8,7 +8,7 @@ def get_significance(chi2ratio, df1, df2):
 	z = norm.ppf(1.-alpha)
 	return z
 
-err = 370.e-6
+err = 370.e-6*np.sqrt(1.078)
 chi2min = 201.38
 
 #teachey_dir = "teachey_fits/"
@@ -19,7 +19,7 @@ lk_dir = "lk_fits_new/"
 plt.figure(figsize = (8.5,4))
 
 plt.subplot(221)
-plt.title("Data from this work")
+plt.title("This Work")
 phase, data_nosys, norm_resid, t_hr, fit_hr, rms, rms_predicted, chi2, chi2red, chi2red_rms395, dof_nomoon = pickle.load(open(lk_dir + "no_moon.p", "rb"))
 plt.plot(phase, data_nosys, '.w', markeredgecolor = 'k')
 plt.plot(t_hr, fit_hr, color = 'b', label = 'no moon', linewidth = 2.)
@@ -66,7 +66,7 @@ chi2ratio = chi2nu_lk_moon/chi2nu_lk_nomoon
 print("significance", get_significance(chi2ratio, dof_moon, dof_nomoon))
 
 plt.subplot(222)
-plt.title("Data from T&K (2018)")
+plt.title("Teachey & Kipping (2018)")
 phase, data_nosys, norm_resid, t_hr, fit_hr, rms, rms_predicted, chi2, chi2red, chi2red_rms395 = pickle.load(open(teachey_dir + "lsq_teachey_nomoon.p", "rb"))
 plt.plot(phase, data_nosys, '.w', markeredgecolor = 'k')
 plt.plot(t_hr, fit_hr, color = 'r', label = 'no moon', linewidth = 2.)

### 2019-01-22 figures/fig5_corner.py

@@ -6,7 +6,7 @@ def quantile(x, q): return np.percentile(x, [100. * qi for qi in q])
 
 chain = np.load("mcmc_output/mcmc_LK.npy")
 ndim = chain.shape[-1]
-samples_lk = chain[:, 2000:10000, :].reshape((-1, ndim))
+samples_lk = chain[:, 1000:5000, :].reshape((-1, ndim))
 
 chain = np.load("mcmc_output/mcmc_TK18.npy")
 ndim = chain.shape[-1]
@@ -15,11 +15,11 @@ samples_tk = chain[:, 2000:10000, :].reshape((-1, ndim))
 samples_lk = samples_lk[:,5:7]
 
 samples_tk = samples_tk[:,5:7].T
-#corner.corner(samples_lk, samples_tk, plot_datapoints = False, 
-            #levels = [0.68, 0.95, 0.997], fill_contours = True, alpha = 0.5, 
-            #color = 'blue', 
-            #labels = ["Moon mid-transit time\n(BJD$_\mathrm{TDB}$ - 2458055)", 
-            #"Moon radius (R$_\oplus$)"]) 
+corner.corner(samples_lk, samples_tk, plot_datapoints = False, 
+            levels = [0.68, 0.95, 0.997], fill_contours = True, alpha = 0.5, 
+            color = 'blue', 
+            labels = ["Moon mid-transit time\n(BJD$_\mathrm{TDB}$ - 2458055)", 
+            "Moon radius (R$_\oplus$)"]) 
 
 print(quantile(samples_lk[:, 1], [0.95, 0.997]))
-#plt.savefig('fig5_pairs.pdf')
+plt.savefig('fig5_pairs.pdf')

### 2019-01-22 figures/fig3_bestfits.py
moon ingress

@@ -8,8 +8,9 @@ def get_significance(chi2ratio, df1, df2):
 	z = norm.ppf(1.-alpha)
 	return z
 
-err = 370.e-6*np.sqrt(1.078)
+err = 362.2e-6
 chi2min = 201.38
+moon_ingress = 0.00191
 
 #teachey_dir = "teachey_fits/"
 #teachey_dir = "teachey_fits_xydecorr/"
@@ -33,7 +34,7 @@ ax.text( 0.03, 0.27,
         transform=ax.transAxes, fontsize = 10
 )
 plt.xlim(-0.0035, 0.0035)
-plt.axvline(0.0016925, linestyle = 'dotted', color = '0.5')
+plt.axvline(moon_ingress, linestyle = 'dotted', color = '0.5')
 plt.gca().set_xticklabels([])
 plt.legend(loc = 'lower right')
 plt.ylabel("Relative flux")
@@ -53,7 +54,7 @@ ax.text( 0.03, 0.27,
         transform=ax.transAxes, fontsize = 10
 )
 plt.xlim(-0.0035, 0.0035)
-plt.axvline(0.0016925, linestyle = 'dotted', color = '0.5')
+plt.axvline(moon_ingress, linestyle = 'dotted', color = '0.5')
 plt.ylabel("Relative flux")
 plt.xlabel("Orbital phase")
 plt.legend(loc = 'lower right')
@@ -81,7 +82,7 @@ ax.text( 0.03, 0.27,
 )
 plt.gca().set_xticklabels([])
 plt.gca().set_yticklabels([])
-plt.axvline(0.0016925, linestyle = 'dotted', color = '0.5')
+plt.axvline(moon_ingress, linestyle = 'dotted', color = '0.5')
 plt.xlim(-0.0035, 0.0035)
 plt.legend(loc = 'lower right')
 
@@ -100,7 +101,7 @@ ax.text( 0.03, 0.27,
         transform=ax.transAxes, fontsize = 10
 )
 plt.gca().set_yticklabels([])
-plt.axvline(0.0016925, linestyle = 'dotted', color = '0.5')
+plt.axvline(moon_ingress, linestyle = 'dotted', color = '0.5')
 plt.xlim(-0.0035, 0.0035)
 plt.xlabel("Orbital phase")
 

### 2019-01-22 figures/fig6_rawdata.py

@@ -1,26 +1,33 @@
 import numpy as np
 import matplotlib.pyplot as plt
 
+moon_ingress = 1.3
 
 d = np.genfromtxt("lc_kep1625_kreidberg.txt")
 #d = np.genfromtxt("lc_kep1625_kreidberg_rot_1_16_19.txt")
 ind = np.arange(len(d))                                                
+d= d[np.argsort(d[:,0])]
 d = d[(ind!=106)&(ind!=115)&(ind != 0)&(ind!=124)&(ind!=125)] 
+print("len lk", len(d[:,0]))
 
 
+plt.figure(figsize = (4.5,4.5))
 plt.subplot(211)
 med = np.median(d[0:50, 1])
 
 plt.plot(d[:,0] - np.min(d[:,0]), d[:,1]/1.e6, '.b', alpha = 0.5, label = "This work")
+#plt.plot(d[:,0] - np.min(d[:,0]), np.log(d[:,1]), '.b', alpha = 0.5, label = "This work")
 
 
 e = np.genfromtxt("prehook_correction_discrete.dat")
+print("len tk", len(e[:,0]))
 med = np.median(e[0:50, 1])
 plt.plot(e[:,0] - np.min(e[:,0]), e[:,1]*290.776306/1.e6, '.r', alpha = 0.5, label = "TK18")
+#plt.plot(e[:,0] - np.min(e[:,0]), np.log(e[:,1]*290.776306), '.r', alpha = 0.5, label = "TK18")
 plt.ylabel("Photoelectrons ($\\times10^6$)")
 
-plt.legend(loc = 'lower right')
-plt.ylim(9, 9.4)
+plt.legend(loc = 'center right')
+#plt.ylim(9, 9.4)
 
 
 plt.subplot(212)
@@ -28,6 +35,7 @@ plt.subplot(212)
 plt.ylabel("Difference (e-$\\times10^6$)")
 plt.xlabel("Time since first exposure (days)")
 plt.plot(d[:,0] - np.min(d[:,0]), (d[:,1] - e[:,1]*290.776306)/1.e6, '.k', label = "difference")
+plt.axvline(moon_ingress, linestyle = 'dotted', color = '0.5')
 
 plt.tight_layout()
 plt.savefig("fig6_rawdata.pdf")

### 2019-01-22 figures/fig3_bestfits.py
analysis

@@ -8,9 +8,13 @@ def get_significance(chi2ratio, df1, df2):
 	z = norm.ppf(1.-alpha)
 	return z
 
-err = 362.2e-6
+#err = 362.22e-6
+err = 367.e-6
 chi2min = 201.38
-moon_ingress = 0.00191
+#moon_ingress = 0.00191
+moon_ingress = 1.3
+period = 287.378949 
+xmin, xmax = -0.3, 1.7
 
 #teachey_dir = "teachey_fits/"
 #teachey_dir = "teachey_fits_xydecorr/"
@@ -22,18 +26,25 @@ plt.figure(figsize = (8.5,4))
 plt.subplot(221)
 plt.title("This Work")
 phase, data_nosys, norm_resid, t_hr, fit_hr, rms, rms_predicted, chi2, chi2red, chi2red_rms395, dof_nomoon = pickle.load(open(lk_dir + "no_moon.p", "rb"))
-plt.plot(phase, data_nosys, '.w', markeredgecolor = 'k')
-plt.plot(t_hr, fit_hr, color = 'b', label = 'no moon', linewidth = 2.)
+plt.plot(period*phase - period*np.min(phase), data_nosys, '.w', markeredgecolor = 'k')
+plt.plot(period*(t_hr) - period*np.min(phase), fit_hr, color = 'b', label = 'no moon', linewidth = 2.)
 chi2 = np.sum((norm_resid/err)**2) 
+
+npoints = len(phase)
+nfreepar = 219 - dof_nomoon
+BIC_LK_nomoon = chi2 + nfreepar*np.log(npoints)
+BIC = chi2 + nfreepar*np.log(npoints)
 ax = plt.gca()
-ax.text( 0.03, 0.27,
-        #'$\Delta{\chi^2} = $' + '{0:0.1f}'.format(chi2red_rms395 - chi2min)   + '\n'
-        '${\chi^2} = $' + '{0:0.1f}'.format(chi2)   + '\n'
-        + 'rms = ' + '{0:0.1f}'.format(rms), 
+ax.text( 0.03, 0.51,
+        '$\mathrm{rms} =$' + '{0:0.1f}'.format(rms) + '\n' 
+        + '${\chi^2} = $' + '{0:0.1f}'.format(chi2) + '\n'
+        + '$\mathrm{dof} =$' + '{0:0d}'.format(int(dof_nomoon)) + '\n'
[…]

### 2019-01-22 figures/fig5_corner.py

@@ -22,4 +22,6 @@ corner.corner(samples_lk, samples_tk, plot_datapoints = False,
             "Moon radius (R$_\oplus$)"]) 
 
 print(quantile(samples_lk[:, 1], [0.95, 0.997]))
+print(quantile(samples_tk[1, :], [0.003, 0.16, 0.5, 0.84]))
+print(quantile(samples_tk[0, :], [0.16, 0.5, 0.84]) + 2458055.)
 plt.savefig('fig5_pairs.pdf')

### 2019-01-22 figures/mycorner.py

@@ -272,12 +272,16 @@ def corner(xs, ys, bins=20, range=None, weights=None, color="k",
             if top_ticks:
                 ax.xaxis.set_ticks_position("top")
                 [l.set_rotation(45) for l in ax.get_xticklabels()]
+                for tick in ax.xaxis.get_major_ticks():
+                    tick.label.set_fontsize(14) 
             else:
                 ax.set_xticklabels([])
         else:
             [l.set_rotation(45) for l in ax.get_xticklabels()]
+            for tick in ax.xaxis.get_major_ticks():
+                tick.label.set_fontsize(14) 
             if labels is not None:
-                ax.set_xlabel(labels[i], **label_kwargs)
+                ax.set_xlabel(labels[i], fontsize = 14, **label_kwargs)
                 ax.xaxis.set_label_coords(0.5, -0.3)
 
             # use MathText for axes ticks
@@ -331,8 +335,10 @@ def corner(xs, ys, bins=20, range=None, weights=None, color="k",
                 ax.set_xticklabels([])
             else:
                 [l.set_rotation(45) for l in ax.get_xticklabels()]
+                for tick in ax.xaxis.get_major_ticks():
+                    tick.label.set_fontsize(14) 
                 if labels is not None:
-                    ax.set_xlabel(labels[j], **label_kwargs)
+                    ax.set_xlabel(labels[j], fontsize= 14, **label_kwargs)
                     ax.xaxis.set_label_coords(0.5, -0.3)
 
                 # use MathText for axes ticks
@@ -343,8 +349,10 @@ def corner(xs, ys, bins=20, range=None, weights=None, color="k",
                 ax.set_yticklabels([])
             else:
                 [l.set_rotation(45) for l in ax.get_yticklabels()]
+                for tick in ax.yaxis.get_major_ticks():
+                    tick.label.set_fontsize(14) 
                 if labels is not None:
-                    ax.set_ylabel(labels[i], **label_kwargs)
+                    ax.set_ylabel(labels[i], fontsize = 14, **label_kwargs)
                     ax.yaxis.set_label_coords(-0.3, 0.5)
 
                 # use MathText for axes ticks

### 2019-01-23 ms.tex
pairs'
results

@@
 We find that the transit light curve is well fit with a planet-only model, and that the addition of a moon does not significantly improve the fit quality.
-The $3\,\sigma$ upper limit on the moon radius is $3.5R_\oplus$.
+The $3\,\sigma$ upper limit on the moon radius is $4.0R_\oplus$.
 FIXME: why are we different from TK18?
@@
 \begin{equation}
+\label{eq:sys}
 S_i = c_{j}\times(1 + aX_i + bY_i) 
@@
 We also ran a Markov chain Monte Carlo (MCMC) fit to determine the posterior probability of each parameters.
-The MCMC used the \texttt{emcee} package \citep{foremanmackey13} with 50 walkers and ran for $10^4$ steps.
+The MCMC used the \texttt{emcee} package \citep{foremanmackey13} with 50 walkers and ran for 5000 steps.
 We discarded the first 20\% of the MCMC chain as burn-in.
-As a quick test for convergence, we divided the remainder of the chain in half and checked that the results from the first half were consistent with the second half.
-
-%\begin{enumerate}
-%\item{No moon, non-parametric ramp, X-Y decorrelation} 
-%\item{Moon, non-parametric ramp, X-Y decorrelation} 
-%\item{No moon, non-parametric ramp, X-Y decorrelation, visit-long polynomial} 
-%\item{Moon, non-parametric ramp, X-Y decorrelation, visit-long polynomial} 
-%\end{enumerate}
+As a quick test for convergence, we divided the remainder of the chain in half and confirmed that the results from the first half were consistent with the second half.
 
 \section{Results}
-Figure FIXME shows the best fits.
+We obtained an excellent fit to the light curve with the no-moon model, as illustrated in  Figure\,\ref{fig:bestfit}.
+The residuals to our no-moon model fit have rms equal to 362.2 parts per million (ppm), which is within 2\% of the predicted photon shot noise (367 ppm), and yields a $\chi_\nu^2 = 1.05$.
+The binned rms decreases with the square root of the number of points per bin, as expected for photon noise-limited statistics (see rms versus bin size in Figure~\ref{fig:rms}).
+
+We also obtained a good fit with the moon model; however, the addition of three more free parameters does not significantly improve the fit quality.
+The best fit moon model has a radius $r_\mathrm{moon} = 2.4R_\oplus$, a mid-transit time $t_\mathrm{moon} = 2458055.2869\,\mathrm{BJD_{TDB}}$, and a period $P_m = 26.5$ days.
+This fit has a slightly lower rms than the no-moon model (359.5 ppm versus 362.2 ppm), but the $\chi_\nu^2$ is unchanged (also $1.05$).
+According to the Bayesian information criterion \citep[BIC;][]{kass95}, the moon model is disfavored with $\Delta\mathrm{BIC} = 13$, which constitutes strong evidence against the inclusion of a moon.
+In addition, the moon transit time is not well-constrained by the data.
+As shown in the posterior distribution in Figure~\ref{fig:corner}, the $2\,\sigma$ confidence interval for the moon's transit includes the entire visit.
+The upper limit on the moon radius is $3.2\,R_\oplus$ at $2\sigma$ confidence and $4.0\,R_\oplus$ at $3\sigma$.
+
+\subsection{Comparison with Teachey \& Kipping (2018)}
+For comparison, we also fit the raw TK18 data using the no-moon and moon models (best fits shown in Figure\,\ref{fig:bestfit}).
+We tested the same detrending model described above (decorrelation with the spectrum's $X$ and $Y$ position), but found that it did not perform as well as the systematics models presented in TK18 (10\% higher rms and time-correlated residuals).
+We therefore opted to use a TK18 systematics model to enable a fair comparison between our results.
+We used a second-order polynomial trend in time, a constant offset after orbit 14 (where the guide stars are reacquired), and the non-parameteric orbit-long ramp model.
+This model has one more free parameter than the systematics model given in Equation~\ref{eq:sys}.
+
+Our results are consistent with those presented in TK18, including the large improvement in $\chi^2$ when the moon is included ($\Delta\chi^2 = 22.0$).
+The posterior distribution for the moon radius is $r_\mathrm{moon} = 4.0^{+0.8}_{-0.6}\,R_\oplus$ ($>2.1\,R_\oplus$ at $3\sigma$ confidence), and the moon transit time is centered on $t_\mathrm{moon} =  2458056.29^{+0.06}_{-0.04}\,\mathrm{BJD_{TDB}}$ (as shown in Figure\,\ref{fig:corner}).
+
+Compared to fits to our data, the fits to the TK18 data have a larger rms.
+Notably, the moon model fit to the TK18 data has a larger rms than the no-moon fit to our data (363.4 versus 362.2 ppm), even though it has four additional free parameters.
+This difference in fit quality corresponds to $\Delta\mathrm{BIC} = 23.9$, which is strong evidence against the moon model.
+We obtain a better fit (a lower $\chi^2$) with the no-moon model fit to our data than we obtain with the moon model fit to the TK18 data, even though it has four additional free parameters.
 
@@
 The top panel shows the best fit no-moon model (blue), and the bottom shows the best fit moon model (red).
-The lower left of each panel indicates the fit rms (in ppm) and the $\Delta_{\chi_2}$ relative to the overall best fit (data reduction from this work, moon model).
+The lower left of each panel indicates the fit rms (in ppm), the ${\chi_2}$, the degrees of freedom, and the change in GIC relative to the lowest value.
 The dotted gray line marks the possible moon ingress identified by TK18.}
@@
 
-\section{Comparison with Teachey \& Kipping 2018}
-For comparison, we also fit the raw light curve from \cite{teachey18b}.
+\begin{figure}
+\includegraphics[width = 0.5 \textwidth]{figures/fig6_rawdata.pdf}
+    \caption{Comparison of raw data.}
+\label{fig:raw}
+\end{figure}
+
+\section{Discussion and Conclusion}
+We found
+approach to data reduction was very similar, but of the data reduction, and
 

### 2019-01-23 ms.tex
finished results

@@
 We varied the height and width of the box in 1-pixel increments to find the window that minimized the root-mean-square (rms) deviation from the best fit to the transit light curve.
-The best was $445  < X < 569$, and $517 < Y < 531$, where $X$ and $Y$ are physical pixels in the spectral and spatial direction, respectively.
+The best was $445  < \mathrm{X} < 569$, and $517 < \mathrm{Y} < 531$, where X and Y are physical pixels in the spectral and spatial direction, respectively.
 
@@
 Moreover, the host star is in a crowded field, so the pixels used to estimate the background must be chosen carefully to avoid contamination from other stars.
-We identified several uncontaminated regions by eye: $130 < X < 215$ and $6 < Y  < 24$;  $220 < X < 250$ and $110 < X < 155$; $6 < X < 47$ and $127 < Y < 141$, where $X$ and $Y$ are pixel numbers in the spectral and spatial direction, respectively (numbering from zero).
+We identified several uncontaminated regions by eye: $130 < \mathrm{X} < 215$ and $6 < \mathrm{Y}  < 24$;  $220 < \mathrm{X} < 250$ and $110 < \mathrm{X} < 155$; $6 < \mathrm{X} < 47$ and $127 < \mathrm{Y} < 141$, where X and Y are pixel numbers in the spectral and spatial direction, respectively (numbering from zero).
 To estimate the background and its uncertainty for each exposure, we took the median and median absolute deviation (MAD) of the pixel counts in these three regions.
@@
 To fit the orbit-long ramp, we used the non-parametric model from \cite{teachey18b}, which assigns each of the nine exposures per orbit a normalization constant, $c_1, ..., c_9$.
-To fit the visit-long trend, we used a linear combination of $X$ and $Y$ position (the shift relative to the mean in the spatial and spectral directions, respectively; shown in Figure~\ref{fig:shifts}).
-In sum, for exposure number $i$, the systematics model is:
+To fit the visit-long trend, we used a linear combination of X and Y position (the shift relative to the mean in the spatial and spectral directions, respectively; shown in Figure~\ref{fig:shifts}).
+In sum, for exposure number $i$, the systematics model S is:
 \begin{equation}
 \label{eq:sys}
-S_i = c_{j}\times(1 + aX_i + bY_i) 
+    \mathrm{S}_i = c_{j}\times(1 + a\mathrm{X}_i + b\mathrm{Y}_i) 
 \end{equation}
@@
 
+\begin{figure*}
+\includegraphics[width = 1.0 \textwidth]{figures/fig3_bestfits.pdf}
+    \caption{Best fit models compared to normalized transit light curves from this work (left) and from TK18 (right).
+The top panel shows the best fit no-moon model (blue), and the bottom shows the best fit moon model (red).
+The lower left of each panel indicates the fit rms (in ppm), the $\chi_2$, the degrees of freedom, and the change in BIC relative to the lowest value.
+Each light curve is divided by its best fit systematics model (XY decorrelation for this work; second-order polynomial and offset for TK18).
+The dotted gray line marks the possible moon ingress identified by TK18.}
+\label{fig:bestfit}
+\end{figure*}
+
 \subsection{Light Curve Fits}
@@
 We also ran a Markov chain Monte Carlo (MCMC) fit to determine the posterior probability of each parameters.
+For the MCMC, we held the ramp parameters $c_1, ..., c_9$ fixed at their best-fit values.
 The MCMC used the \texttt{emcee} package \citep{foremanmackey13} with 50 walkers and ran for 5000 steps.
@@
 This fit has a slightly lower rms than the no-moon model (359.5 ppm versus 362.2 ppm), but the $\chi_\nu^2$ is unchanged (also $1.05$).
-According to the Bayesian information criterion \citep[BIC;][]{kass95}, the moon model is disfavored with $\Delta\mathrm{BIC} = 13$, which constitutes strong evidence against the inclusion of a moon.
+According to the Bayesian information criterion (BIC), which penalizes unnecessary model complexity, the moon model is disfavored with $\Delta\mathrm{BIC} = 13$.
+This constitutes strong evidence against the inclusion of a moon \citep{kass95}.
 In addition, the moon transit time is not well-constrained by the data.
@@
 \subsection{Comparison with Teachey \& Kipping (2018)}
-For comparison, we also fit the raw TK18 data using the no-moon and moon models (best fits shown in Figure\,\ref{fig:bestfit}).
-We tested the same detrending model described above (decorrelation with the spectrum's $X$ and $Y$ position), but found that it did not perform as well as the systematics models presented in TK18 (10\% higher rms and time-correlated residuals).
+\cite{teachey18b} found evidence for the transit of a Neptune-size moon in their analysis of the HST data, in contrast to the results findings here.
+To make a direct comparison with their results, we fit the raw TK18 data directly.
+
+We fit the data with both the no-moon and models.
+For the systematics, we tested the XY decorrelation model described above, but found that it did not perform as well as the systematics models presented in TK18 (10\% higher rms and time-correlated residuals).
 We therefore opted to use a TK18 systematics model to enable a fair comparison between our results.
@@
 This model has one more free parameter than the systematics model given in Equation~\ref{eq:sys}.
+Figure\,\ref{fig:bestfit} shows the best fit models.
 
-Our results are consistent with those presented in TK18, including the large improvement in $\chi^2$ when the moon is included ($\Delta\chi^2 = 22.0$).
-The posterior distribution for the moon radius is $r_\mathrm{moon} = 4.0^{+0.8}_{-0.6}\,R_\oplus$ ($>2.1\,R_\oplus$ at $3\sigma$ confidence), and the moon transit time is centered on $t_\mathrm{moon} =  2458056.29^{+0.06}_{-0.04}\,\mathrm{BJD_{TDB}}$ (as shown in Figure\,\ref{fig:corner}).
+Overall, we find that the TK18 fits have a larger rms than the fits to our new data reduction.
+The no-moon model has an rms of 381.5 ppm (compared to 362.2 for our data).
+As TK18 found, the moon model improves the rms to 363.4 ppm ($\Delta\chi^2 = 22.0$); however, even with the additional four free parameters, the moon model does not perform as well as the no-moon model fit to our data.
+This difference in fit quality corresponds to $\Delta\mathrm{BIC} = 23.9$, which is strong evidence against the moon.
+%Even when a moon is included, the fit is still slightly worse (rms of 363.4 ppm) than our best no-moon model, in spite of four additional free parameters.
 
-Compared to fits to our data, the fits to the TK18 data have a larger rms.
-Notably, the moon model fit to the TK18 data has a larger rms than the no-moon fit to our data (363.4 versus 362.2 ppm), even though it has four additional free parameters.
-This difference in fit quality corresponds to $\Delta\mathrm{BIC} = 23.9$, which is strong evidence against the moon model.
-We obtain a better fit (a lower $\chi^2$) with the no-moon model fit to our data than we obtain with the moon model fit to the TK18 data, even though it has four additional free parameters.
+The moon model also yields qualitatively different posterior distributions for the two data sets.
+For the TK18 data, the moon radius and transit time are peaked at $r_\mathrm{moon} = 4.0^{+0.8}_{-0.6}\,R_\oplus$ ($>2.1\,R_\oplus$ at $3\sigma$ confidence), and $t_\mathrm{moon} =  2458056.29^{+0.06}_{-0.04}\,\mathrm{BJD_{TDB}}$ (as shown in Figure\,\ref{fig:corner}).
+By contrast, the fit to the new data only yields an upper limit on the moon radius of ($4.0\,R_\oplus$ at $3\sigma$ confidence), and the transit time is unconstrained.
 
-\begin{figure*}
-\includegraphics[width = 1.0 \textwidth]{figures/fig3_bestfits.pdf}
-    \caption{Best fit models compared to transit light curves from this work (left) and from TK18 (right).
-The top panel shows the best fit no-moon model (blue), and the bottom shows the best fit moon model (red).
-The lower left of each panel indicates the fit rms (in ppm), the ${\chi_2}$, the degrees of freedom, and the change in GIC relative to the lowest value.
-The dotted gray line marks the possible moon ingress identified by TK18.}
-\label{fig:bestfit}
-\end{figure*}
+%Our results are consistent with those originally published in TK18, including the large improvement in $\chi^2$ when the moon is included ($\Delta\chi^2 = 22.0$). The posterior distribution for
+
+%We obtain a better fit (a lower $\chi^2$) with the no-moon model fit to our data than we obtain with the moon model fit to the TK18 data, even though it has four additional free parameters.
 

### 2019-01-23 figures/fig3_bestfits.py

@@ -12,7 +12,7 @@ def get_significance(chi2ratio, df1, df2):
 err = 367.e-6
 chi2min = 201.38
 #moon_ingress = 0.00191
-moon_ingress = 1.3
+moon_ingress = 1.25
 period = 287.378949 
 xmin, xmax = -0.3, 1.7
 
@@ -35,7 +35,7 @@ nfreepar = 219 - dof_nomoon
 BIC_LK_nomoon = chi2 + nfreepar*np.log(npoints)
 BIC = chi2 + nfreepar*np.log(npoints)
 ax = plt.gca()
-ax.text( 0.03, 0.51,
+ax.text( 0.03, 0.52,
         '$\mathrm{rms} =$' + '{0:0.1f}'.format(rms) + '\n' 
         + '${\chi^2} = $' + '{0:0.1f}'.format(chi2) + '\n'
         + '$\mathrm{dof} =$' + '{0:0d}'.format(int(dof_nomoon)) + '\n'
@@ -59,7 +59,7 @@ chi2 = np.sum((norm_resid/err)**2)
 nfreepar = 219 - dof_moon
 BIC = chi2 + nfreepar*np.log(npoints)
 ax = plt.gca()
-ax.text( 0.03, 0.51,
+ax.text( 0.03, 0.52,
         '$\mathrm{rms} =$' + '{0:0.1f}'.format(rms) + '\n' 
         + '${\chi^2} = $' + '{0:0.1f}'.format(chi2) + '\n'
         + '$\mathrm{dof} =$' + '{0:0d}'.format(int(dof_moon)) + '\n'
@@ -91,7 +91,7 @@ dof_nomoon = 203
 nfreepar = 219 - dof_nomoon
 BIC = chi2 + nfreepar*np.log(npoints)
 ax = plt.gca()
-ax.text( 0.03, 0.51,                                                            
+ax.text( 0.03, 0.52,                                                            
         '$\mathrm{rms} =$' + '{0:0.1f}'.format(rms) + '\n'                      
         + '${\chi^2} = $' + '{0:0.1f}'.format(chi2) + '\n'                      
         + '$\mathrm{dof} =$' + '{0:0d}'.format(int(dof_nomoon)) + '\n'            
@@ -116,7 +116,7 @@ dof_moon = 200
 nfreepar = 219 - dof_moon                                                     
 BIC = chi2 + nfreepar*np.log(npoints)  
 ax = plt.gca()
-ax.text( 0.03, 0.51,                                                            
[…]

### 2019-01-23 figures/fig4_shifts.py

@@ -36,7 +36,7 @@ sys = 1. + a*xshifts + b*yshifts
 
 f /= sys
 
-plt.figure(figsize = (4,5))
+plt.figure(figsize = (4,4))
 
 plt.subplot(211)
 plt.plot(t - np.min(t), xshifts, '.k', alpha = 0.5, label = "spectral")

### 2019-01-23 figures/fig6_rawdata.py

@@ -1,7 +1,7 @@
 import numpy as np
 import matplotlib.pyplot as plt
 
-moon_ingress = 1.3
+moon_ingress = 1.25
 
 d = np.genfromtxt("lc_kep1625_kreidberg.txt")
 #d = np.genfromtxt("lc_kep1625_kreidberg_rot_1_16_19.txt")

### 2019-01-23 ms.tex
start discussion

@@
 
+\begin{figure}
+\includegraphics[width = 0.5 \textwidth]{figures/fig6_rawdata.pdf}
+    \caption{Top: raw data from this work (blue) compared to TK18 (red).
+Bottom: the difference in raw photoelectron counts between the data sets.
+The moon ingress identified by TK18 is marked by the dotted gray line.}
+\label{fig:raw}
+\end{figure}
+
 \section{Analysis}
@@
 We also fixed the planet eccentricity to zero and the mass to $1\,M_\mathrm{Jup}$.
+
+\begin{figure*}
+\includegraphics[width = 1.0 \textwidth]{figures/fig3_bestfits.pdf}
+    \caption{Best fit models compared to normalized transit light curves from this work (left) and from TK18 (right).
+The top panel shows the best fit no-moon model (blue), and the bottom shows the best fit moon model (red).
+The lower left of each panel indicates the fit rms (in ppm), the $\chi_2$, the degrees of freedom, and the change in BIC relative to the lowest value.
+Each light curve is divided by its best fit systematics model (XY decorrelation for this work; second-order polynomial and offset for TK18).
+The dotted gray line marks the possible moon ingress identified by TK18.}
+\label{fig:bestfit}
+\end{figure*}
 
@@
 
-%For more direct comparison with \citep{teachey18b}, we also considered a second systematics model that included three terms: (1) a visit-long second order polynomial trend in time, and (2) a constant offset after orbit 14.
-%We also considered a second, more complex systematics model, $S_2$, which added a visit-long quadratic trend.
-A long-term trend was favored by the \cite{teachey18b} analysis, and has been observed in other long-duration WFC3 time series \citep[e.g.][]{stevenson14, kreidberg18b}.
-The model is:
-%\begin{equation}
-%S_{2,i} = c_{j} \times (1 + vt_i + v_2t_i^2)
-%\end{equation}
-%where $v$ and $v_2$ are free parameters and $t_i$ is the time elapsed since the first exposure in the visit.
-
-\begin{figure*}
-\includegraphics[width = 1.0 \textwidth]{figures/fig3_bestfits.pdf}
-    \caption{Best fit models compared to normalized transit light curves from this work (left) and from TK18 (right).
-The top panel shows the best fit no-moon model (blue), and the bottom shows the best fit moon model (red).
-The lower left of each panel indicates the fit rms (in ppm), the $\chi_2$, the degrees of freedom, and the change in BIC relative to the lowest value.
-Each light curve is divided by its best fit systematics model (XY decorrelation for this work; second-order polynomial and offset for TK18).
-The dotted gray line marks the possible moon ingress identified by TK18.}
-\label{fig:bestfit}
-\end{figure*}
-
 \subsection{Light Curve Fits}
@@
 
+\begin{figure}
+\includegraphics[width = 0.5 \textwidth]{figures/fig2_rms.pdf}
+    \caption{Light curve rms versus bin size for the best fit no-moon model.
+The fit to data from this work (blue line) agrees well with the expected photon-limited, $\sqrt{N}$ decrease in rms with bin size (black line).
+The TK18 rms (red line) ranges from $1.3 - 2\times$ the photon limit for bin sizes of 1 to 20 data points.
+The increase in relative rms for larger bin sizes indicates that time-correlated noise is present in the TK18 data.}
+\label{fig:rms}
+\end{figure}
+
 We also obtained a good fit with the moon model; however, the addition of three more free parameters does not significantly improve the fit quality.
@@
 \subsection{Comparison with Teachey \& Kipping (2018)}
-\cite{teachey18b} found evidence for the transit of a Neptune-size moon in their analysis of the HST data, in contrast to the results findings here.
+\cite{teachey18b} found evidence for the transit of a Neptune-size moon in their analysis of the HST data, in contrast to the findings presented here.
 To make a direct comparison with their results, we fit the raw TK18 data directly.
@@
 \begin{figure}
-\includegraphics[width = 0.5 \textwidth]{figures/fig2_rms.pdf}
-    \caption{Light curve rms versus bin size for the best fit no-moon model.
-The fit to data from this work (blue line) agrees well with the expected photon-limited, $\sqrt{N}$ decrease in rms with bin size (black line).
-The TK18 rms (red line) ranges from $1.3 - 2\times$ the photon limit for bin sizes of 1 to 20 data points.
-The increase in relative rms for larger bin sizes indicates that time-correlated noise is present in the TK18 data.}
-\label{fig:rms}
-\end{figure}
-
-\begin{figure}
 \includegraphics[width = 0.5 \textwidth]{figures/fig5_pairs.pdf}
-    \caption{Posterior distributions for the moon radius and time of central transit. Blue = this work; red = our analysis of TK18 data.}
+    \caption{Posterior distributions for the moon radius and time of transit based on an MCMC fit to data from this work (blue) and from TK18 (red).
+The shading corresponds to $1-$, $2-$, and $3\sigma$ contours (darkest to lightest).
+These values are marginalized over all other model parameters.
+The diagonal shows the normalized posterior probability density.}
 \label{fig:corner}
@@
 
-\begin{figure}
-\includegraphics[width = 0.5 \textwidth]{figures/fig6_rawdata.pdf}
-    \caption{Comparison of raw data.}
-\label{fig:raw}
-\end{figure}
+\section{Conclusion}
+In this work, we presented an independent analysis of HST observations of the Kepler-1625 system.
+In contrast to previous analysis by \citep{teachey18b}, we do not find evidence for the transit of a moon.
 
-\section{Discussion and Conclusion}
-We found
+what is 
 approach to data reduction was very similar, but of the data reduction, and
@@
 \acknowledgments
-Dan Foreman-Mackey
-
 The HST data presented in this paper were obtained from the Mikulski Archive for Space Telescopes (MAST).

### 2019-01-23 ms-temp.tex
discussing

--- 2019-01-23 ms.tex
@@
 Moreover, the host star is in a crowded field, so the pixels used to estimate the background must be chosen carefully to avoid contamination from other stars.
-We identified several uncontaminated regions by eye: $130 < \mathrm{X} < 215$ and $6 < \mathrm{Y}  < 24$;  $220 < \mathrm{X} < 250$ and $110 < \mathrm{X} < 155$; $6 < \mathrm{X} < 47$ and $127 < \mathrm{Y} < 141$, where X and Y are pixel numbers in the spectral and spatial direction, respectively (numbering from zero).
-To estimate the background and its uncertainty for each exposure, we took the median and median absolute deviation (MAD) of the pixel counts in these three regions.
-The per pixel uncertainty due to background subtraction is 1.4826 times the MAD.
+To estimate the background counts, we masked pixels with total counts larger than 800 electrons and took the median count in the unmasked pixels.
+The per pixel uncertainty due to background subtraction is 1.4826 times the median absolute deviation.
+
+%We identified several uncontaminated regions by eye: $130 < \mathrm{X} < 215$ and $6 < \mathrm{Y}  < 24$;  $220 < \mathrm{X} < 250$ and $110 < \mathrm{X} < 155$; $6 < \mathrm{X} < 47$ and $127 < \mathrm{Y} < 141$, where X and Y are pixel numbers in the spectral and spatial direction, respectively (numbering from zero).
 
@@
 \includegraphics[width = 1.0 \textwidth]{figures/fig3_bestfits.pdf}
-    \caption{Best fit models compared to normalized transit light curves from this work (left) and from TK18 (right).
-The top panel shows the best fit no-moon model (blue), and the bottom shows the best fit moon model (red).
+    \caption{Best fit models compared to normalized transit light curves from this work (left, blue) and from TK18 (right, red).
+The top panel shows the best fit no-moon model, and the bottom shows the best fit moon model.
 The lower left of each panel indicates the fit rms (in ppm), the $\chi_2$, the degrees of freedom, and the change in BIC relative to the lowest value.
@@
 
+\section{Discussion}
+We  do not recover the moon
+differs both in the data reduction and the choice of systematics model
+neither
+
+many choices
+rotate the image, aperture choice, measurement of the background, outlier masking,
+
 \section{Conclusion}
@@
 
-\bibliographystyle{aasjournal}
-\bibliography{ms.bib}
+\newcommand{\noop}[1]{}
+\begin{thebibliography}{}
+\expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi
+\providecommand{\url}[1]{\href{#1}{#1}}
+\providecommand{\dodoi}[1]{doi:~\href{http://doi.org/#1}{\nolinkurl{#1}}}
+\providecommand{\doeprint}[1]{\href{http://ascl.net/#1}{\nolinkurl{http://ascl.net/#1}}}
+\providecommand{\doarXiv}[1]{\href{https://arxiv.org/abs/#1}{\nolinkurl{https://arxiv.org/abs/#1}}}
+
+\bibitem[{{Agol} {et~al.}(2015){Agol}, {Jansen}, {Lacy}, {Robinson}, \&
+  {Meadows}}]{agol15}
+{Agol}, E., {Jansen}, T., {Lacy}, B., {Robinson}, T.~D., \& {Meadows}, V. 2015,
+  \apj, 812, 5, \dodoi{10.1088/0004-637X/812/1/5}
+
+\bibitem[{{Deming} {et~al.}(2013){Deming}, {Wilkins}, {McCullough}, {Burrows},
+  {Fortney}, {Agol}, {Dobbs-Dixon}, {Madhusudhan}, {Crouzet}, {Desert},
+  {Gilliland}, {Haynes}, {Knutson}, {Line}, {Magic}, {Mandell}, {Ranjan},
+  {Charbonneau}, {Clampin}, {Seager}, \& {Showman}}]{deming13}
+{Deming}, D., {Wilkins}, A., {McCullough}, P., {et~al.} 2013, \apj, 774, 95,
+  \dodoi{10.1088/0004-637X/774/2/95}
+
+\bibitem[{{Domingos} {et~al.}(2006){Domingos}, {Winter}, \&
+  {Yokoyama}}]{domingos06}
+{Domingos}, R.~C., {Winter}, O.~C., \& {Yokoyama}, T. 2006, \mnras, 373, 1227,
+  \dodoi{10.1111/j.1365-2966.2006.11104.x}
+
+\bibitem[{{Dotter} {et~al.}(2008){Dotter}, {Chaboyer}, {Jevremovi{\'c}},
+  {Kostov}, {Baron}, \& {Ferguson}}]{Dotter2008}
+{Dotter}, A., {Chaboyer}, B., {Jevremovi{\'c}}, D., {et~al.} 2008, \apjs, 178,
+  89, \dodoi{10.1086/589654}
+
+\bibitem[{{Espinoza} \& {Jord{\'a}n}(2015)}]{espinoza15}
+{Espinoza}, N., \& {Jord{\'a}n}, A. 2015, \mnras, 450, 1879,
+  \dodoi{10.1093/mnras/stv744}
+
+\bibitem[{{Everett} {et~al.}(2012){Everett}, {Howell}, \&
+  {Kinemuchi}}]{Everett2012}
+{Everett}, M.~E., {Howell}, S.~B., \& {Kinemuchi}, K. 2012, Publications of the
+  Astronomical Society of the Pacific, 124, 316, \dodoi{10.1086/665529}
+
+\bibitem[{{Foreman-Mackey} {et~al.}(2013){Foreman-Mackey}, {Hogg}, {Lang}, \&
+  {Goodman}}]{foremanmackey13}
+{Foreman-Mackey}, D., {Hogg}, D.~W., {Lang}, D., \& {Goodman}, J. 2013, \pasp,
+  125, 306, \dodoi{10.1086/670067}
+
+\bibitem[{{Gaia Collaboration} {et~al.}(2016){Gaia Collaboration}, {Prusti},
+  {de Bruijne}, {Brown}, {Vallenari}, {Babusiaux}, {Bailer-Jones}, {Bastian},
+  {Biermann}, {Evans}, {Eyer}, {Jansen}, {Jordi}, {Klioner}, {Lammers},
+  {Lindegren}, {Luri}, {Mignard}, {Milligan}, {Panem}, {Poinsignon},
+  {Pourbaix}, {Randich}, {Sarri}, {Sartoretti}, {Siddiqui}, {Soubiran},
+  {Valette}, {van Leeuwen}, {Walton}, {Aerts}, {Arenou}, {Cropper}, {Drimmel},
+  {H{\o}g}, {Katz}, {Lattanzi}, {O'Mullane}, {Grebel}, {Holland}, {Huc},
+  {Passot}, {Bramante}, {Cacciari}, {Casta{\~n}eda}, {Chaoul}, {Cheek}, {De
+  Angeli}, {Fabricius}, {Guerra}, {Hern{\'a}ndez}, {Jean-Antoine-Piccolo},
+  {Masana}, {Messineo}, {Mowlavi}, {Nienartowicz}, {Ord{\'o}{\~n}ez- Blanco},
+  {Panuzzo}, {Portell}, {Richards}, {Riello}, {Seabroke}, {Tanga},
+  {Th{\'e}venin}, {Torra}, {Els}, {Gracia- Abril}, {Comoretto},
+  {Garcia-Reinaldos}, {Lock}, {Mercier}, {Altmann}, {Andrae}, {Astraatmadja},
+  {Bellas-Velidis}, {Benson}, {Berthier}, {Blomme}, {Busso}, {Carry},
+  {Cellino}, {Clementini}, {Cowell}, {Creevey}, {Cuypers}, {Davidson}, {De
+  Ridder}, {de Torres}, {Delchambre}, {Dell'Oro}, {Ducourant}, {Fr{\'e}mat},
+  {Garc{\'\i}a-Torres}, {Gosset}, {Halbwachs}, {Hambly}, {Harrison}, {Hauser},
+  {Hestroffer}, {Hodgkin}, {Huckle}, {Hutton}, {Jasniewicz}, {Jordan},
+  {Kontizas}, {Korn}, {Lanzafame}, {Manteiga}, {Moitinho}, {Muinonen},
+  {Osinde}, {Pancino}, {Pauwels}, {Petit}, {Recio-Blanco}, {Robin}, {Sarro},
+  {Siopis}, {Smith}, {Smith}, {Sozzetti}, {Thuillot}, {van Reeven}, {Viala},
+  {Abbas}, {Abreu Aramburu}, {Accart}, {Aguado}, {Allan}, {Allasia},
+  {Altavilla}, {{\'A}lvarez}, {Alves}, {Anderson}, {Andrei}, {Anglada Varela},
+  {Antiche}, {Antoja}, {Ant{\'o}n}, {Arcay}, {Atzei}, {Ayache}, {Bach},
+  {Baker}, {Balaguer-N{\'u}{\~n}ez}, {Barache}, {Barata}, {Barbier}, {Barblan},
+  {Baroni}, {Barrado y Navascu{\'e}s}, {Barros}, {Barstow}, {Becciani},
+  {Bellazzini}, {Bellei}, {Bello Garc{\'\i}a}, {Belokurov}, {Bendjoya},
+  {Berihuete}, {Bianchi}, {Bienaym{\'e}}, {Billebaud}, {Blagorodnova},
+  {Blanco-Cuaresma}, {Boch}, {Bombrun}, {Borrachero}, {Bouquillon}, {Bourda},
+  {Bouy}, {Bragaglia}, {Breddels}, {Brouillet}, {Br{\"u}semeister},
+  {Bucciarelli}, {Budnik}, {Burgess}, {Burgon}, {Burlacu}, {Busonero}, {Buzzi},
+  {Caffau}, {Cambras}, {Campbell}, {Cancelliere}, {Cantat-Gaudin}, {Carlucci},
+  {Carrasco}, {Castellani}, {Charlot}, {Charnas}, {Charvet}, {Chassat},
+  {Chiavassa}, {Clotet}, {Cocozza}, {Collins}, {Collins}, {Costigan}, {Crifo},
+  {Cross}, {Crosta}, {Crowley}, {Dafonte}, {Damerdji}, {Dapergolas}, {David},
+  {David}, {De Cat}, {de Felice}, {de Laverny}, {De Luise}, {De March}, {de
+  Martino}, {de Souza}, {Debosscher}, {del Pozo}, {Delbo}, {Delgado},
+  {Delgado}, {di Marco}, {Di Matteo}, {Diakite}, {Distefano}, {Dolding}, {Dos
+  Anjos}, {Drazinos}, {Dur{\'a}n}, {Dzigan}, {Ecale}, {Edvardsson}, {Enke},
+  {Erdmann}, {Escolar}, {Espina}, {Evans}, {Eynard Bontemps}, {Fabre},
+  {Fabrizio}, {Faigler}, {Falc{\~a}o}, {Farr{\`a}s Casas}, {Faye}, {Federici},
+  {Fedorets}, {Fern{\'a}ndez-Hern{\'a}ndez}, {Fernique}, {Fienga}, {Figueras},
+  {Filippi}, {Findeisen}, {Fonti}, {Fouesneau}, {Fraile}, {Fraser}, {Fuchs},
+  {Furnell}, {Gai}, {Galleti}, {Galluccio}, {Garabato}, {Garc{\'\i}a-Sedano},
+  {Gar{\'e}}, {Garofalo}, {Garralda}, {Gavras}, {Gerssen}, {Geyer}, {Gilmore},
+  {Girona}, {Giuffrida}, {Gomes}, {Gonz{\'a}lez-Marcos},
+  {Gonz{\'a}lez-N{\'u}{\~n}ez}, {Gonz{\'a}lez-Vidal}, {Granvik}, {Guerrier},
+  {Guillout}, {Guiraud}, {G{\'u}rpide}, {Guti{\'e}rrez-S{\'a}nchez}, {Guy},
+  {Haigron}, {Hatzidimitriou}, {Haywood}, {Heiter}, {Helmi}, {Hobbs},
+  {Hofmann}, {Holl}, {Holland}, {Hunt}, {Hypki}, {Icardi}, {Irwin}, {Jevardat
+  de Fombelle}, {Jofr{\'e}}, {Jonker}, {Jorissen}, {Julbe}, {Karampelas},
+  {Kochoska}, {Kohley}, {Kolenberg}, {Kontizas}, {Koposov}, {Kordopatis},
+  {Koubsky}, {Kowalczyk}, {Krone-Martins}, {Kudryashova}, {Kull}, {Bachchan},
+  {Lacoste-Seris}, {Lanza}, {Lavigne}, {Le Poncin-Lafitte}, {Lebreton},
+  {Lebzelter}, {Leccia}, {Leclerc}, {Lecoeur-Taibi}, {Lemaitre}, {Lenhardt},
+  {Leroux}, {Liao}, {Licata}, {Lindstr{\o}m}, {Lister}, {Livanou}, {Lobel},
+  {L{\"o}ffler}, {L{\'o}pez}, {Lopez-Lozano}, {Lorenz}, {Loureiro},
+  {MacDonald}, {Magalh{\~a}es Fernandes}, {Managau}, {Mann}, {Mantelet},
+  {Marchal}, {Marchant}, {Marconi}, {Marie}, {Marinoni}, {Marrese},
+  {Marschalk{\'o}}, {Marshall}, {Mart{\'\i}n-Fleitas}, {Martino}, {Mary},
+  {Matijevi{\v{c}}}, {Mazeh}, {McMillan}, {Messina}, {Mestre}, {Michalik},
+  {Millar}, {Miranda}, {Molina}, {Molinaro}, {Molinaro}, {Moln{\'a}r},
+  {Moniez}, {Montegriffo}, {Monteiro}, {Mor}, {Mora}, {Morbidelli}, {Morel},
+  {Morgenthaler}, {Morley}, {Morris}, {Mulone}, {Muraveva}, {Musella},
+  {Narbonne}, {Nelemans}, {Nicastro}, {Noval}, {Ord{\'e}novic},
+  {Ordieres-Mer{\'e}}, {Osborne}, {Pagani}, {Pagano}, {Pailler}, {Palacin},
+  {Palaversa}, {Parsons}, {Paulsen}, {Pecoraro}, {Pedrosa}, {Pentik{\"a}inen},
+  {Pereira}, {Pichon}, {Piersimoni}, {Pineau}, {Plachy}, {Plum}, {Poujoulet},
+  {Pr{\v{s}}a}, {Pulone}, {Ragaini}, {Rago}, {Rambaux}, {Ramos-Lerate},
+  {Ranalli}, {Rauw}, {Read}, {Regibo}, {Renk}, {Reyl{\'e}}, {Ribeiro},
+  {Rimoldini}, {Ripepi}, {Riva}, {Rixon}, {Roelens}, {Romero-G{\'o}mez},
+  {Rowell}, {Royer}, {Rudolph}, {Ruiz-Dern}, {Sadowski}, {Sagrist{\`a}
+  Sell{\'e}s}, {Sahlmann}, {Salgado}, {Salguero}, {Sarasso}, {Savietto},
+  {Schnorhk}, {Schultheis}, {Sciacca}, {Segol}, {Segovia}, {Segransan},
+  {Serpell}, {Shih}, {Smareglia}, {Smart}, {Smith}, {Solano}, {Solitro},
+  {Sordo}, {Soria Nieto}, {Souchay}, {Spagna}, {Spoto}, {Stampa}, {Steele},
+  {Steidelm{\"u}ller}, {Stephenson}, {Stoev}, {Suess}, {S{\"u}veges}, {Surdej},
+  {Szabados}, {Szegedi-Elek}, {Tapiador}, {Taris}, {Tauran}, {Taylor},
+  {Teixeira}, {Terrett}, {Tingley}, {Trager}, {Turon}, {Ulla}, {Utrilla},
+  {Valentini}, {van Elteren}, {Van Hemelryck}, {van Leeuwen}, {Varadi},
+  {Vecchiato}, {Veljanoski}, {Via}, {Vicente}, {Vogt}, {Voss}, {Votruba},
+  {Voutsinas}, {Walmsley}, {Weiler}, {Weingrill}, {Werner}, {Wevers},
+  {Whitehead}, {Wyrzykowski}, {Yoldas}, {{\v{Z}}erjal}, {Zucker}, {Zurbach},
+  {Zwitter}, {Alecu}, {Allen}, {Allende Prieto}, {Amorim},
+  {Anglada-Escud{\'e}}, {Arsenijevic}, {Azaz}, {Balm}, {Beck}, {Bernstein},
+  {Bigot}, {Bijaoui}, {Blasco}, {Bonfigli}, {Bono}, {Boudreault}, {Bressan},
+  {Brown}, {Brunet}, {Bunclark}, {Buonanno}, {Butkevich}, {Carret}, {Carrion},
+  {Chemin}, {Ch{\'e}reau}, {Corcione}, {Darmigny}, {de Boer}, {de Teodoro}, {de
+  Zeeuw}, {Delle Luche}, {Domingues}, {Dubath}, {Fodor}, {Fr{\'e}zouls},
+  {Fries}, {Fustes}, {Fyfe}, {Gallardo}, {Gallegos}, {Gardiol}, {Gebran},
+  {Gomboc}, {G{\'o}mez}, {Grux}, {Gueguen}, {Heyrovsky}, {Hoar}, {Iannicola},
+  {Isasi Parache}, {Janotto}, {Joliet}, {Jonckheere}, {Keil}, {Kim},
+  {Klagyivik}, {Klar}, {Knude}, {Kochukhov}, {Kolka}, {Kos}, {Kutka}, {Lainey},
+  {LeBouquin}, {Liu}, {Loreggia}, {Makarov}, {Marseille}, {Martayan},
+  {Martinez-Rubi}, {Massart}, {Meynadier}, {Mignot}, {Munari}, {Nguyen},
+  {Nordlander}, {Ocvirk}, {O'Flaherty}, {Olias Sanz}, {Ortiz}, {Osorio},
+  {Oszkiewicz}, {Ouzounis}, {Palmer}, {Park}, {Pasquato}, {Peltzer}, {Peralta},
+  {P{\'e}turaud}, {Pieniluoma}, {Pigozzi}, {Poels}, {Prat}, {Prod'homme},
+  {Raison}, {Rebordao}, {Risquez}, {Rocca-Volmerange}, {Rosen}, {Ruiz-Fuertes},
+  {Russo}, {Sembay}, {Serraller Vizcaino}, {Short}, {Siebert}, {Silva},
+  {Sinachopoulos}, {Slezak}, {Soffel}, {Sosnowska}, {Strai{\v{z}}ys}, {ter
+  Linden}, {Terrell}, {Theil}, {Tiede}, {Troisi}, {Tsalmantza}, {Tur},
+  {Vaccari}, {Vachier}, {Valles}, {Van Hamme}, {Veltz}, {Virtanen}, {Wallut},
+  {Wichmann}, {Wilkinson}, {Ziaeepour}, \& {Zschocke}}]{Gaia}
+{Gaia Collaboration}, {Prusti}, T., {de Bruijne}, J.~H.~J., {et~al.} 2016,
+  \aap, 595, A1, \dodoi{10.1051/0004-6361/201629272}
+
+\bibitem[{{Gaia Collaboration} {et~al.}(2018){Gaia Collaboration}, {Brown},
+  {Vallenari}, {Prusti}, {de Bruijne}, {Babusiaux}, {Bailer-Jones}, {Biermann},
+  {Evans}, {Eyer}, {Jansen}, {Jordi}, {Klioner}, {Lammers}, {Lindegren},
+  {Luri}, {Mignard}, {Panem}, {Pourbaix}, {Randich}, {Sartoretti}, {Siddiqui},
+  {Soubiran}, {van Leeuwen}, {Walton}, {Arenou}, {Bastian}, {Cropper},
+  {Drimmel}, {Katz}, {Lattanzi}, {Bakker}, {Cacciari}, {Casta{\~n}eda},
+  {Chaoul}, {Cheek}, {De Angeli}, {Fabricius}, {Guerra}, {Holl}, {Masana},
+  {Messineo}, {Mowlavi}, {Nienartowicz}, {Panuzzo}, {Portell}, {Riello},
+  {Seabroke}, {Tanga}, {Th{\'e}venin}, {Gracia-Abril}, {Comoretto},
+  {Garcia-Reinaldos}, {Teyssier}, {Altmann}, {Andrae}, {Audard},
+  {Bellas-Velidis}, {Benson}, {Berthier}, {Blomme}, {Burgess}, {Busso},
+  {Carry}, {Cellino}, {Clementini}, {Clotet}, {Creevey}, {Davidson}, {De
+  Ridder}, {Delchambre}, {Dell'Oro}, {Ducourant}, {Fern{\'a}ndez-
+  Hern{\'a}ndez}, {Fouesneau}, {Fr{\'e}mat}, {Galluccio}, {Garc{\'\i}a-Torres},
+  {Gonz{\'a}lez-N{\'u}{\~n}ez}, {Gonz{\'a}lez-Vidal}, {Gosset}, {Guy},
+  {Halbwachs}, {Hambly}, {Harrison}, {Hern{\'a}ndez}, {Hestroffer}, {Hodgkin},
+  {Hutton}, {Jasniewicz}, {Jean-Antoine-Piccolo}, {Jordan}, {Korn},
+  {Krone-Martins}, {Lanzafame}, {Lebzelter}, {L{\"o}ffler}, {Manteiga},
+  {Marrese}, {Mart{\'\i}n-Fleitas}, {Moitinho}, {Mora}, {Muinonen}, {Osinde},
+  {Pancino}, {Pauwels}, {Petit}, {Recio-Blanco}, {Richards}, {Rimoldini},
+  {Robin}, {Sarro}, {Siopis}, {Smith}, {Sozzetti}, {S{\"u}veges}, {Torra}, {van
+  Reeven}, {Abbas}, {Abreu Aramburu}, {Accart}, {Aerts}, {Altavilla},
+  {{\'A}lvarez}, {Alvarez}, {Alves}, {Anderson}, {Andrei}, {Anglada Varela},
+  {Antiche}, {Antoja}, {Arcay}, {Astraatmadja}, {Bach}, {Baker},
+  {Balaguer-N{\'u}{\~n}ez}, {Balm}, {Barache}, {Barata}, {Barbato}, {Barblan},
+  {Barklem}, {Barrado}, {Barros}, {Barstow}, {Bartholom{\'e} Mu{\~n}oz},
+  {Bassilana}, {Becciani}, {Bellazzini}, {Berihuete}, {Bertone}, {Bianchi},
+  {Bienaym{\'e}}, {Blanco-Cuaresma}, {Boch}, {Boeche}, {Bombrun}, {Borrachero},
+  {Bossini}, {Bouquillon}, {Bourda}, {Bragaglia}, {Bramante}, {Breddels},
+  {Bressan}, {Brouillet}, {Br{\"u}semeister}, {Brugaletta}, {Bucciarelli},
+  {Burlacu}, {Busonero}, {Butkevich}, {Buzzi}, {Caffau}, {Cancelliere},
+  {Cannizzaro}, {Cantat-Gaudin}, {Carballo}, {Carlucci}, {Carrasco},
+  {Casamiquela}, {Castellani}, {Castro-Ginard}, {Charlot}, {Chemin},
+  {Chiavassa}, {Cocozza}, {Costigan}, {Cowell}, {Crifo}, {Crosta}, {Crowley},
+  {Cuypers}, {Dafonte}, {Damerdji}, {Dapergolas}, {David}, {David}, {de
+  Laverny}, {De Luise}, {De March}, {de Martino}, {de Souza}, {de Torres},
+  {Debosscher}, {del Pozo}, {Delbo}, {Delgado}, {Delgado}, {Di Matteo},
+  {Diakite}, {Diener}, {Distefano}, {Dolding}, {Drazinos}, {Dur{\'a}n},
+  {Edvardsson}, {Enke}, {Eriksson}, {Esquej}, {Eynard Bontemps}, {Fabre},
+  {Fabrizio}, {Faigler}, {Falc{\~a}o}, {Farr{\`a}s Casas}, {Federici},
+  {Fedorets}, {Fernique}, {Figueras}, {Filippi}, {Findeisen}, {Fonti},
+  {Fraile}, {Fraser}, {Fr{\'e}zouls}, {Gai}, {Galleti}, {Garabato},
+  {Garc{\'\i}a-Sedano}, {Garofalo}, {Garralda}, {Gavel}, {Gavras}, {Gerssen},
+  {Geyer}, {Giacobbe}, {Gilmore}, {Girona}, {Giuffrida}, {Glass}, {Gomes},
+  {Granvik}, {Gueguen}, {Guerrier}, {Guiraud}, {Guti{\'e}rrez-S{\'a}nchez},
+  {Haigron}, {Hatzidimitriou}, {Hauser}, {Haywood}, {Heiter}, {Helmi}, {Heu},
+  {Hilger}, {Hobbs}, {Hofmann}, {Holland}, {Huckle}, {Hypki}, {Icardi},
+  {Jan{\ss}en}, {Jevardat de Fombelle}, {Jonker}, {Juh{\'a}sz}, {Julbe},
+  {Karampelas}, {Kewley}, {Klar}, {Kochoska}, {Kohley}, {Kolenberg},
+  {Kontizas}, {Kontizas}, {Koposov}, {Kordopatis}, {Kostrzewa-Rutkowska},
+  {Koubsky}, {Lambert}, {Lanza}, {Lasne}, {Lavigne}, {Le Fustec}, {Le
+  Poncin-Lafitte}, {Lebreton}, {Leccia}, {Leclerc}, {Lecoeur-Taibi},
+  {Lenhardt}, {Leroux}, {Liao}, {Licata}, {Lindstr{\o}m}, {Lister}, {Livanou},
+  {Lobel}, {L{\'o}pez}, {Managau}, {Mann}, {Mantelet}, {Marchal}, {Marchant},
+  {Marconi}, {Marinoni}, {Marschalk{\'o}}, {Marshall}, {Martino}, {Marton},
+  {Mary}, {Massari}, {Matijevi{\v{c}}}, {Mazeh}, {McMillan}, {Messina},
+  {Michalik}, {Millar}, {Molina}, {Molinaro}, {Moln{\'a}r}, {Montegriffo},
+  {Mor}, {Morbidelli}, {Morel}, {Morris}, {Mulone}, {Muraveva}, {Musella},
+  {Nelemans}, {Nicastro}, {Noval}, {O'Mullane}, {Ord{\'e}novic},
+  {Ord{\'o}{\~n}ez-Blanco}, {Osborne}, {Pagani}, {Pagano}, {Pailler},
+  {Palacin}, {Palaversa}, {Panahi}, {Pawlak}, {Piersimoni}, {Pineau}, {Plachy},
+  {Plum}, {Poggio}, {Poujoulet}, {Pr{\v{s}}a}, {Pulone}, {Racero}, {Ragaini},
+  {Rambaux}, {Ramos-Lerate}, {Regibo}, {Reyl{\'e}}, {Riclet}, {Ripepi}, {Riva},
+  {Rivard}, {Rixon}, {Roegiers}, {Roelens}, {Romero-G{\'o}mez}, {Rowell},
+  {Royer}, {Ruiz-Dern}, {Sadowski}, {Sagrist{\`a} Sell{\'e}s}, {Sahlmann},
+  {Salgado}, {Salguero}, {Sanna}, {Santana- Ros}, {Sarasso}, {Savietto},
+  {Schultheis}, {Sciacca}, {Segol}, {Segovia}, {S{\'e}gransan}, {Shih},
+  {Siltala}, {Silva}, {Smart}, {Smith}, {Solano}, {Solitro}, {Sordo}, {Soria
+  Nieto}, {Souchay}, {Spagna}, {Spoto}, {Stampa}, {Steele},
+  {Steidelm{\"u}ller}, {Stephenson}, {Stoev}, {Suess}, {Surdej}, {Szabados},
+  {Szegedi-Elek}, {Tapiador}, {Taris}, {Tauran}, {Taylor}, {Teixeira},
+  {Terrett}, {Teyssandier}, {Thuillot}, {Titarenko}, {Torra Clotet}, {Turon},
+  {Ulla}, {Utrilla}, {Uzzi}, {Vaillant}, {Valentini}, {Valette}, {van Elteren},
+  {Van Hemelryck}, {van Leeuwen}, {Vaschetto}, {Vecchiato}, {Veljanoski},
+  {Viala}, {Vicente}, {Vogt}, {von Essen}, {Voss}, {Votruba}, {Voutsinas},
+  {Walmsley}, {Weiler}, {Wertz}, {Wevers}, {Wyrzykowski}, {Yoldas},
+  {{\v{Z}}erjal}, {Ziaeepour}, {Zorec}, {Zschocke}, {Zucker}, {Zurbach}, \&
+  {Zwitter}}]{GaiaDR2}
+{Gaia Collaboration}, {Brown}, A.~G.~A., {Vallenari}, A., {et~al.} 2018, \aap,
+  616, A1, \dodoi{10.1051/0004-6361/201833051}
+
+\bibitem[{{Heller} {et~al.}(2014){Heller}, {Williams}, {Kipping}, {Limbach},
+  {Turner}, {Greenberg}, {Sasaki}, {Bolmont}, {Grasset}, {Lewis}, {Barnes}, \&
+  {Zuluaga}}]{heller14}
+{Heller}, R., {Williams}, D., {Kipping}, D., {et~al.} 2014, Astrobiology, 14,
+  798, \dodoi{10.1089/ast.2014.1147}
+
+\bibitem[{{Hippke}(2015)}]{hippke15}
+{Hippke}, M. 2015, \apj, 806, 51, \dodoi{10.1088/0004-637X/806/1/51}
+
+\bibitem[{{Horne}(1986)}]{horne86}
+{Horne}, K. 1986, \pasp, 98, 609, \dodoi{10.1086/131801}
+
+\bibitem[{Kass \& Raftery(1995)}]{kass95}
+Kass, R.~E., \& Raftery, A.~E. 1995, Journal of the American Statistical
+  Association, 90, 773, \dodoi{10.1080/01621459.1995.10476572}
+
+\bibitem[{{Kipping}(2009{\natexlab{a}})}]{kipping09a}
+{Kipping}, D.~M. 2009{\natexlab{a}}, \mnras, 392, 181,
+  \dodoi{10.1111/j.1365-2966.2008.13999.x}
+
+\bibitem[{{Kipping}(2009{\natexlab{b}})}]{kipping09b}
+---. 2009{\natexlab{b}}, \mnras, 396, 1797,
+  \dodoi{10.1111/j.1365-2966.2009.14869.x}
+
+\bibitem[{{Kipping} {et~al.}(2013){Kipping}, {Hartman}, {Buchhave}, {Schmitt},
+  {Bakos}, \& {Nesvorn{\'y}}}]{kipping13}
+{Kipping}, D.~M., {Hartman}, J., {Buchhave}, L.~A., {et~al.} 2013, \apj, 770,
+  101, \dodoi{10.1088/0004-637X/770/2/101}
+
+\bibitem[{{Knutson} {et~al.}(2014){Knutson}, {Dragomir}, {Kreidberg},
+  {Kempton}, {McCullough}, {Fortney}, {Bean}, {Gillon}, {Homeier}, \&
+  {Howard}}]{knutson14b}
+{Knutson}, H.~A., {Dragomir}, D., {Kreidberg}, L., {et~al.} 2014, \apj, 794,
+  155, \dodoi{10.1088/0004-637X/794/2/155}
+
+\bibitem[{{Kreidberg} {et~al.}(2014){Kreidberg}, {Bean}, {D{\'e}sert},
+  {Benneke}, {Deming}, {Stevenson}, {Seager}, {Berta-Thompson}, {Seifahrt}, \&
+  {Homeier}}]{kreidberg14a}
+{Kreidberg}, L., {Bean}, J.~L., {D{\'e}sert}, J.-M., {et~al.} 2014, \nat, 505,
+  69, \dodoi{10.1038/nature12888}
+
+\bibitem[{{Luger} {et~al.}(2017){Luger}, {Lustig-Yaeger}, \& {Agol}}]{luger17}
+{Luger}, R., {Lustig-Yaeger}, J., \& {Agol}, E. 2017, \apj, 851, 94,
+  \dodoi{10.3847/1538-4357/aa9c43}
+
+\bibitem[{{Morton}(2015)}]{isochrone}
+{Morton}, T.~D. 2015, {isochrones: Stellar model grid package}, Astrophysics
+  Source Code Library.
+\newblock \doeprint{1503.010}
+
+\bibitem[{{Noyola} {et~al.}(2014){Noyola}, {Satyal}, \& {Musielak}}]{noyola14}
+{Noyola}, J.~P., {Satyal}, S., \& {Musielak}, Z.~E. 2014, \apj, 791, 25,
+  \dodoi{10.1088/0004-637X/791/1/25}
+
+\bibitem[{{Peters} \& {Turner}(2013)}]{peters13}
+{Peters}, M.~A., \& {Turner}, E.~L. 2013, \apj, 769, 98,
+  \dodoi{10.1088/0004-637X/769/2/98}
+
+\bibitem[{{Rein} \& {Liu}(2012)}]{rein12}
+{Rein}, H., \& {Liu}, S.-F. 2012, \aap, 537, A128,
+  \dodoi{10.1051/0004-6361/201118085}
+
+\bibitem[{{Sengupta} \& {Marley}(2016)}]{sengupta16}
+{Sengupta}, S., \& {Marley}, M.~S. 2016, \apj, 824, 76,
+  \dodoi{10.3847/0004-637X/824/2/76}
+
+\bibitem[{{Simon} {et~al.}(2010){Simon}, {Szab{\'o}}, {Szatm{\'a}ry}, \&
+  {Kiss}}]{simon10}
+{Simon}, A.~E., {Szab{\'o}}, G.~M., {Szatm{\'a}ry}, K., \& {Kiss}, L.~L. 2010,
+  \mnras, 406, 2038, \dodoi{10.1111/j.1365-2966.2010.16818.x}
+
+\bibitem[{{Skrutskie} {et~al.}(2006){Skrutskie}, {Cutri}, {Stiening},
+  {Weinberg}, {Schneider}, {Carpenter}, {Beichman}, {Capps}, {Chester},
+  {Elias}, {Huchra}, {Liebert}, {Lonsdale}, {Monet}, {Price}, {Seitzer},
+  {Jarrett}, {Kirkpatrick}, {Gizis}, {Howard}, {Evans}, {Fowler}, {Fullmer},
+  {Hurt}, {Light}, {Kopan}, {Marsh}, {McCallon}, {Tam}, {Van Dyk}, \&
+  {Wheelock}}]{2MASS}
+{Skrutskie}, M.~F., {Cutri}, R.~M., {Stiening}, R., {et~al.} 2006, \aj, 131,
+  1163, \dodoi{10.1086/498708}
+
+\bibitem[{{Spake} {et~al.}(2018){Spake}, {Sing}, {Evans}, {Oklop{\v c}i{\'c}},
+  {Bourrier}, {Kreidberg}, {Rackham}, {Irwin}, {Ehrenreich}, {Wyttenbach},
+  {Wakeford}, {Zhou}, {Chubb}, {Nikolov}, {Goyal}, {Henry}, {Williamson},
+  {Blumenthal}, {Anderson}, {Hellier}, {Charbonneau}, {Udry}, \&
+  {Madhusudhan}}]{spake18}
+{Spake}, J.~J., {Sing}, D.~K., {Evans}, T.~M., {et~al.} 2018, \nat, 557, 68,
+  \dodoi{10.1038/s41586-018-0067-5}
+
+\bibitem[{{Teachey} \& {Kipping}(2018)}]{teachey18b}
+{Teachey}, A., \& {Kipping}, D.~M. 2018, Science Advances, 4, eaav1784,
+  \dodoi{10.1126/sciadv.aav1784}
+
+\bibitem[{{Teachey} {et~al.}(2018){Teachey}, {Kipping}, \&
+  {Schmitt}}]{teachey18a}
+{Teachey}, A., {Kipping}, D.~M., \& {Schmitt}, A.~R. 2018, \aj, 155, 36,
+  \dodoi{10.3847/1538-3881/aa93f2}
+
+\bibitem[{Van Der~Walt {et~al.}(2011)Van Der~Walt, Colbert, \&
+  Varoquaux}]{van2011numpy}
+Van Der~Walt, S., Colbert, S.~C., \& Varoquaux, G. 2011, Computing in Science
+  \& Engineering, 13, 22
+
+\bibitem[{{Vanderburg} {et~al.}(2018){Vanderburg}, {Rappaport}, \&
+  {Mayo}}]{vanderburg18}
+{Vanderburg}, A., {Rappaport}, S.~A., \& {Mayo}, A.~W. 2018, \aj, 156, 184,
+  \dodoi{10.3847/1538-3881/aae0fc}
+
+\bibitem[{{Zhou} {et~al.}(2017){Zhou}, {Apai}, {Lew}, \& {Schneider}}]{zhou17}
+{Zhou}, Y., {Apai}, D., {Lew}, B.~W.~P., \& {Schneider}, G. 2017, \aj, 153,
+  243, \dodoi{10.3847/1538-3881/aa6481}
+
+\end{thebibliography}
 

### 2019-01-23 ms.tex
bbl

@@
 
-\section{Conclusion}
+\section{Discussion}
+As discussed above, we do not recover the moon. Our analysis was designed to be independent, and as such makes different choices about the data reduction and the choice of sytematics model.
+
+We explored several avenues to determine what caused the difference in our results. We first checked whether the detrending model was responsible.
+
+We also compared the data directly (see Figure\,\ref{fig:raw}). The data is different!
+rotate the image, aperture choice, measurement of the background, outlier masking,
+
 In this work, we presented an independent analysis of HST observations of the Kepler-1625 system.
 In contrast to previous analysis by \citep{teachey18b}, we do not find evidence for the transit of a moon.
-
-what is 
-approach to data reduction was very similar, but of the data reduction, and
+We obtain a better fit to the data without including a moon in the model.
+We
 

### 2019-01-23 ms.tex
blah

@@
 In addition, the moon transit time is not well-constrained by the data.
-As shown in the posterior distribution in Figure~\ref{fig:corner}, the $2\,\sigma$ confidence interval for the moon's transit includes the entire visit.
+As shown in the posterior distribution in Figure~\ref{fig:corner}, the $2\,\sigma$ confidence interval for the moon's transit includes the entire duration of the observations.
 The upper limit on the moon radius is $3.2\,R_\oplus$ at $2\sigma$ confidence and $4.0\,R_\oplus$ at $3\sigma$.
@@
 
-Overall, we find that the TK18 fits have a larger rms than the fits to our new data reduction.
-The no-moon model has an rms of 381.5 ppm (compared to 362.2 for our data).
-As TK18 found, the moon model improves the rms to 363.4 ppm ($\Delta\chi^2 = 22.0$); however, even with the additional four free parameters, the moon model does not perform as well as the no-moon model fit to our data.
-This difference in fit quality corresponds to $\Delta\mathrm{BIC} = 23.9$, which is strong evidence against the moon.
+%Similar to the finding of TK18, the moon model improves the fit quality by a $\Delta\chi^2 = 22.0$.
+However, even with the moon included, the model does not perform better than our no-moon fit (rms = 363 versus 362 ppm).
+This differenc
+
+%Overall, we find that the TK18 fits have a larger rms than the fits to our new data reduction. The no-moon model has an rms of 381.5 ppm (compared to 362.2 for our data).
+
+Similar to the finding of TK18, the moon model improves the fit quality by a $\Delta\chi^2 = 22.0$; however, even with the additional four free parameters, the moon model does not perform better than the no-moon model fit to our data (rms of 363 versus 362 ppm).
+This difference in fit quality --- equivalent rms to within 1 ppm, but four additional parameters --- corresponds to $\Delta\mathrm{BIC} = 23.9$, which is strong evidence against the moon.
 %Even when a moon is included, the fit is still slightly worse (rms of 363.4 ppm) than our best no-moon model, in spite of four additional free parameters.

### 2019-01-23 figures/fig2_rms.py

@@ -51,9 +51,9 @@ def computeStdErr(datastd, datasize, binsz):
 
 
 
-plt.figure(figsize = (4,3))
+plt.figure(figsize = (4,3.5))
 
-chi2red = 1.33   #best fit chi2 (need to scale for photon noise)
+chi2red = 1.05   #best fit chi2 (need to scale for photon noise)
 
 d = np.genfromtxt("kreidberg_nomoon_resid.txt")
 ind = np.argsort(d[:,0])
@@ -64,10 +64,19 @@ normfactor = stderr[0]
 #normfactor = m.rms_predicted
 plt.loglog(binsz, stderr/normfactor, color='black', ls='-', label='Expected  rms', zorder = -1) # expected noise
 #print(stderr/normfactor)
-plt.loglog(binsz, rms/normfactor*np.sqrt(chi2red), color='blue', label='This work')    # our noise
+plt.loglog(binsz, rms/normfactor*np.sqrt(chi2red), zorder = 10, color='blue', label='This work, no-moon')    # our noise
 
 print("excess over photon, LK:", binsz) 
 print("excess over photon, LK:", rms*np.sqrt(chi2red)/stderr)
+
+d = np.genfromtxt("kreidberg_moon_resid.txt")                                 
+ind = np.argsort(d[:,0])                                                        
+d = d[ind]                                                                      
+resid = d[:,1]                                                                  
+rms, stderr, binsz, rmserr = computeRMS(resid, maxnbins = None, binstep = 1, isrmserr = True)
+normfactor = stderr[0]                                                          
+plt.loglog(binsz, rms/normfactor*np.sqrt(chi2red), color='blue', linestyle = 'dashed', label='This work, moon')    # our noise
+
 
 d = np.genfromtxt("teachey_nomoon_resid.txt")
 ind = np.argsort(d[:,0])
@@ -75,13 +84,20 @@ d = d[ind]
 resid = d[:,1]
 rms, stderr, binsz, rmserr = computeRMS(resid, maxnbins = None, binstep = 1, isrmserr = True)
 #normfactor = m.rms_predicted
-plt.loglog(binsz, rms/normfactor*np.sqrt(chi2red), color='red',  label='TK18')    # our noise
[…]

### 2019-01-23 ms.tex
discussion

--- 2019-01-23 ms.tex
@@
 \begin{abstract}
-    Observations of the Kepler-1625 system with the Kepler and Hubble Space Telescopes have suggested the presence of a candidate exomoon, a Neptune-radius satellite orbiting a long-period Jovian planet.
+    Observations of the Kepler-1625 system with the Kepler and Hubble Space Telescopes have suggested the presence of a candidate exomoon, Kepler-1625b-i, a Neptune-radius satellite orbiting a long-period Jovian planet.
 Here we present a new analysis of the Hubble observations from an independent data reduction pipeline.
-We find that the transit light curve is well fit with a planet-only model, and that the addition of a moon does not significantly improve the fit quality.
-The $3\,\sigma$ upper limit on the moon radius is $4.0R_\oplus$.
-FIXME: why are we different from TK18?
-We conclude that FIXME, and future follow-up efforts for exomoons should focus on alternative targets.
+We find that the transit light curve is well fit with a planet-only model, with a best-fit $\chi^2_\nu$ equal to $1.01$.
+The addition of a moon does not significantly improve the fit quality.
+We compare our results directly with \cite{teachey18b}, and find that we obtain a better fit to the light curve using a model with fewer free parameters (no moon).
+We discuss possible sources for the discrepancy in our results, and conclude that there is no single explanation for the difference but rather that it is the sum of many small choices.
+We conclude that future follow-up efforts for exomoons should focus on alternate targets.
+
 \end{abstract}
@@
 We varied the height and width of the box in 1-pixel increments to find the window that minimized the root-mean-square (rms) deviation from the best fit to the transit light curve.
-The best was $445  < \mathrm{X} < 569$, and $517 < \mathrm{Y} < 531$, where X and Y are physical pixels in the spectral and spatial direction, respectively.
+The best was $450  < \mathrm{X} < 574$, and $522 < \mathrm{Y} < 536$, where X and Y are physical pixels in the spectral and spatial direction, respectively.
 
@@
 For the error array, we used a quadrature sum of the photon noise (the square root of the pixel counts), the read noise (12 photoelectrons for \texttt{flt} files; WFC3 Data Handbook\footnote{\url{http://www.stsci.edu/hst/wfc3/documents/handbooks/currentDHB/}}), and the error due to background subtraction (described in \ref{sec:background}).
-The initial bad pixel mask included pixels marked with the data quality flag 4 or 512 (dead pixels or blobs).
+The initial pixel mask marked all pixels as good.
 
@@
 This procedure masks any cosmic rays or bad pixels that were missed by the initial \texttt{flt} calibration.
-We tested a range of thresholds ($4 < \sigma_\mathrm{cut} < 15$) and found that different $\sigma_\mathrm{cut}$ choices did not significantly change the final transit light curve.
-The data reported in this work use $\sigma_\mathrm{cut} = 15$.
+We tested a range of thresholds ($7.5 < \sigma_\mathrm{cut} < 15$) and found that different $\sigma_\mathrm{cut}$ choices did not significantly change the final transit light curve.
+The data reported in this work use $\sigma_\mathrm{cut} = 7.5$.
 To create the broadband transit light curve, we sum each spectrum over all wavelengths.
@@
 Moreover, the host star is in a crowded field, so the pixels used to estimate the background must be chosen carefully to avoid contamination from other stars.
-To estimate the background counts, we masked pixels with total counts larger than 800 electrons and took the median count in the unmasked pixels.
+To estimate the background counts, we masked pixels with total counts larger than 800 electrons (2.7 electrons/sec) and took the median count in the unmasked pixels.
 The per pixel uncertainty due to background subtraction is 1.4826 times the median absolute deviation.
@@
 We obtained an excellent fit to the light curve with the no-moon model, as illustrated in  Figure\,\ref{fig:bestfit}.
-The residuals to our no-moon model fit have rms equal to 362.2 parts per million (ppm), which is within 2\% of the predicted photon shot noise (367 ppm), and yields a $\chi_\nu^2 = 1.05$.
+The residuals to the no-moon model fit have rms equal to 356 parts per million (ppm), which is within 3\% of the predicted photon shot noise (367 ppm), and yields a $\chi_\nu^2 = 1.01$.
 The binned rms decreases with the square root of the number of points per bin, as expected for photon noise-limited statistics (see rms versus bin size in Figure~\ref{fig:rms}).
@@
 \includegraphics[width = 0.5 \textwidth]{figures/fig2_rms.pdf}
-    \caption{Light curve rms versus bin size for the best fit no-moon model.
-The fit to data from this work (blue line) agrees well with the expected photon-limited, $\sqrt{N}$ decrease in rms with bin size (black line).
-The TK18 rms (red line) ranges from $1.3 - 2\times$ the photon limit for bin sizes of 1 to 20 data points.
-The increase in relative rms for larger bin sizes indicates that time-correlated noise is present in the TK18 data.}
+    \caption{Light curve rms versus bin size for the best fit no-moon model (solid lines) and moon model (dashed lines), for data from this work (red) and TK18 (blue).
+The fits to data from this work agree well with the expected photon-limited, $\sqrt{N}$ decrease in rms with bin size (black line).
+We also reach the photon limit for the TK18 data, but only for the moon model.
+The rms for the no-moon fit (red dashed line) ranges from $1.1 - 1.5\times$ the photon limit for 1 to 20 points per bin.}
  \label{fig:rms}
@@
 
-We also obtained a good fit with the moon model; however, the addition of three more free parameters does not significantly improve the fit quality.
-The best fit moon model has a radius $r_\mathrm{moon} = 2.4R_\oplus$, a mid-transit time $t_\mathrm{moon} = 2458055.2869\,\mathrm{BJD_{TDB}}$, and a period $P_m = 26.5$ days.
-This fit has a slightly lower rms than the no-moon model (359.5 ppm versus 362.2 ppm), but the $\chi_\nu^2$ is unchanged (also $1.05$).
-According to the Bayesian information criterion (BIC), which penalizes unnecessary model complexity, the moon model is disfavored with $\Delta\mathrm{BIC} = 13$.
+We obtained a slightly better fit with the moon model (rms = 351 ppm; $\chi_\nu^2 = 0.998$); however, this is not a large enough improvement in fit quality to merit the addition of three additional free parameters.
+According to the Bayesian information criterion (BIC), which penalizes unnecessary model complexity, the moon model is disfavored with $\Delta\mathrm{BIC} = 10.7$.
 This constitutes strong evidence against the inclusion of a moon \citep{kass95}.
 In addition, the moon transit time is not well-constrained by the data.
-As shown in the posterior distribution in Figure~\ref{fig:corner}, the $2\,\sigma$ confidence interval for the moon's transit includes the entire visit.
+As shown in the posterior distribution in Figure~\ref{fig:corner}, the $2\,\sigma$ confidence interval for the moon's transit includes the entire duration of the observations.
 The upper limit on the moon radius is $3.2\,R_\oplus$ at $2\sigma$ confidence and $4.0\,R_\oplus$ at $3\sigma$.
+
+%The best fit moon model has a radius $r_\mathrm{moon} = 2.4R_\oplus$, a mid-transit time $t_\mathrm{moon} = 2458055.2869\,\mathrm{BJD_{TDB}}$, and a period $P_m = 26.5$ days.
+This fit has a slightly lower rms than the no-moon model (359.5 ppm versus 362.2 ppm), but
 
@@
 We therefore opted to use a TK18 systematics model to enable a fair comparison between our results.
-We used a second-order polynomial trend in time, a constant offset after orbit 14 (where the guide stars are reacquired), and the non-parameteric orbit-long ramp model.
+We obtained the best fit using a second-order polynomial trend in time, a constant offset after orbit 14 (where the guide stars are reacquired), and the non-parameteric orbit-long ramp model.
 This model has one more free parameter than the systematics model given in Equation~\ref{eq:sys}.
@@
 
-Overall, we find that the TK18 fits have a larger rms than the fits to our new data reduction.
-The no-moon model has an rms of 381.5 ppm (compared to 362.2 for our data).
-As TK18 found, the moon model improves the rms to 363.4 ppm ($\Delta\chi^2 = 22.0$); however, even with the additional four free parameters, the moon model does not perform as well as the no-moon model fit to our data.
-This difference in fit quality corresponds to $\Delta\mathrm{BIC} = 23.9$, which is strong evidence against the moon.
-%Even when a moon is included, the fit is still slightly worse (rms of 363.4 ppm) than our best no-moon model, in spite of four additional free parameters.
+Similar to the findings of TK18, the moon model improved the fit quality by a $\Delta\chi^2 = 22.0$.
+Notably, however, the moon model fit to the TK18 data does not perform better than the no-moon model fit to our new data (rms of 363 versus 356 ppm), even with the additional four free parameters.
+This difference in fit quality corresponds to $\Delta\mathrm{BIC} = 31.2$, which is strong evidence against the moon.
 
 The moon model also yields qualitatively different posterior distributions for the two data sets.
-For the TK18 data, the moon radius and transit time are peaked at $r_\mathrm{moon} = 4.0^{+0.8}_{-0.6}\,R_\oplus$ ($>2.1\,R_\oplus$ at $3\sigma$ confidence), and $t_\mathrm{moon} =  2458056.29^{+0.06}_{-0.04}\,\mathrm{BJD_{TDB}}$ (as shown in Figure\,\ref{fig:corner}).
-By contrast, the fit to the new data only yields an upper limit on the moon radius of ($4.0\,R_\oplus$ at $3\sigma$ confidence), and the transit time is unconstrained.
-
-%Our results are consistent with those originally published in TK18, including the large improvement in $\chi^2$ when the moon is included ($\Delta\chi^2 = 22.0$). The posterior distribution for
-
-%We obtain a better fit (a lower $\chi^2$) with the no-moon model fit to our data than we obtain with the moon model fit to the TK18 data, even though it has four additional free parameters.
+As shown in Figure\,\ref{fig:corner}, for the TK18 data the moon radius and transit time are peaked at $r_\mathrm{moon} = 4.0^{+0.8}_{-0.6}\,R_\oplus$  and $t_\mathrm{moon} =  2458056.29^{+0.06}_{-0.04}\,\mathrm{BJD_{TDB}}$.
+By contrast, the fit to the new data presented here yields an upper limit on the moon radius of ($4.0\,R_\oplus$ at $3\sigma$ confidence), and the transit time is unconstrained.
 
@@
     \caption{Posterior distributions for the moon radius and time of transit based on an MCMC fit to data from this work (blue) and from TK18 (red).
-The shading corresponds to $1-$, $2-$, and $3\sigma$ contours (darkest to lightest).
-These values are marginalized over all other model parameters.
-The diagonal shows the normalized posterior probability density.}
+The shading corresponds to $1-$, $2-$, and $3\,\sigma$ contours (from darkest to lightest).
+These values are marginalized over all other model parameters.}
 \label{fig:corner}
@@
 \section{Discussion}
-As discussed above, we do not recover the moon. Our analysis was designed to be independent, and as such makes different choices about the data reduction and the choice of sytematics model.
+A natural question arising from our results is what the difference is between TK18 and the new fits presented here.
+One possibility is that the source of the discrepancy is the raw data itself.
+As shown in Figure\,\ref{fig:raw}, our measured count rate ranges from $2.46 -2.74\%$ lower than the TK18 measurement, and there is a small bump in the difference between the two data sets near the location of the moon transit identified in the TK18 data (see the bottom panel).
 
-We explored several avenues to determine what caused the difference in our results. We first checked whether the detrending model was responsible.
+ We explored several modifications to our pipeline to attempt to reproduce the TK18 reduction.
+These included rotating the image by 0.5 degrees, using the same aperture as TK18 to extract the spectrum, and scaling the master sky flat for the background subtraction (rather than just subtracting the median).
+None of these modifications had a significant effect on our results.
 
-We also compared the data directly (see Figure\,\ref{fig:raw}). The data is different!
-rotate the image, aperture choice, measurement of the background, outlier masking,
+There are a few other steps in the TK18 data reduction that would require substantial modification of our pipeline to recreate, but seem unlikely to be responsible for the difference.
+One of these is outlier masking.
+TK18 identify outliers with a Gaussian process fit to the pixel-level light curves, compared to our optimal extraction approach.
+Despite the difference, both methods flag $\sim$0.01\% of pixels as bad.
+We also do not use the STScI software \texttt{axeprep} to embed the raw $256\times256$ image in a larger array; however, this process primarily affects the edge of the image, many pixels distant from the extraction box, so it is unclear how this step would bias the light curve.
 
-In this work, we presented an independent analysis of HST observations of the Kepler-1625 system.
-In contrast to previous analysis by \citep{teachey18b}, we do not find evidence for the transit of a moon.
-We obtain a better fit to the data without including a moon in the model.
-We
+ %The only other difference we identify in the data reduction is the outlier masking.
+In our analysis, we iteratively masked outliers with the optimal extraction routine, whereas TK18 identified outliers via a Gaussian process fit to the pixel-level light curves.
+We flagged 0.07\% of pixels as bad, whereas TK18 flag twice as many.
+It is possible that this discrepancy could play role in the difference between the raw data sets.
+
+In addition to these differences in data reduction, we also used a new detrending model.
+We opted for a decorrelation against X and Y position, motivated by known variation in the sensitivity of individual pixels on the detector and the presence of small shifts in the position of the spectrum (see Figure\,\ref{fig:shifts}).
+We applied this detrending model to the TK18 data, and obtained a poor fit to the light curve compared to the polynomial detrending (for the moon model with X-Y decorrelation, the rms was 404 ppm).
+We did not recover a large moon in this fit (the best fit was $r_\mathrm{moon} = 1.2R_\oplus$), but there was correlated noise present in the data that precluded a robust measurement of the uncertainty on the moon radius for this model.
+The poor quality of the fit points toward the raw data as the culprit for the difference in our results, but as we discuss, we could not identify a specific choice in the data reduction that is responsible.
+
+ We conclude that no single choice in the data reduction or the modeling provides an easy explanation for the difference in our results, but rather that the difference is in the sum of many subtle choices.
+
+\section{Conclusion}
+The hunt for exomoons remains exciting and volatile.
+Our analysis of the exomoon candidate Kepler-1625b-i shows that the evidence in favor of the moon is highly sensitive to details of the data reduction and modeling.
+Future allocation of follow-up resources should prioritize alternative targets.
+
+%\vspace{2cm}
 

### 2019-01-23 figures/fig2_rms.py

@@ -14,7 +14,7 @@ def computeRMS(data, maxnbins=None, binstep=1, isrmserr=False):
     # bin data into multiple bin sizes
     npts    = data.size
     if maxnbins is None:
-        maxnbins = npts/12.
+        maxnbins = npts/11.
     binsz   = np.arange(1, maxnbins+binstep, step=binstep)
     nbins   = np.zeros(binsz.size)
     rms     = np.zeros(binsz.size)
@@ -68,6 +68,7 @@ plt.loglog(binsz, rms/normfactor*np.sqrt(chi2red), zorder = 10, color='blue', la
 
 print("excess over photon, LK:", binsz) 
 print("excess over photon, LK:", rms*np.sqrt(chi2red)/stderr)
+stderr_LK = np.copy(stderr)
 
 d = np.genfromtxt("kreidberg_moon_resid.txt")                                 
 ind = np.argsort(d[:,0])                                                        
@@ -87,7 +88,7 @@ rms, stderr, binsz, rmserr = computeRMS(resid, maxnbins = None, binstep = 1, isr
 plt.loglog(binsz, rms/normfactor*np.sqrt(chi2red), color='red',  label='TK18, no-moon')    # our noise
 
 
-print(rms/normfactor*np.sqrt(chi2red))
+print("excess over photon, teachey nom:", rms*np.sqrt(chi2red)/stderr_LK)
 
 
 
@@ -99,6 +100,7 @@ rms, stderr, binsz, rmserr = computeRMS(resid, maxnbins = None, binstep = 1, isr
 #normfactor = m.rms_predicted
 plt.loglog(binsz, rms/normfactor*np.sqrt(chi2red), color='red',  linestyle = 'dashed', label='TK18, moon')    # our noise
 
+print("excess over photon, teachey moon:", rms*np.sqrt(chi2red)/stderr_LK)
 
 #plt.xlim(0, binsz[-1]*2)
 plt.xlim(1, 20) 

### 2019-01-23 figures/fig3_bestfits.py

@@ -25,7 +25,7 @@ plt.figure(figsize = (8.5,4))
 
 plt.subplot(221)
 plt.title("This Work")
-phase, data_nosys, norm_resid, t_hr, fit_hr, rms, rms_predicted, chi2, chi2red, chi2red_rms395, dof_nomoon = pickle.load(open(lk_dir + "no_moon.p", "rb"))
+phase, data_nosys, norm_resid, t_hr, fit_hr, rms, rms_predicted, chi2, chi2red, chi2red_rms395, dof_nomoon = pickle.load(open(lk_dir + "no_moon.p", "rb"), encoding='latin1')
 plt.plot(period*phase - period*np.min(phase), data_nosys, '.w', markeredgecolor = 'k')
 plt.plot(period*(t_hr) - period*np.min(phase), fit_hr, color = 'b', label = 'no moon', linewidth = 2.)
 chi2 = np.sum((norm_resid/err)**2) 
@@ -52,7 +52,7 @@ plt.ylabel("Relative flux")
 chi2nu_lk_nomoon = chi2/dof_nomoon
 
 plt.subplot(223)
-phase, data_nosys, norm_resid, t_hr, fit_hr, rms, rms_predicted, chi2, chi2red, chi2red_rms395, dof_moon = pickle.load(open(lk_dir + "moon.p", "rb"))
+phase, data_nosys, norm_resid, t_hr, fit_hr, rms, rms_predicted, chi2, chi2red, chi2red_rms395, dof_moon = pickle.load(open(lk_dir + "moon.p", "rb"), encoding='latin1')
 plt.plot(period*(phase - np.min(phase)), data_nosys, '.w', markeredgecolor = 'k')
 plt.plot(period*(t_hr - np.min(phase)), fit_hr, color = 'b', label = 'moon', linewidth = 2.)
 chi2 = np.sum((norm_resid/err)**2) 

### 2019-01-23 figures/fig6_rawdata.py

@@ -37,5 +37,23 @@ plt.xlabel("Time since first exposure (days)")
 plt.plot(d[:,0] - np.min(d[:,0]), (d[:,1] - e[:,1]*290.776306)/1.e6, '.k', label = "difference")
 plt.axvline(moon_ingress, linestyle = 'dotted', color = '0.5')
 
+t = d[:,0] - np.min(d[:,0])
+diff = (d[:,1] - e[:,1]*290.776306)/1.e6 
+
+orb = 0
+orb_num = np.zeros_like(t)
+for i in range(1, len(orb_num)):                                        
+    if (t[i] - t[i-1]) > 0.5/24.: orb += 1
+    orb_num[i] = orb
+
+t_mean = np.zeros(orb)
+diff_mean = np.zeros(orb)
+for i in range(orb):
+    ind = orb_num == i
+    print(i)
+    t_mean[i] = np.mean(t[ind])
+    diff_mean[i] = np.mean(diff[ind])
+#plt.plot(t_mean, diff_mean, 'or')
+
 plt.tight_layout()
 plt.savefig("fig6_rawdata.pdf")

### 2019-01-23 ms-temp.tex
v1

@@
 \begin{abstract}
-    Observations of the Kepler-1625 system with the Kepler and Hubble Space Telescopes have suggested the presence of a candidate exomoon, a Neptune-radius satellite orbiting a long-period Jovian planet.
-Here we present a new analysis of the Hubble observations from an independent data reduction pipeline.
-We find that the transit light curve is well fit with a planet-only model, and that the addition of a moon does not significantly improve the fit quality.
-The $3\,\sigma$ upper limit on the moon radius is $4.0R_\oplus$.
-FIXME: why are we different from TK18?
-We conclude that FIXME, and future follow-up efforts for exomoons should focus on alternative targets.
+    Observations of the Kepler-1625 system with the Kepler and Hubble Space Telescopes have suggested the presence of a candidate exomoon, Kepler-1625b I, a Neptune-radius satellite orbiting a long-period Jovian planet.
+Here we present a new analysis of the Hubble observations, using an independent data reduction pipeline.
+We find that the transit light curve is well fit with a planet-only model, with a best-fit $\chi^2_\nu$ equal to $1.01$.
+The addition of a moon does not significantly improve the fit quality.
+We compare our results directly with \cite{teachey18b}, and find that we obtain a better fit to the light curve using a model with fewer free parameters (no moon).
+We discuss possible sources for the discrepancy in our results, and conclude that there is no single explanation for the difference but rather that it is the sum of many small choices.
+We conclude that future follow-up efforts for exomoons should focus on alternate targets.
+
 \end{abstract}
 
-\keywords{planets and satellites: individual (Kepler-1625b)}
+\keywords{planets and satellites: individual (Kepler-1625b I)}
 
@@
 The host planet, Kepler-1625b has radius consistent with that of Jupiter and an orbital period of 287 days.
-The first evidence for the exomoon candidate, Kepler-1625b I, came from three transit observations from the \Kepler\ primary mission that showed FIXME \citep{teachey18a}...
+The first evidence for the exomoon candidate, Kepler-1625b I, was based on transit observations from \Kepler, which were discrepant with a planet-only model at $>4\sigma$ confidence \citep{teachey18a}.
+Follow-up observations with HST also suggested evidence for a moon, based on a small drop in the system flux after the planet's egress from transit \citep{teachey18b}.
+The best fit moon had a large radius (comparable to that of Neptune), and if real, would be unlike any moon in the Solar System.
+
+Recently, \cite{rodenbeck18} performed an independent fit to the Kepler light curves and found that the evidence for the moon was strongly dependent on the detrending method.
+Motivated by this result, in this work we perform an independent fit to the HST light curve.
 
@@
 \section{Discussion}
-We  do not recover the moon
-differs both in the data reduction and the choice of systematics model
-neither
+A natural question arising from our results is what the difference is between TK18 and the new fits presented here.
+One possibility is that the source of the discrepancy is the raw data itself.
+As shown in Figure\,\ref{fig:raw}, our measured count rate ranges from $2.46 -2.74\%$ lower than the TK18 measurement, and there is a small bump in the difference between the two data sets near the location of the moon transit identified in the TK18 data (see the bottom panel).
 
-many choices
-rotate the image, aperture choice, measurement of the background, outlier masking,
+ We explored several modifications to our pipeline to attempt to reproduce the TK18 reduction.
+These included rotating the image by 0.5 degrees, using the same aperture as TK18 to extract the spectrum, and scaling the master sky flat for the background subtraction (rather than just subtracting the median).
+None of these modifications had a significant effect on our results.
+
+There are a few other steps in the TK18 data reduction that would require substantial modification of our pipeline to recreate, but seem unlikely to be responsible for the difference.
+One of these is outlier masking.
+TK18 identify outliers with a Gaussian process fit to the pixel-level light curves, compared to our optimal extraction approach.
+Despite the difference, both methods flag $\sim$0.01\% of pixels as bad.
+We also do not use the STScI software \texttt{axeprep} to embed the raw $256\times256$ image in a larger array; however, this process primarily affects the edge of the image, many pixels distant from the extraction box, so it is unclear how this step would bias the light curve.
+
+ %The only other difference we identify in the data reduction is the outlier masking.
+In our analysis, we iteratively masked outliers with the optimal extraction routine, whereas TK18 identified outliers via a Gaussian process fit to the pixel-level light curves.
+We flagged 0.07\% of pixels as bad, whereas TK18 flag twice as many.
+It is possible that this discrepancy could play role in the difference between the raw data sets.
+
+In addition to these differences in data reduction, we also used a new detrending model.
+We opted for a decorrelation against X and Y position, motivated by known variation in the sensitivity of individual pixels on the detector and the presence of small shifts in the position of the spectrum (see Figure\,\ref{fig:shifts}).
+We applied this detrending model to the TK18 data, and obtained a poor fit to the light curve compared to the polynomial detrending (for the moon model with X-Y decorrelation, the rms was 404 ppm).
+We did not recover a large moon in this fit (the best fit was $r_\mathrm{moon} = 1.2R_\oplus$), but there was correlated noise present in the data that precluded a robust measurement of the uncertainty on the moon radius for this model.
+The poor quality of the fit points toward the raw data as the culprit for the difference in our results, but as we discuss, we could not identify a specific choice in the data reduction that is responsible.
+
+ We conclude that no single choice in the data reduction or the modeling provides an easy explanation for the difference in our results, but rather that the difference is in the sum of many subtle choices.
 
 \section{Conclusion}
-In this work, we presented an independent analysis of HST observations of the Kepler-1625 system.
-In contrast to previous analysis by \citep{teachey18b}, we do not find evidence for the transit of a moon.
+The hunt for exomoons remains exciting and volatile.
+Our analysis of the exomoon candidate Kepler-1625b I shows that the evidence in favor of the moon is highly sensitive to details of the data reduction and modeling.
+Future allocation of follow-up resources should prioritize alternative targets.
 
-what is 
-approach to data reduction was very similar, but of the data reduction, and
+%\vspace{2cm}
 
@@
 Funding for the DPAC has been provided by national institutions, in particular the institutions participating in the {\it Gaia} Multilateral Agreement.
-We also use data products from the Two Micron All Sky Survey, which is a joint project of the University of Massachusetts and the Infrared Processing and Analysis Center/California Institute of Technology, funded by the National Aeronautics and Space Administration and the National Science Foundation.
+%We also use data products from the Two Micron All Sky Survey, which is a joint project of the University of Massachusetts and the Infrared Processing and Analysis Center/California Institute of Technology, funded by the National Aeronautics and Space Administration and the National Science Foundation.
 This research has made use of the SIMBAD database, operated at CDS, Strasbourg, France; the REBOUND integrator package \citep{rein12}; the NumPy package \citep{van2011numpy}; and NASA's Astrophysics Data System.
@@
 
+\bibitem[{{Rodenbeck} {et~al.}(2018){Rodenbeck}, {Heller}, {Hippke}, \&
+  {Gizon}}]{rodenbeck18}
+{Rodenbeck}, K., {Heller}, R., {Hippke}, M., \& {Gizon}, L. 2018, \aap, 617,
+  A49, \dodoi{10.1051/0004-6361/201833085}
+
 \bibitem[{{Sengupta} \& {Marley}(2016)}]{sengupta16}

### 2019-01-23 ms.tex
v1

@@
 \begin{abstract}
-    Observations of the Kepler-1625 system with the Kepler and Hubble Space Telescopes have suggested the presence of a candidate exomoon, Kepler-1625b-i, a Neptune-radius satellite orbiting a long-period Jovian planet.
-Here we present a new analysis of the Hubble observations from an independent data reduction pipeline.
+    Observations of the Kepler-1625 system with the Kepler and Hubble Space Telescopes have suggested the presence of a candidate exomoon, Kepler-1625b I, a Neptune-radius satellite orbiting a long-period Jovian planet.
+Here we present a new analysis of the Hubble observations, using an independent data reduction pipeline.
 We find that the transit light curve is well fit with a planet-only model, with a best-fit $\chi^2_\nu$ equal to $1.01$.
@@
 
-\keywords{planets and satellites: individual (Kepler-1625b)}
+\keywords{planets and satellites: individual (Kepler-1625b I)}
 
@@
 The hunt for exomoons remains exciting and volatile.
-Our analysis of the exomoon candidate Kepler-1625b-i shows that the evidence in favor of the moon is highly sensitive to details of the data reduction and modeling.
-Future allocation of follow-up resources should prioritize alternative targets.
+Our analysis of the exomoon candidate Kepler-1625b I shows that the evidence in favor of the moon is highly sensitive to details of the data reduction and modeling.
+Given that we achieve an excellent fit to the light curve with a no-moon model, and that the addition of a moon does not significantly improve the fit quality, we conclude that future allocation of follow-up resources for exomoons should prioritize alternate targets.
 

### 2019-02-06 ms.tex
edits

@@
 
-\title{That's No Moon: New Analysis Shows No Evidence for Lunar Companion Orbiting Kepler-1625b}
+\title{New Analysis Shows No Evidence for Lunar Companion Orbiting Kepler-1625b}
 
 \author{Laura Kreidberg}
+\affiliation{Harvard-Smithsonian Center for Astrophysics, 60 Garden Street, Cambridge, MA 02138}
 \affiliation{Harvard Society of Fellows, 78 Mount Auburn Street, Cambridge, MA 02138}
-\affiliation{Harvard-Smithsonian Center for Astrophysics, 60 Garden Street, Cambridge, MA 02138}
 \author{Rodrigo Luger}
+\affiliation{Flatiron Institute, Simons Foundation, 162 Fifth Ave, New York, NY 10010, USA}
 \author{Megan Bedell}
+\affiliation{Flatiron Institute, Simons Foundation, 162 Fifth Ave, New York, NY 10010, USA}
 
@@
 We discuss possible sources for the discrepancy in our results, and conclude that there is no single explanation for the difference but rather that it is the sum of many small choices.
-We conclude that future follow-up efforts for exomoons should focus on alternate targets.
+Given that the evidence for Kepler-1625b I hinges on the data reduction, we suggest that future follow-up efforts for exomoons should prioritize alternate targets.
 
@@
 The centroid position determines the position of the spectral trace, which we calculated using the coeffients provided in the configuration file from STScI: \texttt{G141.F130N.V4.32.conf}\footnote{available at \url{http://www.stsci.edu/hst/wfc3/analysis/grism_obs/calibrations/wfc3_g141.html}}.
-To process the spectra, we flatfielded the raw data using the spectroscopic flatfield coefficients provided by STScI in \texttt{WFC3.IR.G141.flat.2.fits}, following the instructions in Section 6 of the aXe User Manual\footnote{\url{http://axe-info.stsci.edu/}}.
+To process the spectra, we flatfielded the raw data using the spectroscopic flatfield coefficients provided by STScI in \texttt{WFC3.IR.G141.flat.2.fits}, following the instructions in Section 6 of the aXe User Manual\footnote{\url{http://ane-info.stsci.edu/}}.
 We then created an extraction box centered on the spectral trace.
@@
 \includegraphics[width = 0.5 \textwidth]{figures/fig6_rawdata.pdf}
-    \caption{Top: raw data from this work (blue) compared to TK18 (red).
-Bottom: the difference in raw photoelectron counts between the data sets.
+    \caption{Top: extractred light curve from this work (blue) compared to TK18 (red).
+Bottom: the difference in photoelectron counts between the data sets.
 The moon ingress identified by TK18 is marked by the dotted gray line.}
@@
 \section{Analysis}
-The raw light transit light curve (shown in Figure~\ref{fig:raw}) contains both astrophysical signal and instrument systematic noise, which we model simultaneously.
+The extracted transit light transit light curve (shown in Figure~\ref{fig:raw}) contains both astrophysical signal and instrument systematic noise, which we model simultaneously.
 
@@
 \subsection{Light Curve Fits}
-We fit the raw, broadband transit light curve using the models described above.
+We fit the broadband transit light curve using the models described above.
 We determined the best fit model parameters with least-squares minimization.
@@
 \cite{teachey18b} found evidence for the transit of a Neptune-size moon in their analysis of the HST data, in contrast to the findings presented here.
-To make a direct comparison with their results, we fit the raw TK18 data directly.
+To make a direct comparison with their results, we fit the TK18 transit light curve directly.
 
@@
 A natural question arising from our results is what the difference is between TK18 and the new fits presented here.
-One possibility is that the source of the discrepancy is the raw data itself.
-As shown in Figure\,\ref{fig:raw}, our measured count rate ranges from $2.46 -2.74\%$ lower than the TK18 measurement, and there is a small bump in the difference between the two data sets near the location of the moon transit identified in the TK18 data (see the bottom panel).
+One possibility is that the source of the discrepancy is the extracted transit light curves themselves.
+As shown in Figure\,\ref{fig:raw}, our measured count rate ranges from $2.46 -2.74\%$ lower than the TK18 light curve, and there is a small bump in the difference between the two data sets near the location of the moon transit identified in the TK18 data (see the bottom panel).
 
@@
 Despite the difference, both methods flag $\sim$0.01\% of pixels as bad.
-We also do not use the STScI software \texttt{axeprep} to embed the raw $256\times256$ image in a larger array; however, this process primarily affects the edge of the image, many pixels distant from the extraction box, so it is unclear how this step would bias the light curve.
+We also do not use the STScI software \texttt{aXeprep} to embed the raw $256\times256$ image in a larger array; however, this process primarily affects the edge of the image, many pixels distant from the extraction box, so it is unclear how this step would bias the light curve.
 
@@
 We did not recover a large moon in this fit (the best fit was $r_\mathrm{moon} = 1.2R_\oplus$), but there was correlated noise present in the data that precluded a robust measurement of the uncertainty on the moon radius for this model.
-The poor quality of the fit points toward the raw data as the culprit for the difference in our results, but as we discuss, we could not identify a specific choice in the data reduction that is responsible.
+The poor quality of the fit points toward the extracted light curve itself as the culprit for the difference in our results, but as we discuss, we could not identify a specific choice in the data reduction that is responsible.
 
@@
 Our analysis of the exomoon candidate Kepler-1625b I shows that the evidence in favor of the moon is highly sensitive to details of the data reduction and modeling.
-Given that we achieve an excellent fit to the light curve with a no-moon model, and that the addition of a moon does not significantly improve the fit quality, we conclude that future allocation of follow-up resources for exomoons should prioritize alternate targets.
+Given that we achieve an excellent fit to the light curve with a no-moon model, and that the addition of a moon does not significantly improve the fit quality, we suggest that future allocation of follow-up resources for exomoons should prioritize alternate targets.
 
@@
 \acknowledgments
+We thank A.
+Teachey for helpful discussions and for providing his data.
 The HST data presented in this paper were obtained from the Mikulski Archive for Space Telescopes (MAST).

### 2019-02-06 ms.tex
new mcmc

@@
 
-\title{New Analysis Shows No Evidence for Lunar Companion Orbiting Kepler-1625b}
+\title{No Evidence for Lunar Transit in New Analysis of HST Observations of the Kepler-1625 System}
 
@@
 We compare our results directly with \cite{teachey18b}, and find that we obtain a better fit to the light curve using a model with fewer free parameters (no moon).
-We discuss possible sources for the discrepancy in our results, and conclude that there is no single explanation for the difference but rather that it is the sum of many small choices.
+We discuss possible sources for the discrepancy in our results, and conclude that there is no single explanation for the difference but rather that it is the sum of many choices in the data reduction.
 Given that the evidence for Kepler-1625b I hinges on the data reduction, we suggest that future follow-up efforts for exomoons should prioritize alternate targets.
@@
 Recently, a potential exomoon candidate was identified in the Kepler-1625 system \citep{teachey18a}.
-The host planet, Kepler-1625b has radius consistent with that of Jupiter and an orbital period of 287 days.
+The host planet, Kepler-1625b, has a radius consistent with that of Jupiter and an orbital period of 287 days.
 The first evidence for the exomoon candidate, Kepler-1625b I, was based on transit observations from \Kepler, which were discrepant with a planet-only model at $>4\sigma$ confidence \citep{teachey18a}.
@@
 The inputs for optimal extraction are the background-subtracted data array, the error array (including photon noise read noise, and uncertainty due to background subtraction), an initial guess for the spectrum and its uncertainty, and a mask array for bad pixels.
-For the initial guess of the spectrum and its uncertainty, we did a simple box extraction (sum over all rows in the extraction window), and assumed the variance was equal to the box-extracted spectrum (expected for photon noise limit).
+For the initial guess of the spectrum and its uncertainty, we did a simple box extraction (sum over all rows in the extraction window), and assumed the variance was equal to the box-extracted spectrum (expected for photon-limited noise).
 We measured and subtracted the background from the data array as described in \ref{sec:background}.
@@
 \section{Analysis}
-The extracted transit light transit light curve (shown in Figure~\ref{fig:raw}) contains both astrophysical signal and instrument systematic noise, which we model simultaneously.
+The extracted transit light transit light curve (shown in Figure~\ref{fig:raw}) contains both astrophysical signals and instrument systematic noise, which we model simultaneously.
 
@@
 We determined the best fit model parameters with least-squares minimization.
-We also ran a Markov chain Monte Carlo (MCMC) fit to determine the posterior probability of each parameters.
+We also ran a Markov chain Monte Carlo (MCMC) fit to determine the posterior probability of the parameters.
 For the MCMC, we held the ramp parameters $c_1, ..., c_9$ fixed at their best-fit values.
@@
 \cite{teachey18b} found evidence for the transit of a Neptune-size moon in their analysis of the HST data, in contrast to the findings presented here.
-To make a direct comparison with their results, we fit the TK18 transit light curve directly.
+To make a direct comparison with their results, we fit the TK18 light curve directly.
 
@@
 By contrast, the fit to the new data presented here yields an upper limit on the moon radius of ($4.0\,R_\oplus$ at $3\sigma$ confidence), and the transit time is unconstrained.
+
+% transit time is 0.5545 +/- 0.0013; consistent with Kipping, but slighlty earlier
 

### 2019-02-06 figures/fig5_corner.py

@@ -4,17 +4,19 @@ import matplotlib.pyplot as plt
 
 def quantile(x, q): return np.percentile(x, [100. * qi for qi in q])
 
-chain = np.load("mcmc_output/mcmc_LK.npy")
+
+chain = np.load("mcmc_output/mcmc_LK_full.npy")
 ndim = chain.shape[-1]
-samples_lk = chain[:, 1000:5000, :].reshape((-1, ndim))
+samples_lk = chain[:, 5000:10000, :].reshape((-1, ndim))
 
-chain = np.load("mcmc_output/mcmc_TK18.npy")
+chain = np.load("mcmc_output/mcmc_TK18_full.npy")
 ndim = chain.shape[-1]
-samples_tk = chain[:, 2000:10000, :].reshape((-1, ndim))
+samples_tk = chain[:, 5000:10000, :].reshape((-1, ndim))
 
-samples_lk = samples_lk[:,5:7]
+samples_lk = samples_lk[:,[6,8]]
+#samples_lk[:,1] = samples[
 
-samples_tk = samples_tk[:,5:7].T
+samples_tk = samples_tk[:,[6,8]].T
 corner.corner(samples_lk, samples_tk, plot_datapoints = False, 
             levels = [0.68, 0.95, 0.997], fill_contours = True, alpha = 0.5, 
             color = 'blue', 
@@ -23,5 +25,6 @@ corner.corner(samples_lk, samples_tk, plot_datapoints = False,
 
 print(quantile(samples_lk[:, 1], [0.95, 0.997]))
 print(quantile(samples_tk[1, :], [0.003, 0.16, 0.5, 0.84]))
-print(quantile(samples_tk[0, :], [0.16, 0.5, 0.84]) + 2458055.)
+print("t0", quantile(samples_lk[:, 0], [0.16, 0.5, 0.84]) + 2458055.)
+print(samples_lk[:,0].shape)
 plt.savefig('fig5_pairs.pdf')

### 2019-02-06 figures/mycorner.py

@@ -212,9 +212,9 @@ def corner(xs, ys, bins=20, range=None, weights=None, color="k",
         # Plot the histograms.
         #n, _, _ = ax.hist(x, bins=bins[i], weights=weights,
          #                 range=np.sort(range[i]), **hist_kwargs)
-        n, _, _ = ax.hist(x, color = 'b', density = True, histtype = 'step')
+        n, _, _ = ax.hist(x, color = 'b', normed = True, histtype = 'step')
 
-        n, _, _ = ax.hist(y1, color = 'r',  density = True, histtype = 'step') 
+        n, _, _ = ax.hist(y1, color = 'r',  normed = True, histtype = 'step') 
 
         if truths is not None and truths[i] is not None:
             ax.axvline(truths[i], color=truth_color)

### 2019-02-10 ms-temp.tex
6 parameter mcmc

@@
 
-\title{That's No Moon: New Analysis Shows No Evidence for Lunar Companion Orbiting Kepler-1625b}
+\title{No Evidence for Lunar Transit in New Analysis of HST Observations of the Kepler-1625 System}
 
 \author{Laura Kreidberg}
+\affiliation{Harvard-Smithsonian Center for Astrophysics, 60 Garden Street, Cambridge, MA 02138}
 \affiliation{Harvard Society of Fellows, 78 Mount Auburn Street, Cambridge, MA 02138}
-\affiliation{Harvard-Smithsonian Center for Astrophysics, 60 Garden Street, Cambridge, MA 02138}
 \author{Rodrigo Luger}
+\affiliation{Flatiron Institute, Simons Foundation, 162 Fifth Ave, New York, NY 10010, USA}
 \author{Megan Bedell}
+\affiliation{Flatiron Institute, Simons Foundation, 162 Fifth Ave, New York, NY 10010, USA}
 
@@
 The addition of a moon does not significantly improve the fit quality.
-We compare our results directly with \cite{teachey18b}, and find that we obtain a better fit to the light curve using a model with fewer free parameters (no moon).
-We discuss possible sources for the discrepancy in our results, and conclude that there is no single explanation for the difference but rather that it is the sum of many small choices.
-We conclude that future follow-up efforts for exomoons should focus on alternate targets.
+We compare our results directly with the original light curve from \cite{teachey18b}, and find that we obtain a better fit to the data using a model with fewer free parameters (no moon).
+We conclude that the evidence for the transit of Kepler-1625b I hinges on subtleties of the data reduction, and we therefore suggest that future follow-up efforts for exomoons should prioritize alternate targets.
 
@@
 Recently, a potential exomoon candidate was identified in the Kepler-1625 system \citep{teachey18a}.
-The host planet, Kepler-1625b has radius consistent with that of Jupiter and an orbital period of 287 days.
+The host planet, Kepler-1625b, has a radius consistent with that of Jupiter and an orbital period of 287 days.
 The first evidence for the exomoon candidate, Kepler-1625b I, was based on transit observations from \Kepler, which were discrepant with a planet-only model at $>4\sigma$ confidence \citep{teachey18a}.
-Follow-up observations with HST also suggested evidence for a moon, based on a small drop in the system flux after the planet's egress from transit \citep{teachey18b}.
+Follow-up observations with HST also suggested evidence for a moon, based on a small drop in the system flux after the planet's egress from transit and a possible transit timing variation \citep[][ hereafter TK18]{teachey18b}.
 The best fit moon had a large radius (comparable to that of Neptune), and if real, would be unlike any moon in the Solar System.
@@
 Recently, \cite{rodenbeck18} performed an independent fit to the Kepler light curves and found that the evidence for the moon was strongly dependent on the detrending method.
-Motivated by this result, in this work we perform an independent fit to the HST light curve.
+Motivated by this result, in this work we perform an independent reduction and fit to the HST light curve.
 
@@
 At the beginning of the visit, there was a single exposure taken with the F130N filter, which is used to determine the position of the spectral trace.
-The following exposures used the G141 grism with the \texttt{SPARS25}, \texttt{NSAMP}=15 readout pattern (exposure time of 290.8 seconds; 9 exposures per orbit).
-For additional description of the observation design, see \cite{teachey18b}.
+The following exposures used the G141 grism.
+See TK18 for additional description of the observation design.
+%with the \texttt{SPARS25}, \texttt{NSAMP}=15 readout pattern (exposure time of 290.8 seconds; 9 exposures per orbit).
 
@@
 We ran our pipeline on the \texttt{flt} data product provided by the Space Telescope Science Institute (STScI).
-The \texttt{flt} files are corrected for dark current, bias, and nonlinearity, and they are cleaned of cosmic ray hits based on a fit to the up-the-ramp samples.
 In keeping with previous WFC3 analysis, we discarded the first orbit of data, where the instrument systematics have larger amplitude.
-We also discard exposures taken during the South Atlantic Anomaly passage (exposures 107, 116, 125, and 126).
+We also discarded exposures taken during the South Atlantic Anomaly passage (exposures 107, 116, 125, and 126).
+%The \texttt{flt} files are corrected for dark current, bias, and nonlinearity, and they are cleaned of cosmic ray hits based on a fit to the up-the-ramp samples.
 
@@
 
-We reduced the grism exposures with the optimal extraction routine of \cite{horne86}, which minimizes background noise in the extracted spectrum by weighting pixels that are dominated by the target spectrum more heavily than pixels dominated by the background.
-The inputs for optimal extraction are the background-subtracted data array, the error array (including photon noise read noise, and uncertainty due to background subtraction), an initial guess for the spectrum and its uncertainty, and a mask array for bad pixels.
-For the initial guess of the spectrum and its uncertainty, we did a simple box extraction (sum over all rows in the extraction window), and assumed the variance was equal to the box-extracted spectrum (expected for photon noise limit).
-We measured and subtracted the background from the data array as described in \ref{sec:background}.
-For the error array, we used a quadrature sum of the photon noise (the square root of the pixel counts), the read noise (12 photoelectrons for \texttt{flt} files; WFC3 Data Handbook\footnote{\url{http://www.stsci.edu/hst/wfc3/documents/handbooks/currentDHB/}}), and the error due to background subtraction (described in \ref{sec:background}).
+We reduced the grism exposures with the optimal extraction routine of \cite{horne86}, which minimizes background noise in the extracted spectrum by preferentially weighting pixels that are dominated by the target spectrum.
+The inputs for optimal extraction are the background-subtracted data array, and estimate of the error per pixel, an initial guess for the spectrum and its uncertainty, and a mask array for bad pixels.
+For the initial guess of the spectrum, we did a simple box extraction (sum over all rows in the extraction window), and assumed the variance was equal to the box-extracted spectrum.
+We subtracted the background from the data array as described in \ref{sec:background}.
+For the error array, we used a quadrature sum of the photon noise (the square root of the pixel counts), the read noise (12 photoelectrons for \texttt{flt} files; WFC3 Data Handbook\footnote{\url{http://www.stsci.edu/hst/wfc3/documents/handbooks/currentDHB/}}), and the error due to background subtraction.
 The initial pixel mask marked all pixels as good.
 
-In brief, optimal extraction is an iterative procedure with the following steps.
-First, we created a smoothed image by median-filtering each row of the data with a 9-pixel-wide window.
+To optimally extract the spectrum,  we first created a smoothed image by median-filtering each row of the data with a 9-pixel-wide window.
 We then normalized the smoothed image by dividing each column by its sum, and multiplied it by the best guess spectrum.
-We compared the smoothed image to the real data and masked outliers in the data that are greater than a threshold $\sigma_\mathrm{cut}$.
+We compared the smoothed image to the real data and masked outliers in the data that are greater than a threshold $\sigma_\mathrm{cut} = 7.5$.
 We then recomputed the best guess spectrum with the new mask and the optimal weights from \cite{horne86}.
 The process is iterated until no outliers greater than the threshold remain.
-This procedure masks any cosmic rays or bad pixels that were missed by the initial \texttt{flt} calibration.
-We tested a range of thresholds ($7.5 < \sigma_\mathrm{cut} < 15$) and found that different $\sigma_\mathrm{cut}$ choices did not significantly change the final transit light curve.
-The data reported in this work use $\sigma_\mathrm{cut} = 7.5$.
-To create the broadband transit light curve, we sum each spectrum over all wavelengths.
+To create the broadband transit light curve, we sum each optimally extracted spectrum over all wavelengths.
+%This procedure masks any cosmic rays or bad pixels that were missed by the initial \texttt{flt} calibration.
 
@@
 To enable a correction for this effect, we measured the position of the spectrum over time.
+Figure\,\ref{fig:shifts} shows the best fit shifts.
 
-To measure shifts in the spatial direction, we first summed each \texttt{flt} image over all columns (which we dub the ``column sum").
+To measure shifts in the spatial direction, we summed each \texttt{flt} image over all columns (which we dub the ``column sum").
 We used the first exposure in the visit as a template, and for each subsequent exposure, we used least-squares minimization to calculate the shift in pixels that minimized the difference between its column sum and the template.
@@
 
-Figure\,\ref{fig:shifts} shows the best fit shifts.
-Over the entire 26-orbit visit, the maximum shift is less than 0.2 pixel in the spatial direction and 0.3 pixel in the spectral direction.
+%Over the entire 26-orbit visit, the maximum shift is less than 0.2 pixel in the spatial direction and 0.3 pixel in the spectral direction.
 The largest shift occurs after orbit 14, when the telescope reacquired the guide stars.
@@
 \section{Analysis}
-The raw light transit light curve (shown in Figure~\ref{fig:raw}) contains both astrophysical signal and instrument systematic noise, which we model simultaneously.
+The extracted transit light transit light curve (shown in Figure~\ref{fig:raw}) contains both astrophysical signals and instrument systematic noise, which we model simultaneously.
 
@@
 Within \texttt{planetplanet}, the orbits are computed with the N-body integrator \texttt{REBOUND} \citep{rein12}.
-The \texttt{planetplanet} model returns the system flux at a specified orbital architecture and time.
+%The \texttt{planetplanet} model returns the system flux at a specified orbital architecture and time.
 
 In our analysis, we considered two scenarios: a no-moon model and a moon model.
-The free parameters for the no-moon model were: the stellar radius $R_*$, the planet radius $R_\mathrm{planet}$, the time of central transit $t_\mathrm{planet}$, and the planet inclination $i$.
-For the moon model, we added a third body with radius $R_\mathrm{moon}$, transit time $t_\mathrm{moon}$, and orbital period $P_\mathrm{moon}$.
-We allowed the moon period to vary from 1.6 to 260 days.
+The free parameters for the no-moon model were: the stellar radius, the planet radius, the planet's time of central transit, the planet inclination, and the planet mass.
+For the moon model, we added a third body with six free parameters: moon radius, moon time of central transit, moon orbital period, moon inclination, moon mass, and longitude of the ascending node relative to that of the planet.
+We fixed the eccentricity of all bodies to zero.
+We also fixed the planet's orbital period to 287.378949 days (the best fit from TK18).
+
+We used the following priors: the stellar radius was normally distributed, $R_* \sim N(1.81, 0.17) R_\odot$ (see next section).
+The planet radius was uniform from $8 - 14R_\oplus$.
+The planet transit time was uniform over the timespan of the observations, and inclination was uniform from $0 - 90^\circ$.
+The planet mass was log-normally distributed, $M_\mathrm{p} \sim 10^{2.5 \pm 0.5} M_\oplus$, based on the expectation for Jupiter-radius objects from \cite{ning18}.
+For the moon model, we allowed the transit time to vary uniformly over the entire visit.
+The moon period was uniform between 1.6 to 260 days.
 These limits span the duration of the \HST\ observations (so there is one possible moon occultation event), to the orbit at 0.5 the Hill radius, based on the stability limit for prograde moon orbits \citep{domingos06}.
 The Hill radius calculation assumed the planet and stellar masses are $1\,M_\mathrm{Jup}$ and $1.37\,M_\odot$.
-
-The models also fixes several parameters that are poorly constrained by the light curve shape.
-For the moon model, we fixed inclination of the moon to $90^\circ$ to exclude grazing transit scenarios, where the moon radius could be arbitrarily large.
-We also fixed the moon mass and eccentricity to zero.
-For both the no-moon and moon models, we fixed the planet's orbital period to 287.378949 days \citep{teachey18b}.
-We also fixed the planet eccentricity to zero and the mass to $1\,M_\mathrm{Jup}$.
+The moon inclination was uniform from $89.7 - 90^\circ$ (to exclude grazing moon transit scenarios, where the moon radius could be arbitrarily large).
+The moon mass varied uniformly from $0 - 30 M_\oplus$.
+The longitude of the ascending node was also uniform from $0 - 180^\circ$.
 
@@
 The top panel shows the best fit no-moon model, and the bottom shows the best fit moon model.
-The lower left of each panel indicates the fit rms (in ppm), the $\chi_2$, the degrees of freedom, and the change in BIC relative to the lowest value.
-Each light curve is divided by its best fit systematics model (XY decorrelation for this work; second-order polynomial and offset for TK18).
+The lower left of each panel indicates the fit rms (in ppm), the $\chi_2$, the degrees of freedom, and the BIC.
+Each light curve is divided by its best fit systematics model (XY decorrelation for this work; exponential and offset for TK18).
 The dotted gray line marks the possible moon ingress identified by TK18.}
@@
 
-To fit the orbit-long ramp, we used the non-parametric model from \cite{teachey18b}, which assigns each of the nine exposures per orbit a normalization constant, $c_1, ..., c_9$.
-To fit the visit-long trend, we used a linear combination of X and Y position (the shift relative to the mean in the spatial and spectral directions, respectively; shown in Figure~\ref{fig:shifts}).
+To fit the orbit-long ramp, we used the non-parametric model from TK18, which assigns each of the nine exposures per orbit a normalization constant, $c_1, ..., c_9$.
+To fit the visit-long trend, we used a linear combination of X and Y position (the shift relative to the mean in the spatial and spectral directions; shown in Figure~\ref{fig:shifts}).
 In sum, for exposure number $i$, the systematics model S is:
@@
 \subsection{Light Curve Fits}
-We fit the raw, broadband transit light curve using the models described above.
+We fit the broadband transit light curve using the models described above.
 We determined the best fit model parameters with least-squares minimization.
-We also ran a Markov chain Monte Carlo (MCMC) fit to determine the posterior probability of each parameters.
+We also ran a Markov chain Monte Carlo (MCMC) fit to determine the posterior probability of the parameters.
 For the MCMC, we held the ramp parameters $c_1, ..., c_9$ fixed at their best-fit values.
@@
 
-We obtained a slightly better fit with the moon model (rms = 351 ppm; $\chi_\nu^2 = 0.998$); however, this is not a large enough improvement in fit quality to merit the addition of three additional free parameters.
-According to the Bayesian information criterion (BIC), which penalizes unnecessary model complexity, the moon model is disfavored with $\Delta\mathrm{BIC} = 10.7$.
+We obtained a slightly lower rms with the moon model (351 ppm); however, this is not a large enough improvement in fit quality to merit the addition of six additional free parameters.
+The moon model has a small increase in $\chi^2_\nu$ to 1.02.
+According to the Bayesian information criterion (BIC), which penalizes unnecessary model complexity, the moon model is disfavored with $\Delta\mathrm{BIC} = 26.7$.
 This constitutes strong evidence against the inclusion of a moon \citep{kass95}.
-In addition, the moon transit time is not well-constrained by the data.
-As shown in the posterior distribution in Figure~\ref{fig:corner}, the $2\,\sigma$ confidence interval for the moon's transit includes the entire duration of the observations.
-The upper limit on the moon radius is $3.2\,R_\oplus$ at $2\sigma$ confidence and $4.0\,R_\oplus$ at $3\sigma$.
+In addition, as shown in Figure\,\ref{fig:corner}, the posterior distribution for the moon transit time is not unimodal, and the $2\,\sigma$ confidence interval for the moon's transit spans the entire duration of the observations.
+The upper limit on the moon radius is $3.5\,R_\oplus$ at $3\sigma$ confidence.
 
@@
 \subsection{Comparison with Teachey \& Kipping (2018)}
-\cite{teachey18b} found evidence for the transit of a Neptune-size moon in their analysis of the HST data, in contrast to the findings presented here.
-To make a direct comparison with their results, we fit the raw TK18 data directly.
+TK18 found evidence for the transit of a Neptune-size moon in their analysis of the HST data, in contrast to the findings presented here.
+To make a direct comparison with their results, we fit the TK18 light curve directly.
 
@@
 We therefore opted to use a TK18 systematics model to enable a fair comparison between our results.
-We obtained the best fit using a second-order polynomial trend in time, a constant offset after orbit 14 (where the guide stars are reacquired), and the non-parameteric orbit-long ramp model.
+We obtained the best fit using an exponential trend in time, a constant offset after orbit 14 (where the guide stars are reacquired), and the non-parameteric orbit-long ramp model.
 This model has one more free parameter than the systematics model given in Equation~\ref{eq:sys}.
@@
 
-Similar to the findings of TK18, the moon model improved the fit quality by a $\Delta\chi^2 = 22.0$.
-Notably, however, the moon model fit to the TK18 data does not perform better than the no-moon model fit to our new data (rms of 363 versus 356 ppm), even with the additional four free parameters.
-This difference in fit quality corresponds to $\Delta\mathrm{BIC} = 31.2$, which is strong evidence against the moon.
+Similar to the findings of TK18, the moon model improved the fit quality by a $\Delta\chi^2 = 29.9$.
+Notably, however, the moon model fit to the TK18 data does not perform better than the no-moon model fit to our new data (rms of 362 versus 356 ppm), even with the additional seven free parameters.
+%This difference in fit quality corresponds to $\Delta\mathrm{BIC} = 31.2$, which is strong evidence against the moon.
 
@@
 As shown in Figure\,\ref{fig:corner}, for the TK18 data the moon radius and transit time are peaked at $r_\mathrm{moon} = 4.0^{+0.8}_{-0.6}\,R_\oplus$  and $t_\mathrm{moon} =  2458056.29^{+0.06}_{-0.04}\,\mathrm{BJD_{TDB}}$.
-By contrast, the fit to the new data presented here yields an upper limit on the moon radius of ($4.0\,R_\oplus$ at $3\sigma$ confidence), and the transit time is unconstrained.
+By contrast, the fit to the new data presented here yields an upper limit on the moon radius of $3.5\,R_\oplus$ at $3\sigma$ confidence, and the transit time is unconstrained.
+
+The mid-transit times from the two fits agree better.
+TK18 found that the planet transited earlier than expected based on the Kepler data.
+Our posterior distribution for the planet's transit time agrees with TK18 to within $1\sigma$, leaving open the possibility for transit timing variations due to another body in the system.
+
+%, finding $t_\mathrm{planet} = 2458055.5545 \pm 0.0013$ versus $2458055.5563 \pm 0.0014\,\mathrm{BJD_{TDB}}$ from TK18.
+This result leaves open the possibility for transit timing variations in the system.
 
@@
 
-In addition to these differences in data reduction, we also used a new detrending model.
+In addition to these differences in data reduction, we also used an alternative detrending model.
 We opted for a decorrelation against X and Y position, motivated by known variation in the sensitivity of individual pixels on the detector and the presence of small shifts in the position of the spectrum (see Figure\,\ref{fig:shifts}).
@@
 We did not recover a large moon in this fit (the best fit was $r_\mathrm{moon} = 1.2R_\oplus$), but there was correlated noise present in the data that precluded a robust measurement of the uncertainty on the moon radius for this model.
-The poor quality of the fit points toward the raw data as the culprit for the difference in our results, but as we discuss, we could not identify a specific choice in the data reduction that is responsible.
+The poor quality of the fit points toward the extracted light curve itself as the culprit for the difference in our results, but as we discuss, we could not identify a specific step in the data reduction that is responsible.
 
- We conclude that no single choice in the data reduction or the modeling provides an easy explanation for the difference in our results, but rather that the difference is in the sum of many subtle choices.
+ We conclude that no single choice in the data reduction or the modeling provides an easy explanation for the difference in our results, but rather that the difference is more likely due to the combination of many subtle choices.
 
@@
 Our analysis of the exomoon candidate Kepler-1625b I shows that the evidence in favor of the moon is highly sensitive to details of the data reduction and modeling.
-Future allocation of follow-up resources should prioritize alternative targets.
+Given that we achieve an excellent fit to the light curve with a no-moon model, and that the addition of a moon does not significantly improve the fit quality, we suggest that future allocation of follow-up resources for exomoons should prioritize alternate targets.
 
@@
 \acknowledgments
+We thank A.
+Teachey for helpful discussions and for providing the extracted light curve from TK18.
 The HST data presented in this paper were obtained from the Mikulski Archive for Space Telescopes (MAST).
@@
 
+\bibitem[{{Ning} {et~al.}(2018){Ning}, {Wolfgang}, \& {Ghosh}}]{ning18}
+{Ning}, B., {Wolfgang}, A., \& {Ghosh}, S. 2018, \apj, 869, 5,
+  \dodoi{10.3847/1538-4357/aaeb31}
+
 \bibitem[{{Noyola} {et~al.}(2014){Noyola}, {Satyal}, \& {Musielak}}]{noyola14}
@@
 
-\bibitem[{Van Der~Walt {et~al.}(2011)Van Der~Walt, Colbert, \&
-  Varoquaux}]{van2011numpy}
-Van Der~Walt, S., Colbert, S.~C., \& Varoquaux, G. 2011, Computing in Science
-  \& Engineering, 13, 22
-
 \bibitem[{{Vanderburg} {et~al.}(2018){Vanderburg}, {Rappaport}, \&

### 2019-02-10 ms.tex
6 parameter mcmc

@@
 The addition of a moon does not significantly improve the fit quality.
-We compare our results directly with \cite{teachey18b}, and find that we obtain a better fit to the light curve using a model with fewer free parameters (no moon).
-We discuss possible sources for the discrepancy in our results, and conclude that there is no single explanation for the difference but rather that it is the sum of many choices in the data reduction.
-Given that the evidence for Kepler-1625b I hinges on the data reduction, we suggest that future follow-up efforts for exomoons should prioritize alternate targets.
+We compare our results directly with the original light curve from \cite{teachey18b}, and find that we obtain a better fit to the data using a model with fewer free parameters (no moon).
+We conclude that the evidence for the transit of Kepler-1625b I hinges on subtleties of the data reduction, and we therefore suggest that future follow-up efforts for exomoons should prioritize alternate targets.
 
@@
 The first evidence for the exomoon candidate, Kepler-1625b I, was based on transit observations from \Kepler, which were discrepant with a planet-only model at $>4\sigma$ confidence \citep{teachey18a}.
-Follow-up observations with HST also suggested evidence for a moon, based on a small drop in the system flux after the planet's egress from transit \citep{teachey18b}.
+Follow-up observations with HST also suggested evidence for a moon, based on a small drop in the system flux after the planet's egress from transit and a possible transit timing variation \citep[][ hereafter TK18]{teachey18b}.
 The best fit moon had a large radius (comparable to that of Neptune), and if real, would be unlike any moon in the Solar System.
@@
 
-We reduced the grism exposures with the optimal extraction routine of \cite{horne86}, which minimizes background noise in the extracted spectrum by weighting pixels that are dominated by the target spectrum more heavily than pixels dominated by the background.
-The inputs for optimal extraction are the background-subtracted data array, the error array (including photon noise read noise, and uncertainty due to background subtraction), an initial guess for the spectrum and its uncertainty, and a mask array for bad pixels.
-For the initial guess of the spectrum and its uncertainty, we did a simple box extraction (sum over all rows in the extraction window), and assumed the variance was equal to the box-extracted spectrum (expected for photon-limited noise).
-We measured and subtracted the background from the data array as described in \ref{sec:background}.
-For the error array, we used a quadrature sum of the photon noise (the square root of the pixel counts), the read noise (12 photoelectrons for \texttt{flt} files; WFC3 Data Handbook\footnote{\url{http://www.stsci.edu/hst/wfc3/documents/handbooks/currentDHB/}}), and the error due to background subtraction (described in \ref{sec:background}).
+We reduced the grism exposures with the optimal extraction routine of \cite{horne86}, which minimizes background noise in the extracted spectrum by preferentially weighting pixels that are dominated by the target spectrum.
+The inputs for optimal extraction are the background-subtracted data array, and estimate of the error per pixel, an initial guess for the spectrum and its uncertainty, and a mask array for bad pixels.
+For the initial guess of the spectrum, we did a simple box extraction (sum over all rows in the extraction window), and assumed the variance was equal to the box-extracted spectrum.
+We subtracted the background from the data array as described in \ref{sec:background}.
+For the error array, we used a quadrature sum of the photon noise (the square root of the pixel counts), the read noise (12 photoelectrons for \texttt{flt} files; WFC3 Data Handbook\footnote{\url{http://www.stsci.edu/hst/wfc3/documents/handbooks/currentDHB/}}), and the error due to background subtraction.
 The initial pixel mask marked all pixels as good.
 
-In brief, optimal extraction is an iterative procedure with the following steps.
-First, we created a smoothed image by median-filtering each row of the data with a 9-pixel-wide window.
+To optimally extract the spectrum,  we first created a smoothed image by median-filtering each row of the data with a 9-pixel-wide window.
 We then normalized the smoothed image by dividing each column by its sum, and multiplied it by the best guess spectrum.
-We compared the smoothed image to the real data and masked outliers in the data that are greater than a threshold $\sigma_\mathrm{cut}$.
+We compared the smoothed image to the real data and masked outliers in the data that are greater than a threshold $\sigma_\mathrm{cut} = 7.5$.
 We then recomputed the best guess spectrum with the new mask and the optimal weights from \cite{horne86}.
 The process is iterated until no outliers greater than the threshold remain.
-This procedure masks any cosmic rays or bad pixels that were missed by the initial \texttt{flt} calibration.
-We tested a range of thresholds ($7.5 < \sigma_\mathrm{cut} < 15$) and found that different $\sigma_\mathrm{cut}$ choices did not significantly change the final transit light curve.
-The data reported in this work use $\sigma_\mathrm{cut} = 7.5$.
-To create the broadband transit light curve, we sum each spectrum over all wavelengths.
+To create the broadband transit light curve, we sum each optimally extracted spectrum over all wavelengths.
+%This procedure masks any cosmic rays or bad pixels that were missed by the initial \texttt{flt} calibration.
 
@@
 \subsection{Comparison with Teachey \& Kipping (2018)}
-\cite{teachey18b} found evidence for the transit of a Neptune-size moon in their analysis of the HST data, in contrast to the findings presented here.
+TK18 found evidence for the transit of a Neptune-size moon in their analysis of the HST data, in contrast to the findings presented here.
 To make a direct comparison with their results, we fit the TK18 light curve directly.
@@
 As shown in Figure\,\ref{fig:corner}, for the TK18 data the moon radius and transit time are peaked at $r_\mathrm{moon} = 4.0^{+0.8}_{-0.6}\,R_\oplus$  and $t_\mathrm{moon} =  2458056.29^{+0.06}_{-0.04}\,\mathrm{BJD_{TDB}}$.
-By contrast, the fit to the new data presented here yields an upper limit on the moon radius of ($4.0\,R_\oplus$ at $3\sigma$ confidence), and the transit time is unconstrained.
+By contrast, the fit to the new data presented here yields an upper limit on the moon radius of $3.5\,R_\oplus$ at $3\sigma$ confidence, and the transit time is unconstrained.
 
-% transit time is 0.5545 +/- 0.0013; consistent with Kipping, but slighlty earlier
+The mid-transit times from the two fits agree better.
+TK18 found that the planet transited earlier than expected based on the Kepler data.
+Our posterior distribution for the planet's transit time agrees with TK18 to within $1\sigma$, leaving open the possibility for transit timing variations due to another body in the system.
+
+%, finding $t_\mathrm{planet} = 2458055.5545 \pm 0.0013$ versus $2458055.5563 \pm 0.0014\,\mathrm{BJD_{TDB}}$ from TK18.
+This result leaves open the possibility for transit timing variations in the system.
 
@@
 
-In addition to these differences in data reduction, we also used a new detrending model.
+In addition to these differences in data reduction, we also used an alternative detrending model.
 We opted for a decorrelation against X and Y position, motivated by known variation in the sensitivity of individual pixels on the detector and the presence of small shifts in the position of the spectrum (see Figure\,\ref{fig:shifts}).
-We applied this detrending model to the TK18 data, and obtained a poor fit to the light curve compared to the polynomial detrending (for the moon model with X-Y decorrelation, the rms was 404 ppm).
+We applied this detrending model to the TK18 data, and obtained a poor fit to the light curve compared to exponential detrending (for the moon model with XY decorrelation, the rms was 404 ppm).
 We did not recover a large moon in this fit (the best fit was $r_\mathrm{moon} = 1.2R_\oplus$), but there was correlated noise present in the data that precluded a robust measurement of the uncertainty on the moon radius for this model.
-The poor quality of the fit points toward the extracted light curve itself as the culprit for the difference in our results, but as we discuss, we could not identify a specific choice in the data reduction that is responsible.
+The poor quality of the fit points toward the extracted light curve itself as the culprit for the difference in our results, but as we discuss, we could not identify a specific step in the data reduction that is responsible.
 
- We conclude that no single choice in the data reduction or the modeling provides an easy explanation for the difference in our results, but rather that the difference is in the sum of many subtle choices.
+ We conclude that no single choice in the data reduction or the modeling provides an easy explanation for the difference in our results, but rather that the difference is more likely due to the combination of many subtle choices.
 
@@
 We thank A.
-Teachey for helpful discussions and for providing his data.
+Teachey for helpful discussions and for providing the extracted light curve from TK18.
 The HST data presented in this paper were obtained from the Mikulski Archive for Space Telescopes (MAST).

### 2019-02-10 figures/fig3_bestfits.py

@@ -8,30 +8,29 @@ def get_significance(chi2ratio, df1, df2):
 	z = norm.ppf(1.-alpha)
 	return z
 
-#err = 362.22e-6
 err = 367.e-6
-chi2min = 201.38
-#moon_ingress = 0.00191
 moon_ingress = 1.25
 period = 287.378949 
 xmin, xmax = -0.3, 1.7
+npoints = 219   #number of data points
 
 #teachey_dir = "teachey_fits/"
 #teachey_dir = "teachey_fits_xydecorr/"
-teachey_dir = "teachey_fits_poly2d_tophat/"
-lk_dir = "lk_fits_new/"
+#teachey_dir = "teachey_fits_poly2d_tophat/"
+teachey_dir = "teachey_fits_full/"
+lk_dir = "lk_fits_full/"
 
 plt.figure(figsize = (8.5,4))
 
 plt.subplot(221)
 plt.title("This Work")
-phase, data_nosys, norm_resid, t_hr, fit_hr, rms, rms_predicted, chi2, chi2red, chi2red_rms395, dof_nomoon = pickle.load(open(lk_dir + "no_moon.p", "rb"), encoding='latin1')
+phase, data_nosys, norm_resid, t_hr, fit_hr, rms, rms_predicted, chi2, chi2red, chi2red_rms395, dof_nomoon, nfree= pickle.load(open(lk_dir + "no_moon.p", "rb"), encoding='latin1')
 plt.plot(period*phase - period*np.min(phase), data_nosys, '.w', markeredgecolor = 'k')
 plt.plot(period*(t_hr) - period*np.min(phase), fit_hr, color = 'b', label = 'no moon', linewidth = 2.)
 chi2 = np.sum((norm_resid/err)**2) 
 
 npoints = len(phase)
-nfreepar = 219 - dof_nomoon
+nfreepar = npoints - dof_nomoon
 BIC_LK_nomoon = chi2 + nfreepar*np.log(npoints)
 BIC = chi2 + nfreepar*np.log(npoints)
 ax = plt.gca()
@@ -39,7 +38,8 @@ ax.text( 0.03, 0.52,
         '$\mathrm{rms} =$' + '{0:0.1f}'.format(rms) + '\n' 
         + '${\chi^2} = $' + '{0:0.1f}'.format(chi2) + '\n'
[…]

### 2019-02-10 figures/fig5_corner.py

@@ -5,13 +5,13 @@ import matplotlib.pyplot as plt
 def quantile(x, q): return np.percentile(x, [100. * qi for qi in q])
 
 
-chain = np.load("mcmc_output/mcmc_LK_full.npy")
+chain = np.load("mcmc_output/mcmc_LK_6par.npy")
 ndim = chain.shape[-1]
-samples_lk = chain[:, 5000:10000, :].reshape((-1, ndim))
+samples_lk = chain[:, 2000:10000, :].reshape((-1, ndim))
 
-chain = np.load("mcmc_output/mcmc_TK18_full.npy")
+chain = np.load("mcmc_output/mcmc_TK18_6par.npy")
 ndim = chain.shape[-1]
-samples_tk = chain[:, 5000:10000, :].reshape((-1, ndim))
+samples_tk = chain[:, 2000:10000, :].reshape((-1, ndim))
 
 samples_lk = samples_lk[:,[6,8]]
 #samples_lk[:,1] = samples[

### 2019-02-13 ms.tex
update abs

@@
 We compare our results directly with the original light curve from \cite{teachey18b}, and find that we obtain a better fit to the data using a model with fewer free parameters (no moon).
-We conclude that the evidence for the transit of Kepler-1625b I hinges on subtleties of the data reduction, and we therefore suggest that future follow-up efforts for exomoons should prioritize alternate targets.
-
+We discuss possible sources for the discrepancy in our results, and conclude that the lunar transit signal found by \cite{teachey18b} was likely an artifact of the data reduction.
 \end{abstract}
@@
 \subsection{Instrument Systematics Model}
+\label{sec:sys}
 There are two systematic trends in the data.
@@
 
-To fit the orbit-long ramp, we used the non-parametric model from TK18, which assigns each of the nine exposures per orbit a normalization constant, $c_1, ..., c_9$.
-To fit the visit-long trend, we used a linear combination of X and Y position (the shift relative to the mean in the spatial and spectral directions; shown in Figure~\ref{fig:shifts}).
+For our primary fit, we used a linear combination of the spectrum's X and Y position (shown in Figure~\ref{fig:shifts}), multiplied by the non-parametric orbital ramp model from TK18, which assigns each of the nine exposures per orbit a normalization constant, $c_1, ..., c_9$.
 In sum, for exposure number $i$, the systematics model S is:
@@
 where $a$ and $b$, and $c_j$ are free parameters, and $j = i\Mod9 + 1$ is the exposure number relative to the first exposure in the orbit.
+
+For comparison, we also tested the ``exponential" systematics model from TK18, which combines an exponential visit-long trend, an offset after orbit 14 when the guide stars were reacquired, and the non-parametric orbital ramp model.
 
@@
 
+We found that our results were unchanged when we used the exponential systematics model from TK18 (described in \S\,\ref{sec:sys}).
+For this case, the moon model is also strongly disfavored ($\Delta\rm{BIC} = 32.2$).
+The fit rms is within 5 ppm of the XY decorrelation model.
+
 \subsection{Comparison with Teachey \& Kipping (2018)}
@@
 To make a direct comparison with their results, we fit the TK18 light curve directly.
+We fit the astrophysical signal with both the no-moon and models, and used the exponential systematics model.
+Figure\,\ref{fig:bestfit} shows the best fit models.
 
-We fit the data with both the no-moon and models.
-For the systematics, we tested the XY decorrelation model described above, but found that it did not perform as well as the systematics models presented in TK18 (10\% higher rms and time-correlated residuals).
+%For the systematics, we tested the XY decorrelation model described above, but found that it did not perform as well as the systematics models presented in TK18 (10\% higher rms and time-correlated residuals).
 We therefore opted to use a TK18 systematics model to enable a fair comparison between our results.
 We obtained the best fit using an exponential trend in time, a constant offset after orbit 14 (where the guide stars are reacquired), and the non-parameteric orbit-long ramp model.
-This model has one more free parameter than the systematics model given in Equation~\ref{eq:sys}.
-Figure\,\ref{fig:bestfit} shows the best fit models.
+This model has one more free parameter than the XY decorrelation model given in Equation~\ref{eq:sys}.
 
@@
 \section{Discussion}
-A natural question arising from our results is what the difference is between TK18 and the new fits presented here.
+A natural question arising from our results is what the difference is between TK18 and the new fits presented here. Since we found that
+
 One possibility is that the source of the discrepancy is the extracted transit light curves themselves.

### 2019-02-13 figures/fig3_bestfits.py

@@ -19,6 +19,7 @@ npoints = 219   #number of data points
 #teachey_dir = "teachey_fits_poly2d_tophat/"
 teachey_dir = "teachey_fits_full/"
 lk_dir = "lk_fits_full/"
+#lk_dir = "lk_fits_quad/"
 
 plt.figure(figsize = (8.5,4))
 

### 2019-02-13 arxiv/ms.tex
ready to submit

--- 2019-02-13 ms.tex
@@
 
-\submitjournal{AJ}
+\submitjournal{ApJL}
 
@@
 We discuss possible sources for the discrepancy in our results, and conclude that the lunar transit signal found by \cite{teachey18b} was likely an artifact of the data reduction.
+This finding highlights the need to develop independent pipelines to confirm results that push the limits of measurement precision.
 \end{abstract}
@@
 \begin{figure}
-\includegraphics[width = 0.5 \textwidth]{figures/fig4_shifts.pdf}
+\includegraphics[width = 0.5 \textwidth]{fig1_shifts.pdf}
     \caption{Shift (in pixels) relative to the mean position of the spectrum in the spectral direction (top) and spatial direction (bottom).
@@
 \begin{figure}
-\includegraphics[width = 0.5 \textwidth]{figures/fig6_rawdata.pdf}
+\includegraphics[width = 0.5 \textwidth]{fig2_rawdata.pdf}
     \caption{Top: extractred light curve from this work (blue) compared to TK18 (red).
@@
 \begin{figure*}
-\includegraphics[width = 1.0 \textwidth]{figures/fig3_bestfits.pdf}
+\includegraphics[width = 1.0 \textwidth]{fig3_bestfits.pdf}
     \caption{Best fit models compared to normalized transit light curves from this work (left, blue) and from TK18 (right, red).
@@
 \begin{figure}
-\includegraphics[width = 0.5 \textwidth]{figures/fig2_rms.pdf}
+\includegraphics[width = 0.5 \textwidth]{fig4_rms.pdf}
     \caption{Light curve rms versus bin size for the best fit no-moon model (solid lines) and moon model (dashed lines), for data from this work (red) and TK18 (blue).
@@
 TK18 found evidence for the transit of a Neptune-size moon in their analysis of the HST data, in contrast to the findings presented here.
-To make a direct comparison with their results, we fit the TK18 light curve directly.
+To compare our results with theirs, we fit the TK18 light curve directly.
 We fit the astrophysical signal with both the no-moon and models, and used the exponential systematics model.
@@
 Notably, however, the moon model fit to the TK18 data does not perform better than the no-moon model fit to our new data (rms of 362 versus 356 ppm), even with the additional seven free parameters.
-%This difference in fit quality corresponds to $\Delta\mathrm{BIC} = 31.2$, which is strong evidence against the moon.
 
@@
 \begin{figure}
-\includegraphics[width = 0.5 \textwidth]{figures/fig5_pairs.pdf}
+\includegraphics[width = 0.5 \textwidth]{fig5_pairs.pdf}
     \caption{Posterior distributions for the moon radius and time of transit based on an MCMC fit to data from this work (blue) and from TK18 (red).
@@
 
-\section{Discussion}
-A natural question arising from our results is what the difference is between TK18 and the new fits presented here. Since we found that
+\section{Discussion \& Conclusions}
+A natural question arising from our analysis is the source of the discrepancy between TK18 and the new results presented here.
+We find that with our new data, there is strong evidence against the moon ($\Delta\rm{BIC} > 25$), even when we use a comparable model to TK18 (a 6-parameter moon model and an exponential fit to the visit-long trend).
 
-One possibility is that the source of the discrepancy is the extracted transit light curves themselves.
-As shown in Figure\,\ref{fig:raw}, our measured count rate ranges from $2.46 -2.74\%$ lower than the TK18 light curve, and there is a small bump in the difference between the two data sets near the location of the moon transit identified in the TK18 data (see the bottom panel).
+If the model is not the source of the difference, it must be the extracted transit light curves themselves.
+Figure\,\ref{fig:raw} shows a direct comparison of the light curves.
+The count rate we measure is $2.46 -2.74\%$ lower than the TK18 light curve, and there is a small bump in the difference between the two data sets near the location of the moon transit identified in the TK18 data (see the bottom panel).
+This bump may be the source of the moon feature reported in TK18.
 
- We explored several modifications to our pipeline to attempt to reproduce the TK18 reduction.
+ We explored several modifications to our pipeline to attempt to reproduce the TK18 data reduction.
 These included rotating the image by 0.5 degrees, using the same aperture as TK18 to extract the spectrum, and scaling the master sky flat for the background subtraction (rather than just subtracting the median).
@@
 
+We conclude that no single choice in the data reduction provides an easy explanation for the difference in our light curves.
+This finding illustrates the challenge of pushing measurement precision to the 100 ppm level, and highlights the importance of developing multiple independent pipelines to confirm cutting-edge results.
+
  %The only other difference we identify in the data reduction is the outlier masking.
@@
 
-In addition to these differences in data reduction, we also used an alternative detrending model.
+%In addition to these differences in data reduction, we also used an alternative detrending model.
 We opted for a decorrelation against X and Y position, motivated by known variation in the sensitivity of individual pixels on the detector and the presence of small shifts in the position of the spectrum (see Figure\,\ref{fig:shifts}).
@@
 
- We conclude that no single choice in the data reduction or the modeling provides an easy explanation for the difference in our results, but rather that the difference is more likely due to the combination of many subtle choices.
-
-\section{Conclusion}
-The hunt for exomoons remains exciting and volatile.
-Our analysis of the exomoon candidate Kepler-1625b I shows that the evidence in favor of the moon is highly sensitive to details of the data reduction and modeling.
+%\section{Conclusion}
+%The hunt for exomoons remains exciting and volatile.
+Our analysis of the exomoon candidate Kepler-1625b I shows that the evidence in favor of the moon is highly sensitive to details of the data reduction.
 Given that we achieve an excellent fit to the light curve with a no-moon model, and that the addition of a moon does not significantly improve the fit quality, we suggest that future allocation of follow-up resources for exomoons should prioritize alternate targets.

### 2019-02-13 ms-temp.tex
ready to submit

@@
 We compare our results directly with the original light curve from \cite{teachey18b}, and find that we obtain a better fit to the data using a model with fewer free parameters (no moon).
-We conclude that the evidence for the transit of Kepler-1625b I hinges on subtleties of the data reduction, and we therefore suggest that future follow-up efforts for exomoons should prioritize alternate targets.
-
+We discuss possible sources for the discrepancy in our results, and conclude that the lunar transit signal found by \cite{teachey18b} was likely an artifact of the data reduction.
+This finding highlights the need to develop independent pipelines to confirm results that push the limits of measurement precision.
 \end{abstract}
@@
 
+We found that our results were unchanged when we used the exponential systematics model from TK18 (described in \S\,\ref{sec:sys}).
+For this case, the moon model is also strongly disfavored ($\Delta\rm{BIC} = 32.2$).
+The fit rms is within 5 ppm of the XY decorrelation model.
+
 \subsection{Comparison with Teachey \& Kipping (2018)}
 TK18 found evidence for the transit of a Neptune-size moon in their analysis of the HST data, in contrast to the findings presented here.
-To make a direct comparison with their results, we fit the TK18 light curve directly.
+To compare our results with theirs, we fit the TK18 light curve directly.
+We fit the astrophysical signal with both the no-moon and models, and used the exponential systematics model.
+Figure\,\ref{fig:bestfit} shows the best fit models.
 
-We fit the data with both the no-moon and models.
-For the systematics, we tested the XY decorrelation model described above, but found that it did not perform as well as the systematics models presented in TK18 (10\% higher rms and time-correlated residuals).
+%For the systematics, we tested the XY decorrelation model described above, but found that it did not perform as well as the systematics models presented in TK18 (10\% higher rms and time-correlated residuals).
 We therefore opted to use a TK18 systematics model to enable a fair comparison between our results.
 We obtained the best fit using an exponential trend in time, a constant offset after orbit 14 (where the guide stars are reacquired), and the non-parameteric orbit-long ramp model.
-This model has one more free parameter than the systematics model given in Equation~\ref{eq:sys}.
-Figure\,\ref{fig:bestfit} shows the best fit models.
+This model has one more free parameter than the XY decorrelation model given in Equation~\ref{eq:sys}.
 
@@
 
-\section{Discussion}
-A natural question arising from our results is what the difference is between TK18 and the new fits presented here.
-One possibility is that the source of the discrepancy is the extracted transit light curves themselves.
-As shown in Figure\,\ref{fig:raw}, our measured count rate ranges from $2.46 -2.74\%$ lower than the TK18 light curve, and there is a small bump in the difference between the two data sets near the location of the moon transit identified in the TK18 data (see the bottom panel).
+\section{Discussion \& Conclusions}
+A natural question arising from our analysis is the source of the discrepancy between TK18 and the new results presented here.
+We find that with our new data, there is strong evidence against the moon ($\Delta\rm{BIC} > 25$), even when we use a comparable model to TK18 (a 6-parameter moon model and an exponential fit to the visit-long trend).
 
- We explored several modifications to our pipeline to attempt to reproduce the TK18 reduction.
+If the model is not the source of the difference, it must be the extracted transit light curves themselves.
+Figure\,\ref{fig:raw} shows a direct comparison of the light curves.
+The count rate we measure is $2.46 -2.74\%$ lower than the TK18 light curve, and there is a small bump in the difference between the two data sets near the location of the moon transit identified in the TK18 data (see the bottom panel).
+This bump may be the source of the moon feature reported in TK18.
+
+ We explored several modifications to our pipeline to attempt to reproduce the TK18 data reduction.
 These included rotating the image by 0.5 degrees, using the same aperture as TK18 to extract the spectrum, and scaling the master sky flat for the background subtraction (rather than just subtracting the median).
@@
 
-In addition to these differences in data reduction, we also used an alternative detrending model.
+%In addition to these differences in data reduction, we also used an alternative detrending model.
 We opted for a decorrelation against X and Y position, motivated by known variation in the sensitivity of individual pixels on the detector and the presence of small shifts in the position of the spectrum (see Figure\,\ref{fig:shifts}).
-We applied this detrending model to the TK18 data, and obtained a poor fit to the light curve compared to the polynomial detrending (for the moon model with X-Y decorrelation, the rms was 404 ppm).
+We applied this detrending model to the TK18 data, and obtained a poor fit to the light curve compared to exponential detrending (for the moon model with XY decorrelation, the rms was 404 ppm).
 We did not recover a large moon in this fit (the best fit was $r_\mathrm{moon} = 1.2R_\oplus$), but there was correlated noise present in the data that precluded a robust measurement of the uncertainty on the moon radius for this model.

### 2019-02-13 figures/fig1_shifts.py

@@ -69,5 +69,5 @@ plt.xlabel("Time from first exposure (days)")
 
 
 plt.tight_layout()
-plt.savefig('fig4_shifts.pdf')
+plt.savefig('fig1_shifts.pdf')
 #plt.show()

### 2019-02-13 figures/fig2_rawdata.py

@@ -56,4 +56,4 @@ for i in range(orb):
 #plt.plot(t_mean, diff_mean, 'or')
 
 plt.tight_layout()
-plt.savefig("fig6_rawdata.pdf")
+plt.savefig("fig2_rawdata.pdf")

### 2019-02-13 figures/fig4_rms.py

@@ -119,4 +119,4 @@ plt.gca().tick_params(axis='both', which='major', pad=2)
 
 plt.tight_layout()
 #plt.show()
-plt.savefig("fig2_rms.pdf")
+plt.savefig("fig4_rms.pdf")

### 2019-02-13 ms.tex
correct rmoon

@@
 Notably, however, the moon model fit to the TK18 data does not perform better than the no-moon model fit to our new data (rms of 362 versus 356 ppm), even with the additional seven free parameters.
-%This difference in fit quality corresponds to $\Delta\mathrm{BIC} = 31.2$, which is strong evidence against the moon.
 
 The moon model also yields qualitatively different posterior distributions for the two data sets.
-As shown in Figure\,\ref{fig:corner}, for the TK18 data the moon radius and transit time are peaked at $r_\mathrm{moon} = 4.0^{+0.8}_{-0.6}\,R_\oplus$  and $t_\mathrm{moon} =  2458056.29^{+0.06}_{-0.04}\,\mathrm{BJD_{TDB}}$.
+As shown in Figure\,\ref{fig:corner}, for the TK18 data the moon radius and transit time are peaked at $r_\mathrm{moon} = 3.9\pm0.5\,R_\oplus$  and $t_\mathrm{moon} =  2458056.29^{+0.06}_{-0.04}\,\mathrm{BJD_{TDB}}$.
 By contrast, the fit to the new data presented here yields an upper limit on the moon radius of $3.5\,R_\oplus$ at $3\sigma$ confidence, and the transit time is unconstrained.

### 2019-02-13 figures/mcmc_output/parse_white_mcmc.py

@@ -1,0 +1,34 @@
+import sys                                                                      
+import pickle                                                                   
+import os                                                                       
+import glob                                                                     
+import numpy as np                                                              
+import matplotlib.pyplot as plt 
+import corner
+
+def quantile(x, q): return np.percentile(x, [100. * qi for qi in q]) 
+
+
+ndim = 15
+chain = np.load("mcmc_TK18_6par.npy")
+
+samples = chain[:, 2000:10000, :].reshape((-1, ndim))
+
+
+medians, err_hi, twosig, threesig, err_lo = [], [], [], [], []
+
+for i in range(ndim):
+        q = quantile(samples[:, i], [0.16, 0.5, 0.84, 0.95, 0.997])
+        medians.append(q[1])
+        err_hi.append(q[2] - q[1])
+        err_lo.append(q[1] - q[0])
+        twosig.append(q[3])
+        threesig.append(q[4])
+        print(medians[i], err_lo[i], err_hi[i])
+
+print("moon 2sig, 3sig:", twosig[8], threesig[8])
+print("moon med/err:", medians[8], err_lo[8], err_hi[8])
+
+
+
+

### 2019-04-24 apj_v2/ms.tex
revisions

--- 2019-02-13 arxiv/ms.tex
@@
-\documentclass[twocolumn]{aastex62}
+\documentclass[twocolumn,trackchanges]{aastex62}
 
@@
 The host planet, Kepler-1625b, has a radius consistent with that of Jupiter and an orbital period of 287 days.
-The first evidence for the exomoon candidate, Kepler-1625b I, was based on transit observations from \Kepler, which were discrepant with a planet-only model at $>4\sigma$ confidence \citep{teachey18a}.
-Follow-up observations with HST also suggested evidence for a moon, based on a small drop in the system flux after the planet's egress from transit and a possible transit timing variation \citep[][ hereafter TK18]{teachey18b}.
-The best fit moon had a large radius (comparable to that of Neptune), and if real, would be unlike any moon in the Solar System.
+\added{The first evidence for the exomoon candidate, Kepler-1625b I, was based on observations from \Kepler.
+The light curve showed drops in stellar flux that were attributed to a transiting exomoon; however, later analysis called this result into question, showing that the moon transit features were highly sensitive to the \Kepler\ reduction pipeline and the algorithm used to detrend the data \citep{teachey18b, rodenbeck18}.
 
-Recently, \cite{rodenbeck18} performed an independent fit to the Kepler light curves and found that the evidence for the moon was strongly dependent on the detrending method.
-Motivated by this result, in this work we perform an independent reduction and fit to the HST light curve.
+Subsequent follow-up observations with \HST\ revived the possibility of an exomoon in the system based on two factors: a small drop in the system flux after the planet's transit egress and a transit timing variation \citep[][ hereafter TK18]{teachey18b}.
+The best fit moon had a large radius (comparable to that of Neptune), and if real, is unlike any moon in the Solar System.
+
+Since the primary evidence for the exomoon now rests on the \HST\ transit light curve, in this work we perform an independent reduction and fit to the \HST\ data and compare it to the results from TK18.}
 
@@
 %This procedure masks any cosmic rays or bad pixels that were missed by the initial \texttt{flt} calibration.
+
+\added{The broadband light curve is shown in Figure\,\ref{fig:raw}, in comparison to the light curve from TK18.
+We note that there are differences between the two data sets, particularly a kink near the moon-like transit feature identified by TK18.}
 
@@
 \section{Analysis}
-The extracted transit light transit light curve (shown in Figure~\ref{fig:raw}) contains both astrophysical signals and instrument systematic noise, which we model simultaneously.
+The extracted transit light transit light curve contains both astrophysical signals and instrument systematic noise, which we model simultaneously.
 
@@
 For the astrophysics, we used the \texttt{planetplanet} package \citep{luger17}, a photodynamical code that calculates light curves for multiple occulting bodies orbiting a star.
-Within \texttt{planetplanet}, the orbits are computed with the N-body integrator \texttt{REBOUND} \citep{rein12}.
+Within \texttt{planetplanet}, the orbits are computed with the N-body integrator \texttt{REBOUND} \citep{rein12}, \added{which calculates the three-dimensional motion of the star, planet, and moon over time under the influence of gravity}.
 %The \texttt{planetplanet} model returns the system flux at a specified orbital architecture and time.
@@
 We fixed the eccentricity of all bodies to zero.
-We also fixed the planet's orbital period to 287.378949 days (the best fit from TK18).
+We also fixed the  orbital period \added{of the planet-moon barycenter} to 287.378949 days (the best fit from TK18).
+\added{We elected not to vary the period of the planet-moon barycenter because it is poorly constrained from a single transit observation.
+A longer period would cause a longer transit duration for the planet, but this could equivalently result from a smaller impact parameter, a larger star, or a massive moon that significantly perturbs the planetary orbit.}
 
@@
 The Hill radius calculation assumed the planet and stellar masses are $1\,M_\mathrm{Jup}$ and $1.37\,M_\odot$.
-The moon inclination was uniform from $89.7 - 90^\circ$ (to exclude grazing moon transit scenarios, where the moon radius could be arbitrarily large).
 The moon mass varied uniformly from $0 - 30 M_\oplus$.
-The longitude of the ascending node was also uniform from $0 - 180^\circ$.
+The longitude of the ascending node was also uniform from $0 - 360^\circ$.
+\added{The moon inclination was uniform from $0 - 90^\circ$,  and was defined relative to that of the planet.
+A $90^\circ$ inclined orbit has an impact parameter of zero on the disk of the planet.
+We assigned zero prior probability to scenarios where the moon did not transit or experienced a grazing transit.
+We made this choice to put an upper limit on the radius of a fully transiting moon; for grazing transits or non-transits the moon radius could be arbitrarily large.}
 
@@
 
-We estimated the host star parameters using the Gaia DR2 parallax \citep{Gaia, GaiaDR2} along with UBV photometry from \citet{Everett2012} and JHK photometry from 2MASS \citep{2MASS}.
+We estimatea the host star parameters using the Gaia DR2 parallax \citep{Gaia, GaiaDR2} along with UBV photometry from \citet{Everett2012} and JHK photometry from 2MASS \citep{2MASS}.
 We employed the isochrone python package \citep{isochrone} with the Dartmouth isochrone grid \citep{Dotter2008} to obtain posterior constraints on the stellar parameters.
@@
 This constitutes strong evidence against the inclusion of a moon \citep{kass95}.
-In addition, as shown in Figure\,\ref{fig:corner}, the posterior distribution for the moon transit time is not unimodal, and the $2\,\sigma$ confidence interval for the moon's transit spans the entire duration of the observations.
-The upper limit on the moon radius is $3.5\,R_\oplus$ at $3\sigma$ confidence.
+In addition, as shown in Figure\,\ref{fig:corner}, the posterior distribution for the moon transit time spans the entire duration of the observations ($2\sigma$ confidence).
+The upper limit on the moon radius is \deleted{3.5} \added{$3.6\,R_\oplus$} at $3\sigma$ confidence.
 
@@
 The fit rms is within 5 ppm of the XY decorrelation model.
+
+\added{The posterior probabilites for the planet's mass and radius are consistent with either a gas giant planet or brown dwarf.
+The radius is $11.1^{+0.5}_{-0.2}\,R_\oplus$ and mass is $10^{2.2\pm0.5}\, M_\oplus$.}
 
@@
 The moon model also yields qualitatively different posterior distributions for the two data sets.
-As shown in Figure\,\ref{fig:corner}, for the TK18 data the moon radius and transit time are peaked at $r_\mathrm{moon} = 4.0^{+0.8}_{-0.6}\,R_\oplus$  and $t_\mathrm{moon} =  2458056.29^{+0.06}_{-0.04}\,\mathrm{BJD_{TDB}}$.
-By contrast, the fit to the new data presented here yields an upper limit on the moon radius of $3.5\,R_\oplus$ at $3\sigma$ confidence, and the transit time is unconstrained.
+As shown in Figure\,\ref{fig:corner}, for the TK18 data the moon radius and transit time are peaked at \deleted{$r_\mathrm{moon} = 3.9\pm0.5\,R_\oplus$} \added{$r_\mathrm{moon} = 4.3\pm0.5\,R_\oplus$}  and $t_\mathrm{moon} =  2458056.29^{+0.06}_{-0.04}\,\mathrm{BJD_{TDB}}$.
+By contrast, the fit to the new data presented here yields an upper limit on the moon radius of \deleted{3.5} \added{$3.6\,R_\oplus$} at $3\sigma$ confidence, and the transit time is unconstrained.
 
-The mid-transit times from the two fits agree better.
-TK18 found that the planet transited earlier than expected based on the Kepler data.
-Our posterior distribution for the planet's transit time agrees with TK18 to within $1\sigma$, leaving open the possibility for transit timing variations due to another body in the system.
+\added{Although the two data sets yield different constraints on the moon properties, the planet's mid-transit time agrees to better than $1\sigma$ for the two fits.
+The transit time is earlier than expected based on the Kepler data ($3\sigma$ confidence; TK18), suggesting that there are transit timing variations in the system.
+Such variation could arise from the presence of a moon, as suggested by TK18; however, the variation could also be caused by another planet in the system.}
 
@@
 We also do not use the STScI software \texttt{aXeprep} to embed the raw $256\times256$ image in a larger array; however, this process primarily affects the edge of the image, many pixels distant from the extraction box, so it is unclear how this step would bias the light curve.
+We conclude that no single choice in the data reduction provides an easy explanation for the difference in our light curves.
 
-We conclude that no single choice in the data reduction provides an easy explanation for the difference in our light curves.
-This finding illustrates the challenge of pushing measurement precision to the 100 ppm level, and highlights the importance of developing multiple independent pipelines to confirm cutting-edge results.
+\added{During the referee process for this work, we learned of another manuscript that also reanalyzed the \HST\ transit observation \citep{heller19}.
+The best fit favored a moon model similar to that found by TK18;  however, an MCMC analysis did not converge on this model, leading the authors to conclude that the highest likelihood solution may be an outlier.}
+
+Taken together, these findings illustrate the challenge of pushing measurement precision to the 100 ppm level, and highlight the importance of developing multiple independent pipelines to confirm cutting-edge results.
 
@@
 Teachey for helpful discussions and for providing the extracted light curve from TK18.
+We also thank the anonymous referee for a thoughtful report that improved the manuscript.
 The HST data presented in this paper were obtained from the Mikulski Archive for Space Telescopes (MAST).

### 2019-04-24 arxiv_v1/ms.tex
revisions

--- 2019-04-24 apj_v2/ms.tex
@@
 The host planet, Kepler-1625b, has a radius consistent with that of Jupiter and an orbital period of 287 days.
-\added{The first evidence for the exomoon candidate, Kepler-1625b I, was based on observations from \Kepler.
+The first evidence for the exomoon candidate, Kepler-1625b I, was based on observations from \Kepler.
 The light curve showed drops in stellar flux that were attributed to a transiting exomoon; however, later analysis called this result into question, showing that the moon transit features were highly sensitive to the \Kepler\ reduction pipeline and the algorithm used to detrend the data \citep{teachey18b, rodenbeck18}.
@@
 
-Since the primary evidence for the exomoon now rests on the \HST\ transit light curve, in this work we perform an independent reduction and fit to the \HST\ data and compare it to the results from TK18.}
+Since the primary evidence for the exomoon now rests on the \HST\ transit light curve, in this work we perform an independent reduction and fit to the \HST\ data and compare it to the results from TK18.
 
@@
 
-\added{The broadband light curve is shown in Figure\,\ref{fig:raw}, in comparison to the light curve from TK18.
-We note that there are differences between the two data sets, particularly a kink near the moon-like transit feature identified by TK18.}
+The broadband light curve is shown in Figure\,\ref{fig:raw}, in comparison to the light curve from TK18.
+We note that there are differences between the two data sets, particularly a kink near the moon-like transit feature identified by TK18.
 
@@
 For the astrophysics, we used the \texttt{planetplanet} package \citep{luger17}, a photodynamical code that calculates light curves for multiple occulting bodies orbiting a star.
-Within \texttt{planetplanet}, the orbits are computed with the N-body integrator \texttt{REBOUND} \citep{rein12}, \added{which calculates the three-dimensional motion of the star, planet, and moon over time under the influence of gravity}.
+Within \texttt{planetplanet}, the orbits are computed with the N-body integrator \texttt{REBOUND} \citep{rein12}, which calculates the three-dimensional motion of the star, planet, and moon over time under the influence of gravity.
 %The \texttt{planetplanet} model returns the system flux at a specified orbital architecture and time.
@@
 We fixed the eccentricity of all bodies to zero.
-We also fixed the  orbital period \added{of the planet-moon barycenter} to 287.378949 days (the best fit from TK18).
-\added{We elected not to vary the period of the planet-moon barycenter because it is poorly constrained from a single transit observation.
-A longer period would cause a longer transit duration for the planet, but this could equivalently result from a smaller impact parameter, a larger star, or a massive moon that significantly perturbs the planetary orbit.}
+We also fixed the  orbital period of the planet-moon barycenter to 287.378949 days (the best fit from TK18).
+We elected not to vary the period of the planet-moon barycenter because it is poorly constrained from a single transit observation.
+A longer period would cause a longer transit duration for the planet, but this could equivalently result from a smaller impact parameter, a larger star, or a massive moon that significantly perturbs the planetary orbit.
 
@@
 The longitude of the ascending node was also uniform from $0 - 360^\circ$.
-\added{The moon inclination was uniform from $0 - 90^\circ$,  and was defined relative to that of the planet.
+The moon inclination was uniform from $0 - 90^\circ$,  and was defined relative to that of the planet.
 A $90^\circ$ inclined orbit has an impact parameter of zero on the disk of the planet.
 We assigned zero prior probability to scenarios where the moon did not transit or experienced a grazing transit.
-We made this choice to put an upper limit on the radius of a fully transiting moon; for grazing transits or non-transits the moon radius could be arbitrarily large.}
+We made this choice to put an upper limit on the radius of a fully transiting moon; for grazing transits or non-transits the moon radius could be arbitrarily large.
 
@@
 In addition, as shown in Figure\,\ref{fig:corner}, the posterior distribution for the moon transit time spans the entire duration of the observations ($2\sigma$ confidence).
-The upper limit on the moon radius is \deleted{3.5} \added{$3.6\,R_\oplus$} at $3\sigma$ confidence.
+The upper limit on the moon radius is $3.6\,R_\oplus$ at $3\sigma$ confidence.
 
@@
 
-\added{The posterior probabilites for the planet's mass and radius are consistent with either a gas giant planet or brown dwarf.
-The radius is $11.1^{+0.5}_{-0.2}\,R_\oplus$ and mass is $10^{2.2\pm0.5}\, M_\oplus$.}
+The posterior probabilites for the planet's mass and radius are consistent with either a gas giant planet or brown dwarf.
+The radius is $11.1^{+0.5}_{-0.2}\,R_\oplus$ and mass is $10^{2.2\pm0.5}\, M_\oplus$.
 
@@
 The moon model also yields qualitatively different posterior distributions for the two data sets.
-As shown in Figure\,\ref{fig:corner}, for the TK18 data the moon radius and transit time are peaked at \deleted{$r_\mathrm{moon} = 3.9\pm0.5\,R_\oplus$} \added{$r_\mathrm{moon} = 4.3\pm0.5\,R_\oplus$}  and $t_\mathrm{moon} =  2458056.29^{+0.06}_{-0.04}\,\mathrm{BJD_{TDB}}$.
-By contrast, the fit to the new data presented here yields an upper limit on the moon radius of \deleted{3.5} \added{$3.6\,R_\oplus$} at $3\sigma$ confidence, and the transit time is unconstrained.
+As shown in Figure\,\ref{fig:corner}, for the TK18 data the moon radius and transit time are peaked at $r_\mathrm{moon} = 4.3\pm0.5\,R_\oplus$  and $t_\mathrm{moon} =  2458056.29^{+0.06}_{-0.04}\,\mathrm{BJD_{TDB}}$.
+By contrast, the fit to the new data presented here yields an upper limit on the moon radius of $3.6\,R_\oplus$ at $3\sigma$ confidence, and the transit time is unconstrained.
 
-\added{Although the two data sets yield different constraints on the moon properties, the planet's mid-transit time agrees to better than $1\sigma$ for the two fits.
+Although the two data sets yield different constraints on the moon properties, the planet's mid-transit time agrees to better than $1\sigma$ for the two fits.
 The transit time is earlier than expected based on the Kepler data ($3\sigma$ confidence; TK18), suggesting that there are transit timing variations in the system.
-Such variation could arise from the presence of a moon, as suggested by TK18; however, the variation could also be caused by another planet in the system.}
+Such variation could arise from the presence of a moon, as suggested by TK18; however, the variation could also be caused by another planet in the system.
 
@@
 
-\added{During the referee process for this work, we learned of another manuscript that also reanalyzed the \HST\ transit observation \citep{heller19}.
-The best fit favored a moon model similar to that found by TK18;  however, an MCMC analysis did not converge on this model, leading the authors to conclude that the highest likelihood solution may be an outlier.}
+During the referee process for this work, we learned of another manuscript that also reanalyzed the \HST\ transit observation \citep{heller19}.
+The best fit favored a moon model similar to that found by TK18;  however, an MCMC analysis did not converge on this model, leading the authors to conclude that the highest likelihood solution may be an outlier.
 

### 2019-04-24 figures/fig2_rawdata.py

@@ -3,20 +3,8 @@ import matplotlib.pyplot as plt
 
 moon_ingress = 1.25
 
-d = np.genfromtxt("lc_kep1625_kreidberg.txt")
-#d = np.genfromtxt("lc_kep1625_kreidberg_rot_1_16_19.txt")
-ind = np.arange(len(d))                                                
-d= d[np.argsort(d[:,0])]
-d = d[(ind!=106)&(ind!=115)&(ind != 0)&(ind!=124)&(ind!=125)] 
-print("len lk", len(d[:,0]))
-
-
 plt.figure(figsize = (4.5,4.5))
 plt.subplot(211)
-med = np.median(d[0:50, 1])
-
-plt.plot(d[:,0] - np.min(d[:,0]), d[:,1]/1.e6, '.b', alpha = 0.5, label = "This work")
-#plt.plot(d[:,0] - np.min(d[:,0]), np.log(d[:,1]), '.b', alpha = 0.5, label = "This work")
 
 
 e = np.genfromtxt("prehook_correction_discrete.dat")
@@ -26,6 +14,19 @@ plt.plot(e[:,0] - np.min(e[:,0]), e[:,1]*290.776306/1.e6, '.r', alpha = 0.5, lab
 #plt.plot(e[:,0] - np.min(e[:,0]), np.log(e[:,1]*290.776306), '.r', alpha = 0.5, label = "TK18")
 plt.ylabel("Photoelectrons ($\\times10^6$)")
 
+d = np.genfromtxt("lc_kep1625_kreidberg.txt")
+#d = np.genfromtxt("lc_kep1625_kreidberg_rot_1_16_19.txt")
+ind = np.arange(len(d))                                                
+d= d[np.argsort(d[:,0])]
+d = d[(ind!=106)&(ind!=115)&(ind != 0)&(ind!=124)&(ind!=125)] 
+print("len lk", len(d[:,0]))
+
+
+med = np.median(d[0:50, 1])
+
+plt.plot(d[:,0] - np.min(d[:,0]), d[:,1]/1.e6, '.b', alpha = 0.5, label = "This work")
+#plt.plot(d[:,0] - np.min(d[:,0]), np.log(d[:,1]), '.b', alpha = 0.5, label = "This work")
+
 plt.legend(loc = 'center right')
 #plt.ylim(9, 9.4)
 
@@ -34,7 +35,7 @@ plt.subplot(212)
 
[…]

### 2019-04-24 figures/fig5_corner.py

@@ -5,26 +5,45 @@ import matplotlib.pyplot as plt
 def quantile(x, q): return np.percentile(x, [100. * qi for qi in q])
 
 
-chain = np.load("mcmc_output/mcmc_LK_6par.npy")
+"""chain = np.load("mcmc_output/mcmc_LK_6par.npy")
 ndim = chain.shape[-1]
-samples_lk = chain[:, 2000:10000, :].reshape((-1, ndim))
+samples_lk = chain[:, 2000:10000, :].reshape((-1, ndim))"""
+#samples_lk = samples_lk[:,[6,8]]
 
-chain = np.load("mcmc_output/mcmc_TK18_6par.npy")
+chain = np.load("mcmc_output/mcmc_LK_correct_for_referee.npy")
+chain[0,:] -= 2458055.
+ind = chain[2,:] == 1
+chain = chain[:,ind]
+samples_lk = chain[[0,1], :]
+samples_lk = samples_lk.T
+
+"""chain = np.load("mcmc_output/mcmc_TK18_6par.npy")
 ndim = chain.shape[-1]
 samples_tk = chain[:, 2000:10000, :].reshape((-1, ndim))
+samples_tk = samples_tk[:,[6,8]].T"""
 
-samples_lk = samples_lk[:,[6,8]]
+chain = np.load("mcmc_output/mcmc_TK18_correct_for_referee.npy")
+ind = chain[2,:] == 1
+chain = chain[:,ind]
+chain[0,:] -= 2458055.
+samples_tk = chain[[0,1], :]
+
+
+print("LK shape", samples_lk.shape)
+print("TK shape", samples_tk.shape)
+#print("samples TK meds", np.median(samples_tk[0,:]), np.median(samples_tk[1,:]))
 #samples_lk[:,1] = samples[
 
-samples_tk = samples_tk[:,[6,8]].T
 corner.corner(samples_lk, samples_tk, plot_datapoints = False, 
-            levels = [0.68, 0.95, 0.997], fill_contours = True, alpha = 0.5, 
+            levels = [0.68, 0.95, 0.997], fill_contours = True, alpha = 1.0, 
             color = 'blue', 
+            range = [(-0.25,1.5), (0,5)],
             labels = ["Moon mid-transit time\n(BJD$_\mathrm{TDB}$ - 2458055)", 
             "Moon radius (R$_\oplus$)"]) 
 
[…]

### 2019-04-24 figures/mycorner.py

@@ -216,6 +216,8 @@ def corner(xs, ys, bins=20, range=None, weights=None, color="k",
 
         n, _, _ = ax.hist(y1, color = 'r',  normed = True, histtype = 'step') 
 
+        #if i == 0: ax.xlim(0,5)
+
         if truths is not None and truths[i] is not None:
             ax.axvline(truths[i], color=truth_color)
 
@@ -255,6 +257,8 @@ def corner(xs, ys, bins=20, range=None, weights=None, color="k",
 
         # Set up the axes.
         ax.set_xlim(range[i])
+        if i == 1: ax.set_xlim(0, 5) #LK
+
         if scale_hist:
             maxn = np.max(n)
             ax.set_ylim(-0.1 * maxn, 1.1 * maxn)
@@ -312,6 +316,7 @@ def corner(xs, ys, bins=20, range=None, weights=None, color="k",
             hist2d(y2, y1, ax=ax, range=[range[j], range[i]], weights=weights,
                    color='red', smooth=smooth, bins=[bins[j], bins[i]],
                    **hist2d_kwargs)
+            print("ranges", range)
 
 
             if truths is not None:

### 2019-05-21 apj_v3/ms.tex
revised version

--- 2019-04-24 arxiv_v1/ms.tex
@@
 The longitude of the ascending node was also uniform from $0 - 360^\circ$.
-The moon inclination was uniform from $0 - 90^\circ$,  and was defined relative to that of the planet.
-A $90^\circ$ inclined orbit has an impact parameter of zero on the disk of the planet.
-We assigned zero prior probability to scenarios where the moon did not transit or experienced a grazing transit.
+The moon inclination was uniform from $0 - 90^\circ$,  and was defined relative to the \added{line of sight}.
+\deleted{A $90^\circ$ inclined orbit has an impact parameter of zero on the disk of the planet.} We assigned zero prior probability to scenarios where the moon did not transit or experienced a grazing transit.
 We made this choice to put an upper limit on the radius of a fully transiting moon; for grazing transits or non-transits the moon radius could be arbitrarily large.
